### 2019-08-07 Manuscript/Manuscript.Rmd
Initial commit

---
title             : "Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions"
shorttitle        : "DOMAIN-SPECIFIC WORKING MEMORY AND SURPRISED EXPRESSIONS"

author: 
  - name          : "Nicholas R. Harp"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "nharp@huskers.unl.edu"
  - name          : "Maital Neta"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Nebraska-Lincoln"

authornote: |
  Nicholas R. Harp, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln
  Maital Neta, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln

abstract: |
  Individual differences in interpretations of emotional ambiguity are a useful tool for measuring affective biases.

  While trait-like, these biases are also susceptible to experimental manipulations. In the present study, we capitalize on this malleability to expand on previous research suggesting that
  subjective interpretations are stable independently of cognitive load.

  We tested the effects of working memory loads containing either neutral or emotional content on concurrent interpretations of surprised facial expressions.

  Here we show that interpretations of surprise are more negative during maintenance of working memory loads with emotional content compared to those with neutral content.

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "ambiguity, working memory, bias"
wordcount         : "X"

bibliography      : ["CANLab_UNL.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
### import z score updated function ###
source("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/wilcox_test.R")
### code edits taken from : https://stats.stackexchange.com/questions/306841/z-score-on-wilcoxon-signed-ranks-test ###

### load necessary libraries ###
library(readxl)
library(tidyverse)
library(openxlsx)
library(Rmisc)
library(broom)
```
# Introduction
Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world. In fact, facial expressions are seen across cultures [@ekman_constants_1971] and some evidence suggests expressions are innate (cite). Often, facial expressions serve as a clear social signal, but this is not always the case. While a smile from a friend likely expresses a positive affective state, other cues are not so clear. For instance, a surprised facial expression could signal either a positive (e.g., winning the lottery) or negative (e.g., a snake in the woods) affective state. In the absence of a larger context, individuals differ in their tendency to interpret surprised facial expressions as either positive or negative. Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to both surprised faces and ambiguous scenes [@neta_neural_2013]. This bias towards positive or negative interpretations is known as one's valence bias. 
Interpreting facial expressions requires both bottom-up (e.g., perceptual input) and top-down (e.g., emotion regulation strategies) processes. A growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes, and that arriving at a positive interpretation requires additional, top-down regulatory processes. For example, participants reliably rate surprise as negative faster than positive [@neta_dont_2016]. In fact, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018]. Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. In short,  
Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018]. Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017]. Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.

Understanding the influences on decision making under ambiguous contexts sheds light on the mechanisms responsible for these individual differences. in the present study we aim to better understand how concurrent task demands (i.e., working memory load) may influence the cognitive resources used to arrive at more top-down driven interpetations of ambiguity, specifically in an emotional context.  
  Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces [@mattek_differential_2016; @neta_dont_2016]. 
The valence bias is trait-like [@neta_corrugator_2009] and generalizes to non-face stimuli [@neta_neural_2013]; however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding [@brown_cortisol_2017; @neta_dont_2016]. Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology [@petro_initial_2018], at least in children. Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety [@matthews_cognitive_2005].

Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks [; cite, cite]. Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli [@gruber_effects_2001]. This effect holds up in the emotional domain; for example, the Stroop task [@stroop_studies_1935] has been modified by some researchers to include emotional stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Indeed, neuroimaging work supports the idea that separate systems handle attentional biasing for domain-specific (emotional vs. non-emotional) task relevancy [@egner_dissociable_2008].
Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference. Mattek and colleagues [-@mattek_differential_2016] recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories. While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias. Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed. 
In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains. We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials. Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations. 
<!-- Even simple tasks (e.g., remembering a phone number) reveal the limits of  human cognition. In fact, many researchers believe that there is a magic number of the amount of information able to be held in working memory (7 +- 2 paper). Others have focused on the limits of working memory and successful task performance to inform industrial and organizational policies [@sweller_cognitive_1998]. Despite the large amount of research around working memory and cognitive control, much controversy remains around the mechanisms through which attention to perceptually salient stimuli affect attentional processes and subsequent cognitive control [@lavie_load_2004]. Specifically, there is a divide amongst researchers that believe cognitive loads either inhibit perceptions of non-relevant stimuli -->

<!-- Notes: Allie showed that depletion doesn't affect ratings, but we thought that there may be an effect of specific domains of depletion (i.e., neutral vs. emotional) on ratings. Focus on EMO > NEU ratings and POS > NEG MDs. MT analyses could be supplementary material, but you'll be going down the rabbit hole.  -->
<!-- Recently, others have suggested a dynamic social trait space model for judgments of faces [@stolier_dynamic_2018], and it may be important to consider additional components of the categorization process, such as domain-specific loads.  -->

# Methods
## Participants
58 subjects were recruited from the University of Nebraska-Lincoln. All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the local Institutional Review Board (Approval #20141014670EP). The data from eight subjects were excluded due to technical difficulties or an error in the experiment script. This left 50 individuals in the final sample.

## Material
### Stimuli
``` {r stimulus_t.test, include = FALSE}
stim.data <- read.xlsx("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/IAPS_Stim_List.xlsx")
shapiro.test(subset(stim.data, Condition == "POS")$Aro_Mn)
shapiro.test(subset(stim.data, Condition == "NEG")$Aro_Mn)
stim.t.test <- wilcox_test(subset(stim.data, Condition == "POS")$Aro_Mn, subset(stim.data, Condition == "NEG")$Aro_Mn)
```
The stimuli included faces taken from the NimStim [@tottenham_nimstim_2009] and Karolinska Directed Emotional Faces [@lundqvist_karolinska_1998] stimuli sets. The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly. The scenes were taken from the International Affective Picture System [@lang_international_2008]. A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices. The positive and negative images did not differ on arousal (Z = `r printnum(stim.t.test$z_val)`, p = `r printnum(stim.t.test$p.value)`). The scenes were organized into low (two images) and high (six images) cognitive load of either neutral or emotional (equal number of positive and negative) images (Figure 1).

### Software
The task was completed in MouseTracker [@freeman_mousetracker:_2010] and participants used a mouse to click the appropriate response for the face ratings (i.e., "POSITIVE" or "NEGATIVE") and the memory probe (i.e., "YES" or "NO").

## Procedure
Participants were randomly assigned to complete one of the task versions. The tasks included 144 [^1] trials split between working memory probe and face rating trials. On each trial, participants first viewed an image matrix of either neutral or emotional images, which the participants were instructed to remember for the duration of the trial.  The image matrix was presented for four seconds and the images were swapped from low and high load matrices across versions of the task. After the image matrix a happy, angry, or surprised face appeared for one second and the participants rated the face by clicking on either the positive or negative response option. After the face rating, a single image probe appeared, and participants indicated whether or not the image probe was present in the previous image matrix.

[^1]: Some versions of the task only included 142 trials due to a programming error.

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses. Data preprocessing was completed in R using the mousetrap package [@kieslich_mouse-tracking_inpress]. First, percent negative ratings were calculated for happy, angry, and surprised faces across all trial types, as well as a percent correct score for the memory probe trials. After, trials were screened for RT outliers. Any trials that were greater than three standard deviations from the mean were removed from the analyses. Additionally, we removed the preceding face rating trial for any incorrect memory probe trials, as these trials can be considered a manipulation failure.

Prior to completing the analyses, the data were assessed for normality using the Shapiro-Wilks test. Data that met the normality assumption were submitted to repeated measures ANOVA, while data that failed to meet this assumption was analyzed using non-parametric tests. We tested for differences in valence bias among the different working memory load conditions. Friedman's test was used to assess overall differences and pairwise comparisons were completed using Wilcoxon signed rank tests using Bonferroni correction. The same analysis strategy was also used to assess differences in reaction times, collapsed across both positive and negative interpretations of surprised facial expressions. Finally, we checked for differences between reaction times for both positive and negative ratings of surprise in each working memory load condition. Due to a large amount of missing data (almost 50% of the subjects), as a result of some subjects only choosing the positive or negative response option in a given working memory load condition, we were unable to analyze these data with Friedman's test. Thus, we conducted a series of Wilcoxon signed rank tests for each of the four conditions with Bonferroni correction.

# Results
## Subjective ratings
```{r import data and analyze ratings, include = FALSE, echo = TRUE}
data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/Final.Data.csv_2019-08-01_12-38-57.csv")
### remove psych disorders ### Ask maital?
# data <- data[-c(4, 33, 37, 38, 41, 47),]

### assess normality ###
shapiro.test(data$lo.neu.sur_rate)
shapiro.test(data$hi.neu.sur_rate)
shapiro.test(data$lo.emo.sur_rate)
shapiro.test(data$hi.emo.sur_rate)

### make data long ###
friedman.data <- gather(data, key = "Condition", value = "Percent Negative Ratings",
       lo.neu.sur_rate, hi.neu.sur_rate, lo.emo.sur_rate, hi.emo.sur_rate)

### run Friedman's test and store results ###
friedman.results <- friedman.test(`Percent Negative Ratings` ~ Condition|subjID, data = friedman.data)

### Follow up wilcoxon tests ###
lo.emo.v.lo.neu <- wilcox_test(data$lo.emo.sur_rate, data$lo.neu.sur_rate, paired = TRUE, conf.int = TRUE)
lo.emo.v.hi.neu <- wilcox_test(data$lo.emo.sur_rate, data$hi.neu.sur_rate, paired = TRUE, conf.int = TRUE)
lo.emo.v.hi.emo <- wilcox_test(data$lo.emo.sur_rate, data$hi.emo.sur_rate, paired = TRUE, conf.int = TRUE)
hi.emo.v.lo.neu <- wilcox_test(data$hi.emo.sur_rate, data$lo.neu.sur_rate, paired = TRUE, conf.int = TRUE)
hi.emo.v.hi.neu <- wilcox_test(data$hi.emo.sur_rate, data$hi.neu.sur_rate, paired = TRUE, conf.int = TRUE)
lo.neu.v.hi.neu <- wilcox_test(data$hi.neu.sur_rate, data$lo.neu.sur_rate, paired = TRUE, conf.int = TRUE)

```
Distributions of ratings were first tested for normality using Shapiro-Wilk's test. The results of all four tests were highly significant (p's < .001), so non-parametric tests were used for data analysis. Friedman's test results showed significantly different distributions across the conditions $\chi^{2}$(`r (printnum(friedman.results$parameter))`) = `r printnum(friedman.results$statistic)`, p `r printp(friedman.results$p.value)`. Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content. Low emotional load ratings were significantly more negative than low, Z = `r (printnum(lo.emo.v.lo.neu$z_val))`, p = `r (printp(lo.emo.v.lo.neu$p.value))`, neutral and high, Z = `r (printnum(lo.emo.v.hi.neu$z_val))`, p `r (printp(lo.emo.v.hi.neu$p.value))`, neutral loads. The same was true for high emotional load ratings and low, Z = `r (printnum(hi.emo.v.lo.neu$z_val))`, p `r (printp(hi.emo.v.lo.neu$p.value))`, and high, Z = `r (printnum(hi.emo.v.hi.neu$z_val))`, p `r (printp(hi.emo.v.hi.neu$p.value))`, neutral loads. However, there was no discernable effect of load. That is, the comparisons between low and high load ratings for both emotional, Z = `r (printnum(lo.emo.v.hi.emo$z_val))`, p = `r (printp(lo.emo.v.hi.emo$p.value))`, and neutral, Z = `r (printnum(lo.neu.v.hi.neu$z_val))`, p = `r (printp(lo.neu.v.hi.neu$p.value))`, load ratings were not significantly different [^2].

``` {r plot figure 1, include = TRUE}
### summarize the data ###
friedman.data.summarized <- summarySE(friedman.data, measurevar="Percent Negative Ratings", groupvars = "Condition")

ggplot(friedman.data.summarized, aes(Condition, `Percent Negative Ratings`, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean") +
  geom_errorbar(aes(ymin=`Percent Negative Ratings`-se, ymax=`Percent Negative Ratings`+se), width=.1)
```

[^2]: These results are qualitatively the same when analyzing these data with a repeated measures ANOVA.

## Reaction times
```{r analyze RTs, include = FALSE}
## assess normality ###
 shapiro.test(data$lo.neu.sur_RTz)
 shapiro.test(data$hi.neu.sur_RT)
 shapiro.test(data$lo.emo.sur_RT)
 shapiro.test(data$hi.emo.sur_RT)

### force normality ###
RTz.long <- gather(data, key = Condition, value = RTz,
                   lo.neu.sur_RT,
                   hi.neu.sur_RT,
                   lo.emo.sur_RT,
                   hi.emo.sur_RT)

RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)

wide <- spread(RTz.long, key = Condition, value = RTz)
shapiro.test(wide$lo.emo.sur_RT)
### make factors ###
RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Low",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))

RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))

### make w/in subjs factors ###
RTz.long$subjID <- as.factor(RTz.long$subjID)

### traditional ANOVA ###
RTaov <- with(RTz.long,
                   aov(RTz ~ (Load * Type) +
                       Error(subjID / (Load * Type))), contrasts = contr.sum())
summary(RTaov)
RTaov <- tidy(RTaov)

# ### make long ###
# data.long <- gather(data, key = "Condition", value = "ReactionTime",
#                     lo.neu.sur_RT, hi.neu.sur_RT,
#                     lo.emo.sur_RT, hi.emo.sur_RT)
# 
# ### make factors ###
# data.long$Load <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Low",
#                          ifelse(data.long$Condition == "lo.emo.sur_RT", "Low",
#                                 ifelse(data.long$Condition == "hi.neu.sur_RT", "High",
#                                        ifelse(data.long$Condition == "hi.emo.sur_RT", "High", ""))))
# 
# data.long$Type <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Neutral",
#                          ifelse(data.long$Condition == "lo.emo.sur_RT", "Emotional",
#                                 ifelse(data.long$Condition == "hi.neu.sur_RT", "Neutral",
#                                        ifelse(data.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
# 
# ### make w/in subjs factors ###
# data.long$subjID <- as.factor(data.long$subjID)
# 
# ### traditional ANOVA ###
# RTaov <- with(data.long,
#                    aov(ReactionTime ~ (Load * Type) +
#                        Error(subjID / (Load * Type))), contrasts = contr.sum())
# summary(RTaov)
# RTaov <- tidy(RTaov)

# ### friedman's nonparametric ###
# friedman.RT.results <- friedman.test(ReactionTime ~ Condition|subjID, data = data.long)
# ### Follow up wilcoxon tests ###
# lo.emo.v.lo.neuRT <- wilcox.test(data$lo.emo.sur_RT, data$lo.neu.sur_RT, paired = TRUE, conf.int = TRUE)
# lo.emo.v.hi.neuRT <- wilcox.test(data$lo.emo.sur_RT, data$hi.neu.sur_RT, paired = TRUE, conf.int = TRUE)
# lo.emo.v.hi.emoRT <- wilcox.test(data$lo.emo.sur_RT, data$hi.emo.sur_RT, paired = TRUE, conf.int = TRUE)
# hi.emo.v.lo.neuRT <- wilcox.test(data$hi.emo.sur_RT, data$lo.neu.sur_RT, paired = TRUE, conf.int = TRUE)
# hi.emo.v.hi.neuRT <- wilcox.test(data$hi.emo.sur_RT, data$hi.neu.sur_RT, paired = TRUE, conf.int = TRUE)
# lo.neu.v.hi.neuRT <- wilcox.test(data$hi.neu.sur_RT, data$lo.neu.sur_RT, paired = TRUE, conf.int = TRUE)

# summary(friedman.RT.results)

```
To assses for normality, the data were first tested with Shapiro-Wilk's test. All conditions appeared to be sampled from normal distributions (p's > .08). A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs. There was a trend towards a main effect of type, F(`r (RTaov$df[which(RTaov$term == "Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Type")])`. However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons. There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = . One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = . All other comparisons were non-significant (p's > .

```{r plot RT data}
#data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars = "Condition")
#ggplot(data.long.summary, aes(Condition, `ReactionTime`, fill = as.factor(Condition))) +
 # geom_bar(stat = "summary", fun.y = "mean") +
#  geom_errorbar(aes(ymin=`ReactionTime`-se, ymax=`ReactionTime`+se), width=.1)
```

``` {r RT by ratings, include = TRUE}
# ### assess for normality ###
# shapiro.test(data$lo.neu.sur_n_RT) ## non-normal
# shapiro.test(data$lo.neu.sur_p_RT) ## normal
# shapiro.test(data$hi.neu.sur_n_RT) ## non-normal
# shapiro.test(data$hi.neu.sur_p_RT) ## normal
# shapiro.test(data$lo.emo.sur_n_RT) ## non-normal
# shapiro.test(data$lo.emo.sur_p_RT) ## non-normal
# shapiro.test(data$hi.emo.sur_n_RT) ## barely normal
# shapiro.test(data$hi.emo.sur_p_RT) ## non-normal
# 
# ### t-test for pos ratings vs. neg ratings
# lo.neu.RT.pvn <- wilcox.test(data$lo.neu.sur_n_RT, data$lo.neu.sur_p_RT, paired = TRUE)
# wilcox.test(data$hi.neu.sur_n_RT, data$hi.neu.sur_p_RT, paired = TRUE)
# wilcox.test(data$lo.emo.sur_n_RT, data$lo.emo.sur_p_RT, paired = TRUE)
# wilcox.test(data$hi.emo.sur_n_RT, data$hi.emo.sur_p_RT, paired = TRUE)
# 
# ### make long ###
# data.long <- gather(data, key = "Condition", value = "ReactionTime",
#                     lo.neu.sur_n_RT, hi.neu.sur_n_RT,
#                     lo.emo.sur_n_RT, hi.emo.sur_n_RT,
#                     lo.neu.sur_p_RT, hi.neu.sur_p_RT,
#                     lo.emo.sur_p_RT, hi.emo.sur_p_RT)
# data.long$Condition <- as.factor(data.long$Condition)
# 
# data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)
# 
# ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
#   geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
#   geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)

### force normality ###
RTz.long <- gather(data, key = Condition, value = RTz,
                   lo.neu.sur_n_RT, lo.neu.sur_p_RT,
                   hi.neu.sur_n_RT, hi.neu.sur_p_RT,
                   lo.emo.sur_n_RT, lo.emo.sur_p_RT,
                   hi.emo.sur_n_RT, hi.emo.sur_p_RT)

RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)

### back to wide ###
data2 <- spread(RTz.long, key = Condition, value = RTz)
### assess for normality ###
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_n_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_p_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_n_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_p_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_n_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_p_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_n_RT")])
shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_p_RT")])

RTz.long$Condition <- as.factor(RTz.long$Condition)

### make factors ###
RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_n_RT", "Low",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))

RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))

### make w/in subjs factors ###
data.long$subjID <- as.factor(data.long$subjID)

### traditional ANOVA ###
RTaov <- with(data.long,
                   aov(ReactionTime ~ (Load * Type) +
                       Error(subjID / (Load * Type))), contrasts = contr.sum())
summary(RTaov)
RTaov <- tidy(RTaov)

data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)

ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
  geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)

```
Next, we tested for reaciton time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition. Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs. This difference was significant *only* for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (`r printp(lo.neu.RT.pvn$p.value)`). All other comparisons were not significant (p's > .200). Further, this effect survived Bonferroni correction (p = `r printp(.05 / 4)`).

``` {r MAD}
###  MAD analyses ###
results.long <- gather(data, key = "Condition", value = "MAD",
                       lo.emo.sur_MAD, hi.emo.sur_MAD, lo.neu.sur_MAD, hi.neu.sur_MAD)
results.long$load <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Low",
                            ifelse(results.long$Condition == "lo.neu.sur_MAD", "Low", "High"))
results.long$type <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Emo",
                            ifelse(results.long$Condition == "hi.emo.sur_MAD", "Emo", "Neu"))

MAD.anova <- aov(MAD ~ load * type, data = results.long)
summary.aov(MAD.anova)

res.long.sum <- summarySE(results.long, measurevar="MAD", groupvars = "Condition")
ggplot(res.long.sum, aes(Condition, MAD, fill = as.factor(Condition))) +
  geom_bar(stat = "summary", fun.y = "mean") +
  geom_errorbar(aes(ymin=`MAD`-se, ymax=`MAD`+se), width=.1)

```

# Discussion
The effect of high vs. low load is still not apparent in these data, just like Mattek et al. 2016. An alternative explanation is that the high load manipulation is not sufficiently difficult to recruit the targeted cognitive resources; however, future work will be needed to better test this alternative.

Previous work has shown that more positive interpretations of surprised faces are related to slower RTs. Our working hypothesis suggests that this delayed reaction is a result of deliberation and slower, top-down cognitive processing. It is interesting to note that, at least in these data, there is no such difference observed between the neutral and emotional WM trials, *even though* the emotional WM trials are overall more negative. Future work should tease apart why this may be. For instance, ...

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-08-07 Manuscript/Manuscript.tex
Initial commit

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions},
            pdfauthor={Nicholas R. Harp~\& Maital Neta},
            pdfkeywords={ambiguity, working memory, bias},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions}
    \author{Nicholas R. Harp\textsuperscript{1}~\& Maital Neta\textsuperscript{1}}
    \date{}

\shorttitle{DOMAIN-SPECIFIC WORKING MEMORY AND SURPRISED EXPRESSIONS}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Nebraska-Lincoln}
\keywords{ambiguity, working memory, bias\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

\authornote{Nicholas R. Harp, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln
Maital Neta, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln

Correspondence concerning this article should be addressed to Nicholas R. Harp, Postal address. E-mail: \href{mailto:nharp@huskers.unl.edu}{\nolinkurl{nharp@huskers.unl.edu}}}

\abstract{
Individual differences in interpretations of emotional ambiguity are a useful tool for measuring affective biases.

While trait-like, these biases are also susceptible to experimental manipulations. In the present study, we capitalize on this malleability to expand on previous research suggesting that
subjective interpretations are stable independently of cognitive load.

We tested the effects of working memory loads containing either neutral or emotional content on concurrent interpretations of surprised facial expressions.

Here we show that interpretations of surprise are more negative during maintenance of working memory loads with emotional content compared to those with neutral content.

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.

}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world. In fact, facial expressions are seen across cultures ({\textbf{???}}) and some evidence suggests expressions are innate (cite). Often, facial expressions serve as a clear social signal, but this is not always the case. While a smile from a friend likely expresses a positive affective state, other cues are not so clear. For instance, a surprised facial expression could signal either a positive (e.g., winning the lottery) or negative (e.g., a snake in the woods) affective state. In the absence of a larger context, individuals differ in their tendency to interpret surprised facial expressions as either positive or negative. Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to both surprised faces and ambiguous scenes (Neta, Kelley, \& Whalen, 2013). This bias towards positive or negative interpretations is known as one's valence bias.
Interpreting facial expressions requires both bottom-up (e.g., perceptual input) and top-down (e.g., emotion regulation strategies) processes. A growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes, and that arriving at a positive interpretation requires additional, top-down regulatory processes. For example, participants reliably rate surprise as negative faster than positive (Neta \& Tong, 2016). In fact, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity ({\textbf{???}}). Perceptual input also contributes to valence bias. In one recent study, Neta and colleagues ({\textbf{???}}) showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions. In short,\\
Despite the trait-like nature of this bias (Neta, Norris, \& Whalen, 2009), valence bias may be shifted, at least temporarily, by a number of experimental manipulations. As mentioned above, simple manipulations like slowing response times will shift bias ({\textbf{???}}). Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor (Brown, Raio, \& Neta, 2017). Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock ({\textbf{???}}), suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.

Understanding the influences on decision making under ambiguous contexts sheds light on the mechanisms responsible for these individual differences. in the present study we aim to better understand how concurrent task demands (i.e., working memory load) may influence the cognitive resources used to arrive at more top-down driven interpetations of ambiguity, specifically in an emotional context.\\
Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces (Mattek, Whalen, Berkowitz, \& Freeman, 2016; Neta \& Tong, 2016).
The valence bias is trait-like (Neta et al., 2009) and generalizes to non-face stimuli (Neta et al., 2013); however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding (Brown et al., 2017; Neta \& Tong, 2016). Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology ({\textbf{???}}), at least in children. Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety ({\textbf{???}}).

Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks {[}; cite, cite{]}. Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli (Gruber, 2001). This effect holds up in the emotional domain; for example, the Stroop task (Stroop, 1935) has been modified by some researchers to include emotional stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample). Indeed, neuroimaging work supports the idea that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008).
Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference. Mattek and colleagues (2016) recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories. While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias. Given the task irrelevance of the numeric distractors in Mattek and colleagues' (2016) work, it follows that the resources required for interpreting ambiguity as positive (Neta et al., 2009) may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains. We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials. Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

58 subjects were recruited from the University of Nebraska-Lincoln. All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the local Institutional Review Board (Approval \#20141014670EP). The data from eight subjects were excluded due to technical difficulties or an error in the experiment script. This left 50 individuals in the final sample.

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{stimuli}{%
\subsubsection{Stimuli}\label{stimuli}}

The stimuli included faces taken from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets. The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly. The scenes were taken from the International Affective Picture System (Lang, Bradley, \& Cuthbert, 2008). A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices. The positive and negative images did not differ on arousal (Z = -0.23, p = 0.82). The scenes were organized into low (two images) and high (six images) cognitive load of either neutral or emotional (equal number of positive and negative) images (Figure 1).

\hypertarget{software}{%
\subsubsection{Software}\label{software}}

The task was completed in MouseTracker (Freeman \& Ambady, 2010) and participants used a mouse to click the appropriate response for the face ratings (i.e., \enquote{POSITIVE} or \enquote{NEGATIVE}) and the memory probe (i.e., \enquote{YES} or \enquote{NO}).

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Participants were randomly assigned to complete one of the task versions. The tasks included 144\footnote{Some versions of the task only included 142 trials due to a programming error.} trials split between working memory probe and face rating trials. On each trial, participants first viewed an image matrix of either neutral or emotional images, which the participants were instructed to remember for the duration of the trial. The image matrix was presented for four seconds and the images were swapped from low and high load matrices across versions of the task. After the image matrix a happy, angry, or surprised face appeared for one second and the participants rated the face by clicking on either the positive or negative response option. After the face rating, a single image probe appeared, and participants indicated whether or not the image probe was present in the previous image matrix.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 3.6.0; {\textbf{???}}) and the R-packages * \}dplyr* {[}@ \}R-dplyr{]}, \emph{broom} (Version 0.5.2; {\textbf{???}}), \emph{forcats} (Version 0.4.0; {\textbf{???}}), \emph{ggplot2} (Version 3.1.1; {\textbf{???}}), \emph{lattice} (Version 0.20.38; {\textbf{???}}), \emph{openxlsx} (Version 4.1.0; {\textbf{???}}), \emph{papaja} (Version 0.1.0.9842; {\textbf{???}}), \emph{plyr} (Version 1.8.4; @ \}R-dplyr; {\textbf{???}}), \emph{purrr} (Version 0.3.2; {\textbf{???}}), \emph{readr} (Version 1.3.1; {\textbf{???}}), \emph{readxl} (Version 1.3.1; {\textbf{???}}), \emph{Rmisc} (Version 1.5; {\textbf{???}}), \emph{stringr} (Version 1.4.0; {\textbf{???}}), \emph{tibble} (Version 2.1.3; {\textbf{???}}), \emph{tidyr} (Version 0.8.3.9000; {\textbf{???}}), and \emph{tidyverse} (Version 1.2.1; {\textbf{???}}) for all our analyses. Data preprocessing was completed in R using the mousetrap package ({\textbf{???}}). First, percent negative ratings were calculated for happy, angry, and surprised faces across all trial types, as well as a percent correct score for the memory probe trials. After, trials were screened for RT outliers. Any trials that were greater than three standard deviations from the mean were removed from the analyses. Additionally, we removed the preceding face rating trial for any incorrect memory probe trials, as these trials can be considered a manipulation failure.

Prior to completing the analyses, the data were assessed for normality using the Shapiro-Wilks test. Data that met the normality assumption were submitted to repeated measures ANOVA, while data that failed to meet this assumption was analyzed using non-parametric tests. We tested for differences in valence bias among the different working memory load conditions. Friedman's test was used to assess overall differences and pairwise comparisons were completed using Wilcoxon signed rank tests using Bonferroni correction. The same analysis strategy was also used to assess differences in reaction times, collapsed across both positive and negative interpretations of surprised facial expressions. Finally, we checked for differences between reaction times for both positive and negative ratings of surprise in each working memory load condition. Due to a large amount of missing data (almost 50\% of the subjects), as a result of some subjects only choosing the positive or negative response option in a given working memory load condition, we were unable to analyze these data with Friedman's test. Thus, we conducted a series of Wilcoxon signed rank tests for each of the four conditions with Bonferroni correction.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{subjective-ratings}{%
\subsection{Subjective ratings}\label{subjective-ratings}}

Distributions of ratings were first tested for normality using Shapiro-Wilk's test. The results of all four tests were highly significant (p's \textless{} .001), so non-parametric tests were used for data analysis. Friedman's test results showed significantly different distributions across the conditions \(\chi^{2}\)(3.00) = 27.41, p \textless{} .001. Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content. Low emotional load ratings were significantly more negative than low, Z = 3.31, p = .001, neutral and high, Z = 3.62, p \textless{} .001, neutral loads. The same was true for high emotional load ratings and low, Z = 4.52, p \textless{} .001, and high, Z = 3.72, p \textless{} .001, neutral loads. However, there was no discernable effect of load. That is, the comparisons between low and high load ratings for both emotional, Z = -1.10, p = .273, and neutral, Z = -0.03, p = .975, load ratings were not significantly different.\footnote{These results are qualitatively the same when analyzing these data with a repeated measures ANOVA.}

\includegraphics{Manuscript_files/figure-latex/plot figure 1-1.pdf}

\hypertarget{reaction-times}{%
\subsection{Reaction times}\label{reaction-times}}

To assses for normality, the data were first tested with Shapiro-Wilk's test. All conditions appeared to be sampled from normal distributions (p's \textgreater{} .08). A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs. There was a trend towards a main effect of type, F(1, 49) = 3.82, p = 0.06. However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons. There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = . One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = . All other comparisons were non-significant (p's \textgreater{} .

\includegraphics{Manuscript_files/figure-latex/plot RT data-1.pdf}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$lo.neu.sur_n_RT
## W = 0.92168, p-value = 0.003408
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$lo.neu.sur_p_RT
## W = 0.96281, p-value = 0.139
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$hi.neu.sur_n_RT
## W = 0.9405, p-value = 0.01547
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$hi.neu.sur_p_RT
## W = 0.98072, p-value = 0.6489
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$lo.emo.sur_n_RT
## W = 0.94444, p-value = 0.02027
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$lo.emo.sur_p_RT
## W = 0.90016, p-value = 0.002575
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$hi.emo.sur_n_RT
## W = 0.95402, p-value = 0.05001
\end{verbatim}

\begin{verbatim}
## 
##  Shapiro-Wilk normality test
## 
## data:  data$hi.emo.sur_p_RT
## W = 0.88408, p-value = 0.002496
\end{verbatim}

\begin{verbatim}
## 
##  Wilcoxon signed rank test
## 
## data:  data$hi.neu.sur_n_RT and data$hi.neu.sur_p_RT
## V = 604, p-value = 0.2076
## alternative hypothesis: true location shift is not equal to 0
\end{verbatim}

\begin{verbatim}
## 
##  Wilcoxon signed rank test
## 
## data:  data$lo.emo.sur_n_RT and data$lo.emo.sur_p_RT
## V = 392, p-value = 0.7634
## alternative hypothesis: true location shift is not equal to 0
\end{verbatim}

\begin{verbatim}
## 
##  Wilcoxon signed rank test
## 
## data:  data$hi.emo.sur_n_RT and data$hi.emo.sur_p_RT
## V = 260, p-value = 0.9485
## alternative hypothesis: true location shift is not equal to 0
\end{verbatim}

\includegraphics{Manuscript_files/figure-latex/RT by ratings-1.pdf}
Next, we tested for reaciton time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition. Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs. This difference was significant \emph{only} for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (.009). All other comparisons were not significant (p's \textgreater{} .200). Further, this effect survived Bonferroni correction (p = .012).

\begin{verbatim}
##              Df Sum Sq Mean Sq F value Pr(>F)  
## load          1  0.164 0.16398   5.118 0.0248 *
## type          1  0.002 0.00154   0.048 0.8265  
## load:type     1  0.087 0.08683   2.710 0.1013  
## Residuals   196  6.279 0.03204                 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\includegraphics{Manuscript_files/figure-latex/MAD-1.pdf}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The effect of high vs.~low load is still not apparent in these data, just like Mattek et al.~2016. An alternative explanation is that the high load manipulation is not sufficiently difficult to recruit the targeted cognitive resources; however, future work will be needed to better test this alternative.

Previous work has shown that more positive interpretations of surprised faces are related to slower RTs. Our working hypothesis suggests that this delayed reaction is a result of deliberation and slower, top-down cognitive processing. It is interesting to note that, at least in these data, there is no such difference observed between the neutral and emotional WM trials, \emph{even though} the emotional WM trials are overall more negative. Future work should tease apart why this may be. For instance, \ldots{}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-brown_cortisol_2017}{}%
Brown, C. C., Raio, C. M., \& Neta, M. (2017). Cortisol responses enhance negative valence perception for ambiguous facial expressions. \emph{Scientific Reports}, \emph{7}(1), 15107. doi:\href{https://doi.org/10.1038/s41598-017-14846-3}{10.1038/s41598-017-14846-3}

\leavevmode\hypertarget{ref-egner_dissociable_2008}{}%
Egner, T., Etkin, A., Gale, S., \& Hirsch, J. (2008). Dissociable neural systems resolve conflict from emotional versus nonemotional distracters. \emph{Cerebral Cortex (New York, N.Y.: 1991)}, \emph{18}(6), 1475--1484. doi:\href{https://doi.org/10.1093/cercor/bhm179}{10.1093/cercor/bhm179}

\leavevmode\hypertarget{ref-freeman_mousetracker:_2010}{}%
Freeman, J. B., \& Ambady, N. (2010). MouseTracker: Software for studying real-time mental processing using a computer mouse-tracking method. \emph{Behavior Research Methods}, \emph{42}(1), 226--241. doi:\href{https://doi.org/10.3758/BRM.42.1.226}{10.3758/BRM.42.1.226}

\leavevmode\hypertarget{ref-gruber_effects_2001}{}%
Gruber, O. (2001). Effects of domain-specific interference on brain activation associated with verbal working memory task performance. \emph{Cerebral Cortex (New York, N.Y.: 1991)}, \emph{11}(11), 1047--1055. doi:\href{https://doi.org/10.1093/cercor/11.11.1047}{10.1093/cercor/11.11.1047}

\leavevmode\hypertarget{ref-lang_international_2008}{}%
Lang, P., Bradley, M. M., \& Cuthbert, B. N. (2008). International affective picture system (IAPS): Affective ratings of pictures and instruction manual., Technical Report A--8. University of Florida, Gainesville, FL.

\leavevmode\hypertarget{ref-lundqvist_karolinska_1998}{}%
Lundqvist, D., Flykt, A., \& Öhman, A. (1998). The karolinska directed emotional faces---KDEF (CD ROM)., Stockholm: Karolinska Institute, Departmentof Clinical Neuroscience, PsychologySection.

\leavevmode\hypertarget{ref-mattek_differential_2016}{}%
Mattek, A. M., Whalen, P. J., Berkowitz, J. L., \& Freeman, J. B. (2016). Differential effects of cognitive load on subjective versus motor responses to ambiguously valenced facial expressions. \emph{Emotion}, \emph{16}(6), 929--936. doi:\href{https://doi.org/10.1037/emo0000148}{10.1037/emo0000148}

\leavevmode\hypertarget{ref-neta_neural_2013}{}%
Neta, M., Kelley, W. M., \& Whalen, P. J. (2013). Neural responses to ambiguity involve domain-general and domain-specific emotion processing systems. \emph{Journal of Cognitive Neuroscience}, \emph{25}(4), 547--557. doi:\href{https://doi.org/10.1162/jocn_a_00363}{10.1162/jocn\_a\_00363}

\leavevmode\hypertarget{ref-neta_corrugator_2009}{}%
Neta, M., Norris, C. J., \& Whalen, P. J. (2009). Corrugator muscle responses are associated with individual differences in positivity-negativity bias. \emph{Emotion (Washington, D.C.)}, \emph{9}(5), 640--648. doi:\href{https://doi.org/10.1037/a0016819}{10.1037/a0016819}

\leavevmode\hypertarget{ref-neta_dont_2016}{}%
Neta, M., \& Tong, T. T. (2016). Don't like what you see? Give it time: Longer reaction times associated with increased positive affect. \emph{Emotion (Washington, D.C.)}, \emph{16}(5), 730--739. doi:\href{https://doi.org/10.1037/emo0000181}{10.1037/emo0000181}

\leavevmode\hypertarget{ref-stroop_studies_1935}{}%
Stroop, J. R. (1935). Studies of interference in serial verbal reactions. \emph{Journal of Experimental Psychology}, \emph{18}(6), 643--662. doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}

\leavevmode\hypertarget{ref-tottenham_nimstim_2009}{}%
Tottenham, N., Tanaka, J. W., Leon, A. C., McCarry, T., Nurse, M., Hare, T. A., \ldots{} Nelson, C. (2009). The NimStim set of facial expressions: Judgments from untrained research participants. \emph{Psychiatry Research}, \emph{168}(3), 242--249. doi:\href{https://doi.org/10.1016/j.psychres.2008.05.006}{10.1016/j.psychres.2008.05.006}

\leavevmode\hypertarget{ref-whalen_emotional_2006}{}%
Whalen, P. J., Bush, G., Shin, L. M., \& Rauch, S. L. (2006). The emotional counting stroop: A task for assessing emotional interference during brain imaging. \emph{Nature Protocols}, \emph{1}(1), 293--296. doi:\href{https://doi.org/10.1038/nprot.2006.45}{10.1038/nprot.2006.45}

\endgroup

\end{document}

### 2019-08-07 Data_Cleaning.R

@@ -1,0 +1,1786 @@
+### set working directory to MouseTrap Demo folder ###
+setwd("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses")
+
+if (!require("processx")) install.packages("processx")
+
+{### install MouseTrap... This only needs to be done once. ###
+### ... and readbulk for applying to a set of files ###
+#install.packages("mousetrap")
+#install.packages("readbulk")
+#install.packages("here")
+#install.packages("foreach")
+#install.packages("tidyverse")
+#install.packages("plyr")
+#install.packages("utils")
+#install.packages("stats")
+#install.packages("pracma")
+#install.packages("tidyr")
+#install.packages("magrittr")
+#install.packages("graphics")
+#install.packages("grDevices")
+#install.packages("ggplot2")
+#install.packages("scales")
+#install.packages("psych")
+#install.packages("Rcpp")
+#install.packages("diptest")
+#install.packages("RColorBrewer")
+#install.packages("cstab")
+#install.packages("fastcluster")
+#install.packages("parallel")
+#install.packages("fields")
+#install.packages("orca")
+#install.packages("plotly")
+#install.packages("weights")
+}
+### load the packages... This needs to be done every time. ###
+{library(mousetrap)
+library(foreach)
+library(tidyverse)
+library(readbulk)
+library(plyr)
+library(utils)
+library(stats)
+library(pracma)
+library(tidyr)
+library(magrittr)
+library(graphics)
+library(grDevices)
+library(ggplot2)
+library(scales)
+library(psych)
+library(Rcpp)
+library(diptest)
+library(RColorBrewer)
+library(cstab)
+library(fastcluster)
+library(parallel)
+library(fields)
+library(readxl)
+library(yarrr)
+library(weights)}
+
+{
+session1files <- list.files(path = "/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/Data/Session1", 
+                            pattern = "*.mt", full.names = TRUE, recursive = FALSE)
+session1.data <- read_bulk("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/Data/Session1/", fun = read_mt, 
+                           extension = ".mt")
+session1.data <- mt_import_wide(session1.data)
+foreach(file = session1files) %do% {
[…]

### 2019-08-07 Image_Probe_Analysis.R

@@ -1,0 +1,13 @@
+### remove bad sub ###
+bound.data <- bound.data[-38,]
+bound.data$subjID <- as.factor(bound.data$subjID)
+long.data <- gather(bound.data, Condition, Correct,
+                    mem.cor.yes, mem.cor.no, emo.mem, neu.mem,
+                    lo.mem, hi.mem)
+pirateplot(Correct ~ Condition, data = long.data)
+
+t.test(bound.data$mem.cor.yes, bound.data$mem.cor.no, paired = TRUE)
+
+t.test(bound.data$emo.mem, bound.data$neu.mem, paired = TRUE)
+
+t.test(bound.data$hi.mem, bound.data$lo.mem, paired = TRUE)

### 2019-08-07 MeetwCal.R

@@ -1,0 +1,161 @@
+library(dplyr)
+library(ggpubr)
+
+### checking normality ###
+
+### surprise ###
+shapiro.test(MT.data.rating.table$lo.emo.sur_rate)
+ggdensity(MT.data.rating.table$lo.emo.sur_rate)
+ggqqplot(MT.data.rating.table$lo.emo.sur_rate)
+
+shapiro.test(MT.data.rating.table$hi.emo.sur_rate)
+ggdensity(MT.data.rating.table$hi.emo.sur_rate)
+ggqqplot(MT.data.rating.table$hi.emo.sur_rate)
+
+shapiro.test(MT.data.rating.table$lo.neu.sur_rate)
+ggdensity(MT.data.rating.table$lo.neu.sur_rate)
+ggqqplot(MT.data.rating.table$lo.neu.sur_rate)
+
+shapiro.test(MT.data.rating.table$hi.neu.sur_rate)
+ggdensity(MT.data.rating.table$hi.neu.sur_rate)
+ggqqplot(MT.data.rating.table$hi.neu.sur_rate)
+
+### happy ###
+shapiro.test(MT.data.rating.table$lo.emo.hap_rate)
+ggdensity(MT.data.rating.table$lo.emo.hap_rate)
+ggqqplot(MT.data.rating.table$lo.emo.hap_rate)
+
+shapiro.test(MT.data.rating.table$hi.emo.hap_rate)
+ggdensity(MT.data.rating.table$hi.emo.hap_rate)
+ggqqplot(MT.data.rating.table$hi.emo.hap_rate)
+
+shapiro.test(MT.data.rating.table$lo.neu.hap_rate)
+ggdensity(MT.data.rating.table$lo.neu.hap_rate)
+ggqqplot(MT.data.rating.table$lo.neu.hap_rate)
+
+shapiro.test(MT.data.rating.table$hi.neu.hap_rate)
+ggdensity(MT.data.rating.table$hi.neu.hap_rate)
+ggqqplot(MT.data.rating.table$hi.neu.hap_rate)
+
+### angry ###
+shapiro.test(MT.data.rating.table$lo.emo.ang_rate)
+ggdensity(MT.data.rating.table$lo.emo.ang_rate)
[…]

### 2019-08-07 Rating_Analysis.R

@@ -1,0 +1,198 @@
+setwd("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses")
+#install.packages("BANOVA")
+library(BANOVA)
+library(tidyr)
+library(dplyr)
+library(yarrr)
+library(emmeans)
+library(BayesFactor)
+library(readr)
+
+bound.data <- read_csv("Final_Data_20190324.csv")
+bound.data <- bound.data[,-1]
+bound.data$subjID <- factor(bound.data$subjID)
+### remove bad subject ###
+t.test(MT.data.rating.table$emo.mem, MT.data.rating.table$neu.mem, paired = TRUE)
+mean(MT.data.rating.table$neu.mem)
+library(ggpubr)
+shapiro.test(MT.data.rating.table$lo.neu.sur_rate)
+
+rate.data_long <- gather(MT.data.rating.table, key = condition, value = "Percent Negative",  
+                         lo.emo.ang_rate,hi.emo.ang_rate,lo.neu.ang_rate,hi.neu.ang_rate,
+                         lo.emo.hap_rate,hi.emo.hap_rate,lo.neu.hap_rate,hi.neu.hap_rate,
+                         lo.emo.sur_rate,hi.emo.sur_rate,lo.neu.sur_rate,hi.neu.sur_rate)
+mem.data_long <- gather(MT.data.rating.table, key = Memory, value = "Accuracy",  
+                         lo.mem, hi.mem)
+### effect of load (Low = 2images, High = 6images ###
+rate.data_long$load <- ifelse(rate.data_long$condition %in% 
+                                c("lo.emo.ang_rate","lo.neu.ang_rate",
+                                  "lo.emo.hap_rate","lo.neu.hap_rate",
+                                  "lo.emo.sur_rate","lo.neu.sur_rate"), "Low",
+                              ifelse(rate.data_long$condition %in%
+                                       c("hi.emo.ang_rate","hi.neu.ang_rate",
+                                         "hi.emo.hap_rate","hi.neu.hap_rate",
+                                         "hi.emo.sur_rate","hi.neu.sur_rate"), "High",""))
+
+### effect of valence ###
+rate.data_long$type <- ifelse(rate.data_long$condition %in% 
+                               c("lo.emo.ang_rate","hi.emo.ang_rate", 
+                                 "lo.emo.hap_rate", "hi.emo.hap_rate",
[…]

### 2019-08-07 survey_score-WM.R

@@ -1,0 +1,577 @@
+### set wd ###
+### make this your working directory (file path) ###
+setwd("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/")
+
+### load packages ###
+if(!require(tidyverse)){
+  install.packages("tidyverse")
+  library(tidyverse)
+}
+if(!require(psych)){
+  install.packages("psych")
+  library(psych)
+}
+if(!require(dplyr)){
+  install.packages("dplyr")
+  library(dplyr)
+}
+### import data ###
+data <- read.csv("data/qualtrics_data_20190607.csv")
+
+### preview data (optional) ###
+# View(data)
+
+### remove junk rows ###
+### typically row 1 and 2 in qualtrics csv files ###
+data <- data[-(c(1,2)),]
+
+### reset row names ###
+rownames(data) <- NULL
+
+### create column values ###
+firstcol <- "erq_1"
+lastcol <- "erq_10"
+ERQ.data <- select(data, firstcol:lastcol)
+
+
+### convert choice text to numeric ###
+for(i in 1:ncol(ERQ.data)) {
+  ERQ.data[,i] <- recode(ERQ.data[,i], 
+                         "1-Strongly disagree" = 1,
+                         "2" = 2, "3" = 3, "4-Neutral" = 4,
+                         "5" = 5, "6" = 6, "7-Strongly agree" = 7)
+}
+
+### add items for participant scores and create column in survey.data ###
+ERQ.data$ERQ_CR <-  (rowSums(ERQ.data[,c(1,3,5,7,8,10)], 
+                             na.rm = FALSE)  / 6 )
+
+ERQ.data$ERQ_ES <- ( rowSums(ERQ.data[,c(2,4,6,9)], 
+                             na.rm = FALSE) / 4 )
+
+
+### create NEOFFI data frame ###
+### create column values ###
+firstcol <- "NEO_only_1"
+lastcol <- "NEO_only_60"
+NEO.data <- select(data, firstcol:lastcol)
+
+
+### convert choice text to numeric ###
[…]

### 2019-08-07 wilcox_test.R

@@ -1,0 +1,438 @@
+#  File src/library/stats/R/wilcox_test.R
+#  Part of the R package, https://www.R-project.org
+#
+#  Copyright (C) 1995-2015 The R Core Team
+#
+#  This program is free software; you can redistribute it and/or modify
+#  it under the terms of the GNU General Public License as published by
+#  the Free Software Foundation; either version 2 of the License, or
+#  (at your option) any later version.
+#
+#  This program is distributed in the hope that it will be useful,
+#  but WITHOUT ANY WARRANTY; without even the implied warranty of
+#  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#  GNU General Public License for more details.
+#
+#  A copy of the GNU General Public License is available at
+#  https://www.R-project.org/Licenses/
+
+wilcox_test <- function(x, ...) UseMethod("wilcox_test")
+
+wilcox_test.default <-
+  function(x, y = NULL, alternative = c("two.sided", "less", "greater"),
+           mu = 0, paired = FALSE, exact = NULL, correct = TRUE,
+           conf.int = FALSE, conf.level = 0.95, ...)
+  {
+    alternative <- match.arg(alternative)
+    if(!missing(mu) && ((length(mu) > 1L) || !is.finite(mu)))
+      stop("'mu' must be a single number")
+    if(conf.int) {
+      if(!((length(conf.level) == 1L)
+           && is.finite(conf.level)
+           && (conf.level > 0)
+           && (conf.level < 1)))
+        stop("'conf.level' must be a single number between 0 and 1")
+    }
+    
+    if(!is.numeric(x)) stop("'x' must be numeric")
+    if(!is.null(y)) {
+      if(!is.numeric(y)) stop("'y' must be numeric")
+      DNAME <- paste(deparse(substitute(x)), "and",
+                     deparse(substitute(y)))
+      if(paired) {
+        if(length(x) != length(y))
+          stop("'x' and 'y' must have the same length")
+        OK <- complete.cases(x, y)
+        x <- x[OK] - y[OK]
+        y <- NULL
+      }
+      else {
+        x <- x[is.finite(x)]
+        y <- y[is.finite(y)]
+      }
+    } else {
+      DNAME <- deparse(substitute(x))
+      if(paired)
+        stop("'y' is missing for paired test")
+      x <- x[is.finite(x)]
+    }
+    
+    if(length(x) < 1L)
[…]

### 2019-08-07 Manuscript/Manuscript.Rmd
Updated manuscript, updated cleaning
Removing ridiculous variable creation in the cleaning script. Implementing "which" statements.

Manuscript runs, but is still messy.

@@
 ### import z score updated function ###
-source("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/wilcox_test.R")
+source("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/wilcox_test.R")
 ### code edits taken from : https://stats.stackexchange.com/questions/306841/z-score-on-wilcoxon-signed-ranks-test ###
@@
 ### load necessary libraries ###
-library(readxl)
-library(tidyverse)
-library(openxlsx)
-library(Rmisc)
-library(broom)
+suppressPackageStartupMessages(library(readxl)) 
+suppressPackageStartupMessages(library(tidyverse))
+suppressPackageStartupMessages(library(openxlsx))
+suppressPackageStartupMessages(library(Rmisc))
+suppressPackageStartupMessages(library(broom))
 ```
@@
 ``` {r stimulus_t.test, include = FALSE}
-stim.data <- read.xlsx("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/IAPS_Stim_List.xlsx")
+stim.data <- read.xlsx("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/IAPS_Stim_List.xlsx")
 shapiro.test(subset(stim.data, Condition == "POS")$Aro_Mn)
@@
 ```{r import data and analyze ratings, include = FALSE, echo = TRUE}
-data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/Final.Data.csv_2019-08-01_12-38-57.csv")
+data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-01_12-38-57.csv")
 ### remove psych disorders ### Ask maital?
@@
 ### assess normality ###
-shapiro.test(data$lo.neu.sur_rate)
-shapiro.test(data$hi.neu.sur_rate)
-shapiro.test(data$lo.emo.sur_rate)
-shapiro.test(data$hi.emo.sur_rate)
+shapiro.test(data$lo.neu.sur_rate) # non-normal
+shapiro.test(data$hi.neu.sur_rate) # non-normal
+shapiro.test(data$lo.emo.sur_rate) # non-normal
+shapiro.test(data$hi.emo.sur_rate) # non-normal
 
@@
 shapiro.test(data$lo.neu.sur_RTz)
- shapiro.test(data$hi.neu.sur_RT)
- shapiro.test(data$lo.emo.sur_RT)
- shapiro.test(data$hi.emo.sur_RT)
+shapiro.test(data$hi.neu.sur_RTz)
+shapiro.test(data$lo.emo.sur_RTz)
+shapiro.test(data$hi.emo.sur_RTz)
 
@@
 RTz.long <- gather(data, key = Condition, value = RTz,
-                   lo.neu.sur_RT,
-                   hi.neu.sur_RT,
-                   lo.emo.sur_RT,
-                   hi.emo.sur_RT)
+                   lo.neu.sur_RTz,
+                   hi.neu.sur_RTz,
+                   lo.emo.sur_RTz,
+                   hi.emo.sur_RTz)
 
-RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)
+### run Friedman's test and store results ###
+RTz.friedman <- friedman.test(RTz ~ Condition|subjID, data = RTz.long)
+lo.emo.v.lo.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+lo.emo.v.hi.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+lo.emo.v.hi.emo.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.emo.sur_RTz, paired = TRUE, conf.int = TRUE)
+hi.emo.v.lo.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+hi.emo.v.hi.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+lo.neu.v.hi.neu.RTz <- wilcox_test(data$hi.neu.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
 
-wide <- spread(RTz.long, key = Condition, value = RTz)
-shapiro.test(wide$lo.emo.sur_RT)
+# RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)
+
+# wide <- spread(RTz.long, key = Condition, value = RTz)
+# hapiro.test(wide$lo.emo.sur_RT)
 ### make factors ###
-RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Low",
-                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
-                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
-                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))
+RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Low",
+                         ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Low",
+                                ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "High",
+                                       ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "High", ""))))
 
-RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
-                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
-                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
-                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
+RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Neutral",
+                         ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Emotional",
+                                ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "Neutral",
+                                       ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "Emotional", ""))))
 
@@
 ```
+To assess for normality, the data were first tested with Shapiro-Wilk's test.
+Two conditions did not appear to be sampled from normal distributions, so non-parametric tests were used.
+Overall, there was a trending difference across the four conditions, $\chi^{2}$(`r (printnum(RTz.friedman$parameter))`) = `r printnum(RTz.friedman$statistic)`, p `r printp(RTz.friedman$p.value)`.
+Wilcoxon signed rank tests were used to assess post-hoc comparisons and Bonferroni corrected p-value = `r printnum(.05 / 6)`.
+While none of the post-hoc comparisons reached the adjusted significance level, there was a trending difference between emotional and neutral RTs in the high load condition, Z = `r printnum(hi.emo.v.hi.neu.RTz$z_val)`, p = `r printp(hi.emo.v.hi.neu.RTz$p.value)`, such that high emotional WM loads had slower RTs.
+Two other comparisons were trending for traditional levels of significance.
+Low emotional WM loads tended to take marginally longer than high neutral WM loads, Z = `r printnum(lo.emo.v.hi.neu.RTz$z_val)`, p = `r printp(lo.emo.v.hi.neu.RTz$p.value)`, and low neutral WM loads took marginally longer than high neutral WM laods, Z = `r printnum(lo.neu.v.hi.neu.RTz$z_val)`, p = `r printnum(lo.neu.v.hi.neu.RTz$p.value)`.
+All other comparisons were not significant.
+<!-- IF WE USE RAW RTS, USE THIS TEXT
 To assses for normality, the data were first tested with Shapiro-Wilk's test.
@@
 All other comparisons were non-significant (p's > .
+-->
 
-```{r plot RT data}
-#data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars = "Condition")
-#ggplot(data.long.summary, aes(Condition, `ReactionTime`, fill = as.factor(Condition))) +
- # geom_bar(stat = "summary", fun.y = "mean") +
-#  geom_errorbar(aes(ymin=`ReactionTime`-se, ymax=`ReactionTime`+se), width=.1)
+```{r plot RT data, include = TRUE}
+ggplot(RTz.long, aes(Condition, `RTz`, fill = as.factor(Condition))) +
+  geom_bar(stat = "summary", fun.y = "mean") +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
 ```
 
-``` {r RT by ratings, include = TRUE}
-# ### assess for normality ###
-# shapiro.test(data$lo.neu.sur_n_RT) ## non-normal
-# shapiro.test(data$lo.neu.sur_p_RT) ## normal
-# shapiro.test(data$hi.neu.sur_n_RT) ## non-normal
-# shapiro.test(data$hi.neu.sur_p_RT) ## normal
-# shapiro.test(data$lo.emo.sur_n_RT) ## non-normal
-# shapiro.test(data$lo.emo.sur_p_RT) ## non-normal
-# shapiro.test(data$hi.emo.sur_n_RT) ## barely normal
-# shapiro.test(data$hi.emo.sur_p_RT) ## non-normal
-# 
-# ### t-test for pos ratings vs. neg ratings
-# lo.neu.RT.pvn <- wilcox.test(data$lo.neu.sur_n_RT, data$lo.neu.sur_p_RT, paired = TRUE)
-# wilcox.test(data$hi.neu.sur_n_RT, data$hi.neu.sur_p_RT, paired = TRUE)
-# wilcox.test(data$lo.emo.sur_n_RT, data$lo.emo.sur_p_RT, paired = TRUE)
-# wilcox.test(data$hi.emo.sur_n_RT, data$hi.emo.sur_p_RT, paired = TRUE)
-# 
-# ### make long ###
-# data.long <- gather(data, key = "Condition", value = "ReactionTime",
-#                     lo.neu.sur_n_RT, hi.neu.sur_n_RT,
-#                     lo.emo.sur_n_RT, hi.emo.sur_n_RT,
-#                     lo.neu.sur_p_RT, hi.neu.sur_p_RT,
-#                     lo.emo.sur_p_RT, hi.emo.sur_p_RT)
-# data.long$Condition <- as.factor(data.long$Condition)
-# 
-# data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)
-# 
-# ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
-#   geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-#   geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)
+``` {r RT by ratings, include = FALSE}
+### assess for normality ###
+shapiro.test(data$lo.neu.sur_n_RT) ## non-normal
+shapiro.test(data$lo.neu.sur_p_RT) ## normal
+shapiro.test(data$hi.neu.sur_n_RT) ## non-normal
+shapiro.test(data$hi.neu.sur_p_RT) ## normal
+shapiro.test(data$lo.emo.sur_n_RT) ## non-normal
+shapiro.test(data$lo.emo.sur_p_RT) ## non-normal
+shapiro.test(data$hi.emo.sur_n_RT) ## barely normal
+shapiro.test(data$hi.emo.sur_p_RT) ## non-normal
 
-### force normality ###
-RTz.long <- gather(data, key = Condition, value = RTz,
-                   lo.neu.sur_n_RT, lo.neu.sur_p_RT,
-                   hi.neu.sur_n_RT, hi.neu.sur_p_RT,
-                   lo.emo.sur_n_RT, lo.emo.sur_p_RT,
-                   hi.emo.sur_n_RT, hi.emo.sur_p_RT)
+### t-test for pos ratings vs. neg ratings
+lo.neu.RT.pvn <- wilcox.test(data$lo.neu.sur_n_RT, data$lo.neu.sur_p_RT, paired = TRUE)
+wilcox.test(data$hi.neu.sur_n_RT, data$hi.neu.sur_p_RT, paired = TRUE)
+wilcox.test(data$lo.emo.sur_n_RT, data$lo.emo.sur_p_RT, paired = TRUE)
+wilcox.test(data$hi.emo.sur_n_RT, data$hi.emo.sur_p_RT, paired = TRUE)
 
-RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)
-
-### back to wide ###
-data2 <- spread(RTz.long, key = Condition, value = RTz)
-### assess for normality ###
-shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_n_RT")])
-shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_p_RT")])
-shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_n_RT")])
-shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_p_RT")])
-shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_n_RT")])
-shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_p_RT")])
-shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_n_RT")])
-shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_p_RT")])
-
-RTz.long$Condition <- as.factor(RTz.long$Condition)
-
-### make factors ###
-RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_n_RT", "Low",
-                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
-                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
-                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))
-
-RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
-                         ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
-                                ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
-                                       ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
-
-### make w/in subjs factors ###
-data.long$subjID <- as.factor(data.long$subjID)
-
-### traditional ANOVA ###
-RTaov <- with(data.long,
-                   aov(ReactionTime ~ (Load * Type) +
-                       Error(subjID / (Load * Type))), contrasts = contr.sum())
-summary(RTaov)
-RTaov <- tidy(RTaov)
+### make long ###
+data.long <- gather(data, key = "Condition", value = "ReactionTime",
+                    lo.neu.sur_n_RT, hi.neu.sur_n_RT,
+                    lo.emo.sur_n_RT, hi.emo.sur_n_RT,
+                    lo.neu.sur_p_RT, hi.neu.sur_p_RT,
+                    lo.emo.sur_p_RT, hi.emo.sur_p_RT)
+data.long$Condition <- as.factor(data.long$Condition)
 
@@
   geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)
+
+# ### force normality ###
+# RTz.long <- gather(data, key = Condition, value = RTz,
+#                    lo.neu.sur_n_RT, lo.neu.sur_p_RT,
+#                    hi.neu.sur_n_RT, hi.neu.sur_p_RT,
+#                    lo.emo.sur_n_RT, lo.emo.sur_p_RT,
+#                    hi.emo.sur_n_RT, hi.emo.sur_p_RT)
+# 
+# ### back to wide ###
+# data2 <- spread(RTz.long, key = Condition, value = RTz)
+# ### assess for normality ###
+# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_n_RT")])
+# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_p_RT")])
+# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_n_RT")])
+# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_p_RT")])
+# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_n_RT")])
+# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_p_RT")])
+# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_n_RT")])
+# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_p_RT")])
+# 
+# RTz.long$Condition <- as.factor(RTz.long$Condition)
+# 
+# ### make factors ###
+# RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_n_RT", "Low",
+#                          ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
+#                                 ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
+#                                        ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))
+# 
+# RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
+#                          ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
+#                                 ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
+#                                        ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
+# 
+# ### make w/in subjs factors ###
+# data.long$subjID <- as.factor(data.long$subjID)
+# 
+# ### traditional ANOVA ###
+# RTaov <- with(data.long,
+#                    aov(ReactionTime ~ (Load * Type) +
+#                        Error(subjID / (Load * Type))), contrasts = contr.sum())
+# summary(RTaov)
+# RTaov <- tidy(RTaov)
+# 
+# 
+# 
+# 
+# data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)
+
+# ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
+#   geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
+#   geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)
 
@@
 
-``` {r MAD}
+``` {r MAD, include = FALSE}
 ###  MAD analyses ###
@@
 res.long.sum <- summarySE(results.long, measurevar="MAD", groupvars = "Condition")
+```
+
+``` {r MAD plot, include = TRUE}
 ggplot(res.long.sum, aes(Condition, MAD, fill = as.factor(Condition))) +
@@
   geom_errorbar(aes(ymin=`MAD`-se, ymax=`MAD`+se), width=.1)
-
 ```
+Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
 

### 2019-08-07 Manuscript/Manuscript.tex
Updated manuscript, updated cleaning
Removing ridiculous variable creation in the cleaning script. Implementing "which" statements.

Manuscript runs, but is still messy.

@@
 
-To assses for normality, the data were first tested with Shapiro-Wilk's test.
-All conditions appeared to be sampled from normal distributions (p's \textgreater{} .08).
-A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs.
-There was a trend towards a main effect of type, F(1, 49) = 3.82, p = 0.06.
-However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons.
-There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = .
-One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = .
-All other comparisons were non-significant (p's \textgreater{} .
+To assess for normality, the data were first tested with Shapiro-Wilk's test.
+Two conditions did not appear to be sampled from normal distributions, so non-parametric tests were used.
+Overall, there was a trending difference across the four conditions, \(\chi^{2}\)(3.00) = 7.15, p .067.
+Wilcoxon signed rank tests were used to assess post-hoc comparisons and Bonferroni corrected p-value = 0.01.
+While none of the post-hoc comparisons reached the adjusted significance level, there was a trending difference between emotional and neutral RTs in the high load condition, Z = 2.51, p = .012, such that high emotional WM loads had slower RTs.
+Two other comparisons were trending for traditional levels of significance.
+Low emotional WM loads tended to take marginally longer than high neutral WM loads, Z = 1.96, p = .050, and low neutral WM loads took marginally longer than high neutral WM laods, Z = -1.75, p = 0.08.
+All other comparisons were not significant.
 
@@
 
-\begin{verbatim}
-## 
-##  Shapiro-Wilk normality test
-## 
-## data:  data$lo.neu.sur_n_RT
-## W = 0.92168, p-value = 0.003408
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Shapiro-Wilk normality test
-## 
-## data:  data$lo.neu.sur_p_RT
-## W = 0.96281, p-value = 0.139
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Shapiro-Wilk normality test
-## 
-## data:  data$hi.neu.sur_n_RT
-## W = 0.9405, p-value = 0.01547
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Shapiro-Wilk normality test
-## 
-## data:  data$hi.neu.sur_p_RT
-## W = 0.98072, p-value = 0.6489
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Shapiro-Wilk normality test
-## 
-## data:  data$lo.emo.sur_n_RT
-## W = 0.94444, p-value = 0.02027
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Shapiro-Wilk normality test
-## 
-## data:  data$lo.emo.sur_p_RT
-## W = 0.90016, p-value = 0.002575
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Shapiro-Wilk normality test
-## 
-## data:  data$hi.emo.sur_n_RT
-## W = 0.95402, p-value = 0.05001
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Shapiro-Wilk normality test
-## 
-## data:  data$hi.emo.sur_p_RT
-## W = 0.88408, p-value = 0.002496
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Wilcoxon signed rank test
-## 
-## data:  data$hi.neu.sur_n_RT and data$hi.neu.sur_p_RT
-## V = 604, p-value = 0.2076
-## alternative hypothesis: true location shift is not equal to 0
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Wilcoxon signed rank test
-## 
-## data:  data$lo.emo.sur_n_RT and data$lo.emo.sur_p_RT
-## V = 392, p-value = 0.7634
-## alternative hypothesis: true location shift is not equal to 0
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##  Wilcoxon signed rank test
-## 
-## data:  data$hi.emo.sur_n_RT and data$hi.emo.sur_p_RT
-## V = 260, p-value = 0.9485
-## alternative hypothesis: true location shift is not equal to 0
-\end{verbatim}
-
-\includegraphics{Manuscript_files/figure-latex/RT by ratings-1.pdf}
 Next, we tested for reaciton time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition.
@@
 ##              Df Sum Sq Mean Sq F value Pr(>F)  
-## load          1  0.164 0.16398   5.118 0.0248 *
-## type          1  0.002 0.00154   0.048 0.8265  
-## load:type     1  0.087 0.08683   2.710 0.1013  
-## Residuals   196  6.279 0.03204                 
+## load          1  0.257 0.25709   4.599 0.0332 *
+## type          1  0.002 0.00230   0.041 0.8394  
+## load:type     1  0.001 0.00061   0.011 0.9170  
+## Residuals   196 10.956 0.05590                 
 ## ---

### 2019-08-07 Data_Cleaning.R

@@ -1,5 +1,5 @@
 ### set working directory to MouseTrap Demo folder ###
-setwd("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses")
+setwd("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads")
 
 if (!require("processx")) install.packages("processx")
 
@@ -33,31 +33,31 @@ if (!require("processx")) install.packages("processx")
 #install.packages("weights")
 }
 ### load the packages... This needs to be done every time. ###
-{library(mousetrap)
-library(foreach)
-library(tidyverse)
-library(readbulk)
-library(plyr)
-library(utils)
-library(stats)
-library(pracma)
-library(tidyr)
-library(magrittr)
-library(graphics)
-library(grDevices)
-library(ggplot2)
-library(scales)
-library(psych)
-library(Rcpp)
-library(diptest)
-library(RColorBrewer)
-library(cstab)
-library(fastcluster)
-library(parallel)
-library(fields)
-library(readxl)
-library(yarrr)
-library(weights)}
+{suppressPackageStartupMessages(library(mousetrap)) 
+  suppressPackageStartupMessages(library(foreach))
+  suppressPackageStartupMessages(library(tidyverse))
+  suppressPackageStartupMessages(library(readbulk))
+  suppressPackageStartupMessages(library(plyr))
+  suppressPackageStartupMessages(library(utils))
+  suppressPackageStartupMessages(library(stats))
+  suppressPackageStartupMessages(library(pracma))
+  suppressPackageStartupMessages(library(tidyr))
+  suppressPackageStartupMessages(library(magrittr))
+  suppressPackageStartupMessages(library(graphics))
+  suppressPackageStartupMessages(library(grDevices))
+  suppressPackageStartupMessages(library(ggplot2))
+  suppressPackageStartupMessages(library(scales))
+  suppressPackageStartupMessages(library(psych))
+  suppressPackageStartupMessages(library(Rcpp))
+  suppressPackageStartupMessages(library(diptest))
+  suppressPackageStartupMessages(library(RColorBrewer))
+  suppressPackageStartupMessages(library(cstab))
[…]

### 2019-08-07 Data_Cleaning.R
remove foreach RT

@@ -509,64 +509,10 @@ MT.data <- mt_import_wide(MT.data)
                                                                          "HiNeuHappyNo", "HiEmoHappyNo"),
                                            MT.data$data$mem.cor, ""))
   ### Create column to average for each face ###
-  MT.data$data$lo.emo.ang_rate <- ifelse(MT.data$data$cond.load == "LoEmoAngry", MT.data$data$rate, NA)
-  MT.data$data$hi.emo.ang_rate <- ifelse(MT.data$data$cond.load == "HiEmoAngry", MT.data$data$rate, NA)
-  MT.data$data$lo.neu.ang_rate <- ifelse(MT.data$data$cond.load == "LoNeuAngry", MT.data$data$rate, NA)
-  MT.data$data$hi.neu.ang_rate <- ifelse(MT.data$data$cond.load == "HiNeuAngry", MT.data$data$rate, NA)
-  MT.data$data$lo.emo.hap_rate <- ifelse(MT.data$data$cond.load == "LoEmoHappy", MT.data$data$rate, NA)
-  MT.data$data$hi.emo.hap_rate <- ifelse(MT.data$data$cond.load == "HiEmoHappy", MT.data$data$rate, NA)
-  MT.data$data$lo.neu.hap_rate <- ifelse(MT.data$data$cond.load == "LoNeuHappy", MT.data$data$rate, NA)
-  MT.data$data$hi.neu.hap_rate <- ifelse(MT.data$data$cond.load == "HiNeuHappy", MT.data$data$rate, NA)
-  MT.data$data$lo.emo.sur_rate <- ifelse(MT.data$data$cond.load == "LoEmoSurprise", MT.data$data$rate, NA)
-  MT.data$data$hi.emo.sur_rate <- ifelse(MT.data$data$cond.load == "HiEmoSurprise", MT.data$data$rate, NA)
-  MT.data$data$lo.neu.sur_rate <- ifelse(MT.data$data$cond.load == "LoNeuSurprise", MT.data$data$rate, NA)
-  MT.data$data$hi.neu.sur_rate <- ifelse(MT.data$data$cond.load == "HiNeuSurprise", MT.data$data$rate, NA)
   MT.data$data$mem.cor.yes <- ifelse(MT.data$data$cond.correct == "Yes", MT.data$data$mem.cor, NA)
[…]

### 2019-08-07 Manuscript/Manuscript.Rmd
change file save location

@@
 ```{r import data and analyze ratings, include = FALSE, echo = TRUE}
-data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-01_12-38-57.csv")
+data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-07_15-04-27.csv")
 ### remove psych disorders ### Ask maital?

### 2019-08-07 Manuscript/Manuscript.tex
change file save location

@@
 
-\begin{verbatim}
-##              Df Sum Sq Mean Sq F value Pr(>F)  
-## load          1  0.257 0.25709   4.599 0.0332 *
-## type          1  0.002 0.00230   0.041 0.8394  
-## load:type     1  0.001 0.00061   0.011 0.9170  
-## Residuals   196 10.956 0.05590                 
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-\end{verbatim}
-
-\includegraphics{Manuscript_files/figure-latex/MAD-1.pdf}
+\includegraphics{Manuscript_files/figure-latex/MAD plot-1.pdf}
+Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
 

### 2019-08-07 Data_Cleaning.R

@@ -619,6 +619,18 @@ MT.data.rating.table2 <- (ddply(MT.results2, "subjID", summarise,
                                hi.neu.sur_RT = mean(RT.x[which(cond.correct == "Surprise" & type == "NEU" & load == "HIGH" & trialtype == "face")], na.rm = TRUE),
                                lo.emo.sur_RT = mean(RT.x[which(cond.correct == "Surprise" & type == "EMO" & load == "LOW" & trialtype == "face")], na.rm = TRUE),
                                hi.emo.sur_RT = mean(RT.x[which(cond.correct == "Surprise" & type == "EMO" & load == "HIGH" & trialtype == "face")], na.rm = TRUE),
+                               lo.sur_RT = mean(RT.x[which(cond.correct == "Surprise" & load == "LOW" & trialtype == "face")], na.rm = TRUE),
+                               hi.sur_RT = mean(RT.x[which(cond.correct == "Surprise" & load == "HIGH" & trialtype == "face")], na.rm = TRUE),
+                               neu.sur_RT = mean(RT.x[which(cond.correct == "Surprise" & type == "NEU" & trialtype == "face")], na.rm = TRUE),
+                               emo.sur_RT = mean(RT.x[which(cond.correct == "Surprise" & type == "EMO" & trialtype == "face")], na.rm = TRUE),
+                               lo.sur_n_RT = mean(RT.x[which(cond.correct == "Surprise" & load == "LOW" & trialtype == "face" & rate == 1)], na.rm = TRUE),
+                               hi.sur_n_RT = mean(RT.x[which(cond.correct == "Surprise" & load == "HIGH" & trialtype == "face" & rate == 1)], na.rm = TRUE),
+                               neu.sur_n_RT = mean(RT.x[which(cond.correct == "Surprise" & type == "NEU" & trialtype == "face" & rate == 1)], na.rm = TRUE),
+                               emo.sur_n_RT = mean(RT.x[which(cond.correct == "Surprise" & type == "EMO" & trialtype == "face" & rate ==1)], na.rm = TRUE),
+                               lo.sur_p_RT = mean(RT.x[which(cond.correct == "Surprise" & load == "LOW" & trialtype == "face" & rate == 0)], na.rm = TRUE),
[…]

### 2019-08-13 Manuscript/Manuscript.Rmd
updating w MAD analyses
many changes

@@
 ### make long ###
-data.long <- gather(data, key = "Condition", value = "ReactionTime",
-                    lo.neu.sur_n_RT, hi.neu.sur_n_RT,
-                    lo.emo.sur_n_RT, hi.emo.sur_n_RT,
-                    lo.neu.sur_p_RT, hi.neu.sur_p_RT,
-                    lo.emo.sur_p_RT, hi.emo.sur_p_RT)
+data.long <- gather(data, key = "Condition", value = "ReactionTimeZ",
+                    lo.neu.sur_n_RTz, hi.neu.sur_n_RTz,
+                    lo.emo.sur_n_RTz, hi.emo.sur_n_RTz,
+                    lo.neu.sur_p_RTz, hi.neu.sur_p_RTz,
+                    lo.emo.sur_p_RTz, hi.emo.sur_p_RTz)
 data.long$Condition <- as.factor(data.long$Condition)
 
-data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)
+data.long.summary <- summarySE(data.long, measurevar="ReactionTimeZ", groupvars="Condition", na.rm = TRUE)
 
-ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
+ggplot(data.long.summary, aes(Condition, ReactionTimeZ, fill = as.factor(Condition))) +
   geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)
+  geom_errorbar(aes(ymin=ReactionTimeZ-se, ymax=ReactionTimeZ+se), width=.1)
 
@@
 ###  MAD analyses ###
+### check for normality ###
+shapiro.test(data$lo.emo.sur_MAD) # barely normal (p = .054)
+shapiro.test(data$hi.emo.sur_MAD) # barely normal (p = .08)
+shapiro.test(data$lo.neu.sur_MAD) # normal
+shapiro.test(data$hi.neu.sur_MAD) # normal
+
 results.long <- gather(data, key = "Condition", value = "MAD",
@@
   geom_errorbar(aes(ymin=`MAD`-se, ymax=`MAD`+se), width=.1)
+```
+``` {r MAD map}
+suppressPackageStartupMessages(library(mousetrap)) 
+# source MADFigure.R ???
+
 ```

### 2019-08-13 Data_Cleaning.R

@@ -678,6 +678,57 @@ write.csv(MT.data.rating.table2, paste("Data/Cleaned_Data/Final.Data.csv",format
                                       '.csv',sep = ''))
 
 
+### MD analysis, just like RT by response ###
+MT.results.small <- subset(MT.data.rating.table2[,c(1,56:63)])
+
+shapiro.test(MT.results.small$lo.emo.sur_n_MAD)
+shapiro.test(MT.results.small$lo.emo.sur_p_MAD)
+wilcox.test(MT.results.small$lo.emo.sur_n_MAD, MT.results.small$lo.emo.sur_p_MAD, paired = TRUE)
+MAD.long.resp <- gather(MT.results.small, key = "Condition", value = "MAD",
+                        lo.emo.sur_n_MAD, lo.emo.sur_p_MAD)
+ggplot(data = MAD.long.resp, aes(x = Condition, y = MAD)) +
+  geom_bar(stat = "summary", fun.y = "mean") +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .25, color = c("Black"))
+
+
+shapiro.test(MT.results.small$hi.emo.sur_n_MAD)
+shapiro.test(MT.results.small$hi.emo.sur_p_MAD)
+wilcox.test(MT.results.small$hi.emo.sur_n_MAD, MT.results.small$hi.emo.sur_p_MAD, paired = TRUE)
+MAD.long.resp <- gather(MT.results.small, key = "Condition", value = "MAD",
+                        hi.emo.sur_n_MAD, hi.emo.sur_p_MAD)
+ggplot(data = MAD.long.resp, aes(x = Condition, y = MAD)) +
+  geom_bar(stat = "summary", fun.y = "mean") +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .25, color = c("Black"))
+
+shapiro.test(MT.results.small$lo.neu.sur_n_MAD)
+shapiro.test(MT.results.small$lo.neu.sur_p_MAD)
+wilcox.test(MT.results.small$lo.neu.sur_n_MAD, MT.results.small$lo.neu.sur_p_MAD, paired = TRUE)
+MAD.long.resp <- gather(MT.results.small, key = "Condition", value = "MAD",
+                        lo.neu.sur_n_MAD, lo.neu.sur_p_MAD)
[…]

### 2019-08-13 MADFig.R

@@ -1,0 +1,4 @@
+### check plot trajectories ###
+MT.data.sur <- mt_subset(MT.data, cond.correct == "Surprise")
+
+mt_plot_aggregate(MT.data.sur, use = "tn_trajectories", color = "cond.load")

### 2019-08-13 Manuscript/Manuscript.Rmd
updated final data
RT outliers updated -- now calculates only RTs in face trials

@@
 ```{r import data and analyze ratings, include = FALSE, echo = TRUE}
-data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-07_15-04-27.csv")
+data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-13_12-52-10.csv")
 ### remove psych disorders ### Ask maital?

### 2019-08-13 Manuscript/Manuscript.tex
updated final data
RT outliers updated -- now calculates only RTs in face trials

@@
 \includegraphics{Manuscript_files/figure-latex/MAD plot-1.pdf}
+
 Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.

### 2019-08-13 Data_Cleaning.R

@@ -389,6 +389,14 @@ MT.data <- arrange(MT.data, subjID, order)
 file.list <- list(c(set1.va.files.list, set1.vc.files.list, set2.va.files.list,
                     set2.vc.files.list, set3.vd.files.list, set4.vd.files.list))}
 
+### clean workspace ###
+rm(set1.va.files.list, set1.vc.files.list, set2.va.files.list,
+   set2.vc.files.list, set3.vd.files.list, set4.vd.files.list,
+   set1.va.files, set1.va.trial.order, set1.vc.files,
+   set1.vc.trial.order, set2.va.files, set2.va.trial.order,
+   set2.vc.files, set2.vc.trial.order, set3.vd.files,
+   set3.vd.trial.order, set4.vd.files, set4.vd.trial.order)
+
 ### import MT data ###
 MT.data <- mt_import_wide(MT.data)
 
@@ -564,8 +572,8 @@ MT.data <- mt_import_wide(MT.data)
 }}
 
 ### check RT min / max for outliers ###
-meanrt <- mean(MT.data$data$RT)
-sdrt <- sd(MT.data$data$RT)
+meanrt <- mean(MT.data$data$RT[which(MT.data$data$trialtype == "face")])
+sdrt <- sd(MT.data$data$RT[which(MT.data$data$trialtype == "face")])
 outlier <- meanrt + (3*sdrt)
 #print(outlier)
 
@@ -674,7 +682,7 @@ MT.data.rating.table2 <- (ddply(MT.results2, "subjID", summarise,
                                lo.emo.RTz = mean(RTz[which(factor == "EMO LOW" & trialtype == "face")], na.rm = TRUE),
                                hi.emo.RTz = mean(RTz[which(factor == "EMO HIGH" & trialtype == "face")], na.rm = TRUE)))
 
-write.csv(MT.data.rating.table2, paste("Data/Cleaned_Data/Final.Data.csv",format(Sys.time(),'_%Y-%m-%d_%H-%M-%S'),
+ write.csv(MT.data.rating.table2, paste("Data/Cleaned_Data/Final.Data.csv",format(Sys.time(),'_%Y-%m-%d_%H-%M-%S'),
                                       '.csv',sep = ''))
 
 

### 2019-08-15 Manuscript/Manuscript.Rmd
Updating analyses and markdown
Finalizing results section

--- 2019-08-07 Manuscript/Manuscript.Rmd
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 ---
@@
 ```{r import data and analyze ratings, include = FALSE, echo = TRUE}
-data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-07_15-04-27.csv")
+data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-14_08-52-46.csv")
 ### remove psych disorders ### Ask maital?
@@
 
+### same results with ANOVA ###
+
+# aov.data <- friedman.data
+# aov.data$load <- recode(aov.data$Condition, "lo.neu.sur_rate" = "low",
+#                         "hi.neu.sur_rate"= "high",
+#                         "lo.emo.sur_rate"= "low",
+#                         "hi.emo.sur_rate"= "high")
+# aov.data$type <- recode(aov.data$Condition, "lo.neu.sur_rate" = "neu",
+#                         "hi.neu.sur_rate"= "neu",
+#                         "lo.emo.sur_rate"= "emo",
+#                         "hi.emo.sur_rate"= "emo")
+# summary(aov(`Percent Negative Ratings` ~ load * type, data = aov.data))
 ```
 Distributions of ratings were first tested for normality using Shapiro-Wilk's test.
-The results of all four tests were highly significant (p's < .001), so non-parametric tests were used for data analysis.
-Friedman's test results showed significantly different distributions across the conditions $\chi^{2}$(`r (printnum(friedman.results$parameter))`) = `r printnum(friedman.results$statistic)`, p `r printp(friedman.results$p.value)`.
-Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content.
+The results of all four tests were significant (p's < .001), so non-parametric tests were used for data analysis.
+Friedman's test results showed significantly different rank-order distributions across the conditions $\chi^{2}$(`r (printnum(friedman.results$parameter))`) = `r printnum(friedman.results$statistic)`, p `r printp(friedman.results$p.value)`.
+Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content, and this was true for both low and high loads.
 Low emotional load ratings were significantly more negative than low, Z = `r (printnum(lo.emo.v.lo.neu$z_val))`, p = `r (printp(lo.emo.v.lo.neu$p.value))`, neutral and high, Z = `r (printnum(lo.emo.v.hi.neu$z_val))`, p `r (printp(lo.emo.v.hi.neu$p.value))`, neutral loads.
@@
 ``` {r plot figure 1, include = TRUE}
-### summarize the data ###
-friedman.data.summarized <- summarySE(friedman.data, measurevar="Percent Negative Ratings", groupvars = "Condition")
-
-ggplot(friedman.data.summarized, aes(Condition, `Percent Negative Ratings`, fill = as.factor(Condition))) +
+ggplot(friedman.data, aes(Condition, `Percent Negative Ratings`, fill = as.factor(Condition))) +
   geom_bar(stat = "summary", fun.y = "mean") +
-  geom_errorbar(aes(ymin=`Percent Negative Ratings`-se, ymax=`Percent Negative Ratings`+se), width=.1)
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
 ```
@@
 ## assess normality ###
-shapiro.test(data$lo.neu.sur_RTz)
-shapiro.test(data$hi.neu.sur_RTz)
-shapiro.test(data$lo.emo.sur_RTz)
-shapiro.test(data$hi.emo.sur_RTz)
+shapiro.test(data$lo.neu.sur_RT)
+shapiro.test(data$hi.neu.sur_RT)
+shapiro.test(data$lo.emo.sur_RT)
+shapiro.test(data$hi.emo.sur_RT)
 
 ### force normality ###
-RTz.long <- gather(data, key = Condition, value = RTz,
-                   lo.neu.sur_RTz,
-                   hi.neu.sur_RTz,
-                   lo.emo.sur_RTz,
-                   hi.emo.sur_RTz)
+# RTz.long <- gather(data, key = Condition, value = RTz,
+#                     lo.neu.sur_RTz,
+#                     hi.neu.sur_RTz,
+#                     lo.emo.sur_RTz,
+#                     hi.emo.sur_RTz)
 
-### run Friedman's test and store results ###
-RTz.friedman <- friedman.test(RTz ~ Condition|subjID, data = RTz.long)
-lo.emo.v.lo.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-lo.emo.v.hi.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-lo.emo.v.hi.emo.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.emo.sur_RTz, paired = TRUE, conf.int = TRUE)
-hi.emo.v.lo.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-hi.emo.v.hi.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-lo.neu.v.hi.neu.RTz <- wilcox_test(data$hi.neu.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-
-# RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)
-
-# wide <- spread(RTz.long, key = Condition, value = RTz)
-# hapiro.test(wide$lo.emo.sur_RT)
+# ### run Friedman's test and store results ###
+# RTz.friedman <- friedman.test(RTz ~ Condition|subjID, data = RTz.long)
+# lo.emo.v.lo.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+# lo.emo.v.hi.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+# lo.emo.v.hi.emo.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.emo.sur_RTz, paired = TRUE, conf.int = TRUE)
+# hi.emo.v.lo.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+# hi.emo.v.hi.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+# lo.neu.v.hi.neu.RTz <- wilcox_test(data$hi.neu.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
+# 
+# # RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)
+# 
+# # wide <- spread(RTz.long, key = Condition, value = RTz)
+# # hapiro.test(wide$lo.emo.sur_RT)
 ### make factors ###
-RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Low",
-                         ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Low",
-                                ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "High",
-                                       ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "High", ""))))
-
-RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Neutral",
-                         ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Emotional",
-                                ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "Neutral",
-                                       ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "Emotional", ""))))
-
-### make w/in subjs factors ###
-RTz.long$subjID <- as.factor(RTz.long$subjID)
-
-### traditional ANOVA ###
-RTaov <- with(RTz.long,
-                   aov(RTz ~ (Load * Type) +
-                       Error(subjID / (Load * Type))), contrasts = contr.sum())
-summary(RTaov)
-RTaov <- tidy(RTaov)
-
-# ### make long ###
-# data.long <- gather(data, key = "Condition", value = "ReactionTime",
-#                     lo.neu.sur_RT, hi.neu.sur_RT,
-#                     lo.emo.sur_RT, hi.emo.sur_RT)
+# RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Low",
+#                           ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Low",
+#                                  ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "High",
+#                                         ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "High", ""))))
 #  
-# ### make factors ###
-# data.long$Load <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Low",
-#                          ifelse(data.long$Condition == "lo.emo.sur_RT", "Low",
-#                                 ifelse(data.long$Condition == "hi.neu.sur_RT", "High",
-#                                        ifelse(data.long$Condition == "hi.emo.sur_RT", "High", ""))))
-# 
-# data.long$Type <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Neutral",
-#                          ifelse(data.long$Condition == "lo.emo.sur_RT", "Emotional",
-#                                 ifelse(data.long$Condition == "hi.neu.sur_RT", "Neutral",
-#                                        ifelse(data.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
+# RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Neutral",
+#                           ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Emotional",
+#                                  ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "Neutral",
+#                                         ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "Emotional", ""))))
 #  
 # ### make w/in subjs factors ###
-# data.long$subjID <- as.factor(data.long$subjID)
+# RTz.long$subjID <- as.factor(RTz.long$subjID)
 #  
 # ### traditional ANOVA ###
-# RTaov <- with(data.long,
-#                    aov(ReactionTime ~ (Load * Type) +
+# RTaov <- with(RTz.long,
+#                     aov(RTz ~ (Load * Type) +
 #                         Error(subjID / (Load * Type))), contrasts = contr.sum())
@@
 
-# ### friedman's nonparametric ###
-# friedman.RT.results <- friedman.test(ReactionTime ~ Condition|subjID, data = data.long)
-# ### Follow up wilcoxon tests ###
-# lo.emo.v.lo.neuRT <- wilcox.test(data$lo.emo.sur_RT, data$lo.neu.sur_RT, paired = TRUE, conf.int = TRUE)
-# lo.emo.v.hi.neuRT <- wilcox.test(data$lo.emo.sur_RT, data$hi.neu.sur_RT, paired = TRUE, conf.int = TRUE)
-# lo.emo.v.hi.emoRT <- wilcox.test(data$lo.emo.sur_RT, data$hi.emo.sur_RT, paired = TRUE, conf.int = TRUE)
-# hi.emo.v.lo.neuRT <- wilcox.test(data$hi.emo.sur_RT, data$lo.neu.sur_RT, paired = TRUE, conf.int = TRUE)
-# hi.emo.v.hi.neuRT <- wilcox.test(data$hi.emo.sur_RT, data$hi.neu.sur_RT, paired = TRUE, conf.int = TRUE)
-# lo.neu.v.hi.neuRT <- wilcox.test(data$hi.neu.sur_RT, data$lo.neu.sur_RT, paired = TRUE, conf.int = TRUE)
+### make long ###
+data.long <- gather(data, key = "Condition", value = "ReactionTime",
+                    lo.neu.sur_RT, hi.neu.sur_RT,
+                    lo.emo.sur_RT, hi.emo.sur_RT)
 
-# summary(friedman.RT.results)
+### make factors ###
+data.long$Load <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Low",
+                         ifelse(data.long$Condition == "lo.emo.sur_RT", "Low",
+                                ifelse(data.long$Condition == "hi.neu.sur_RT", "High",
+                                       ifelse(data.long$Condition == "hi.emo.sur_RT", "High", ""))))
 
+data.long$Type <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Neutral",
+                         ifelse(data.long$Condition == "lo.emo.sur_RT", "Emotional",
+                                ifelse(data.long$Condition == "hi.neu.sur_RT", "Neutral",
+                                       ifelse(data.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
+
+### make w/in subjs factors ###
+data.long$subjID <- as.factor(data.long$subjID)
+
+### traditional ANOVA ###
+RTaov <- with(data.long,
+                   aov(ReactionTime ~ (Load * Type) +
+                       Error(subjID / (Load * Type))), contrasts = contr.sum())
+summary(RTaov)
+RTaov <- tidy(RTaov)
 ```
-To assess for normality, the data were first tested with Shapiro-Wilk's test.
-Two conditions did not appear to be sampled from normal distributions, so non-parametric tests were used.
-Overall, there was a trending difference across the four conditions, $\chi^{2}$(`r (printnum(RTz.friedman$parameter))`) = `r printnum(RTz.friedman$statistic)`, p `r printp(RTz.friedman$p.value)`.
-Wilcoxon signed rank tests were used to assess post-hoc comparisons and Bonferroni corrected p-value = `r printnum(.05 / 6)`.
-While none of the post-hoc comparisons reached the adjusted significance level, there was a trending difference between emotional and neutral RTs in the high load condition, Z = `r printnum(hi.emo.v.hi.neu.RTz$z_val)`, p = `r printp(hi.emo.v.hi.neu.RTz$p.value)`, such that high emotional WM loads had slower RTs.
-Two other comparisons were trending for traditional levels of significance.
-Low emotional WM loads tended to take marginally longer than high neutral WM loads, Z = `r printnum(lo.emo.v.hi.neu.RTz$z_val)`, p = `r printp(lo.emo.v.hi.neu.RTz$p.value)`, and low neutral WM loads took marginally longer than high neutral WM laods, Z = `r printnum(lo.neu.v.hi.neu.RTz$z_val)`, p = `r printnum(lo.neu.v.hi.neu.RTz$p.value)`.
-All other comparisons were not significant.
-<!-- IF WE USE RAW RTS, USE THIS TEXT
 To assses for normality, the data were first tested with Shapiro-Wilk's test.
-All conditions appeared to be sampled from normal distributions (p's > .08).
+All conditions appeared to be sampled from normal distributions (p's > .300).
 A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs.
 There was a trend towards a main effect of type, F(`r (RTaov$df[which(RTaov$term == "Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Type")])`.
-However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons.
-There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = .
-One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = .
-All other comparisons were non-significant (p's > .
--->
+There was no effect of domain, F(`r (RTaov$df[which(RTaov$term == "Load")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Load")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Load")])`, nor any interaction between load and domain, F(`r (RTaov$df[which(RTaov$term == "Load:Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Load:Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Load:Type")])`.
 
 ```{r plot RT data, include = TRUE}
-ggplot(RTz.long, aes(Condition, `RTz`, fill = as.factor(Condition))) +
+ggplot(data.long, aes(Condition, `ReactionTime`, fill = as.factor(Condition))) +
   geom_bar(stat = "summary", fun.y = "mean") +
@@
 ### make long ###
-data.long <- gather(data, key = "Condition", value = "ReactionTime",
-                    lo.neu.sur_n_RT, hi.neu.sur_n_RT,
-                    lo.emo.sur_n_RT, hi.emo.sur_n_RT,
-                    lo.neu.sur_p_RT, hi.neu.sur_p_RT,
-                    lo.emo.sur_p_RT, hi.emo.sur_p_RT)
-data.long$Condition <- as.factor(data.long$Condition)
+lo.neu.resp <- gather(data, key = "Condition", value =  "ReactionTime",
+                    lo.neu.sur_n_RT, lo.neu.sur_p_RT)
+lo.emo.resp <- gather(data, key = "Condition", value =  "ReactionTime",
+                    lo.emo.sur_n_RT, lo.emo.sur_p_RT)
+hi.neu.resp <- gather(data, key = "Condition", value =  "ReactionTime",
+                    hi.neu.sur_n_RT, hi.neu.sur_p_RT)
+hi.emo.resp <- gather(data, key = "Condition", value =  "ReactionTime",
+                    hi.emo.sur_n_RT, hi.emo.sur_p_RT)
 
-data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)
+lo.neu.resp$Condition <- as.factor(lo.neu.resp$Condition)
+lo.emo.resp$Condition <- as.factor(lo.emo.resp$Condition)
+hi.neu.resp$Condition <- as.factor(hi.neu.resp$Condition)
+hi.emo.resp$Condition <- as.factor(hi.emo.resp$Condition)
 
-ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
+lo.neu.resp.plot <- ggplot(lo.neu.resp, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
   geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
 
-# ### force normality ###
-# RTz.long <- gather(data, key = Condition, value = RTz,
-#                    lo.neu.sur_n_RT, lo.neu.sur_p_RT,
-#                    hi.neu.sur_n_RT, hi.neu.sur_p_RT,
-#                    lo.emo.sur_n_RT, lo.emo.sur_p_RT,
-#                    hi.emo.sur_n_RT, hi.emo.sur_p_RT)
-# 
-# ### back to wide ###
-# data2 <- spread(RTz.long, key = Condition, value = RTz)
-# ### assess for normality ###
-# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_n_RT")])
-# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.neu.sur_p_RT")])
-# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_n_RT")])
-# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.neu.sur_p_RT")])
-# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_n_RT")])
-# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "lo.emo.sur_p_RT")])
-# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_n_RT")])
-# shapiro.test(RTz.long$RTz[which(RTz.long$Condition == "hi.emo.sur_p_RT")])
-# 
-# RTz.long$Condition <- as.factor(RTz.long$Condition)
-# 
-# ### make factors ###
-# RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_n_RT", "Low",
-#                          ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Low",
-#                                 ifelse(RTz.long$Condition == "hi.neu.sur_RT", "High",
-#                                        ifelse(RTz.long$Condition == "hi.emo.sur_RT", "High", ""))))
-# 
-# RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RT", "Neutral",
-#                          ifelse(RTz.long$Condition == "lo.emo.sur_RT", "Emotional",
-#                                 ifelse(RTz.long$Condition == "hi.neu.sur_RT", "Neutral",
-#                                        ifelse(RTz.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
-# 
-# ### make w/in subjs factors ###
-# data.long$subjID <- as.factor(data.long$subjID)
-# 
-# ### traditional ANOVA ###
-# RTaov <- with(data.long,
-#                    aov(ReactionTime ~ (Load * Type) +
-#                        Error(subjID / (Load * Type))), contrasts = contr.sum())
-# summary(RTaov)
-# RTaov <- tidy(RTaov)
-# 
-# 
-# 
-# 
-# data.long.summary <- summarySE(data.long, measurevar="ReactionTime", groupvars="Condition", na.rm = TRUE)
+lo.emo.resp.plot <- ggplot(lo.emo.resp, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
+  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
 
-# ggplot(data.long.summary, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
-#   geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-#   geom_errorbar(aes(ymin=ReactionTime-se, ymax=ReactionTime+se), width=.1)
+hi.neu.resp.plot <- ggplot(hi.neu.resp, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
+  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
+
+hi.emo.resp.plot <- ggplot(hi.emo.resp, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
+  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
+
+# lo.neu.resp.plot
+
+# hi.neu.resp.plot
+
+#lo.emo.resp.plot
+
+# hi.emo.resp.plot
 
 ```
-Next, we tested for reaciton time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition.
-Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs.
+Next, we tested for reaction time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition.
+A large proportion of the conditions were not normally distributed, thus we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs.
 This difference was significant *only* for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (`r printp(lo.neu.RT.pvn$p.value)`).
@@
 ###  MAD analyses ###
-results.long <- gather(data, key = "Condition", value = "MAD",
+### check for normality ###
+shapiro.test(data$lo.emo.sur_MAD) # not normal (p = .024)
+shapiro.test(data$hi.emo.sur_MAD) # barely normal (p = .09)
+shapiro.test(data$lo.neu.sur_MAD) # normal
+shapiro.test(data$hi.neu.sur_MAD) # normal
+
+MAD.long <- gather(data, key = "Condition", value = "MAD",
                        lo.emo.sur_MAD, hi.emo.sur_MAD, lo.neu.sur_MAD, hi.neu.sur_MAD)
-results.long$load <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Low",
-                            ifelse(results.long$Condition == "lo.neu.sur_MAD", "Low", "High"))
-results.long$type <- ifelse(results.long$Condition == "lo.emo.sur_MAD", "Emo",
-                            ifelse(results.long$Condition == "hi.emo.sur_MAD", "Emo", "Neu"))
+MAD.long$load <- ifelse(MAD.long$Condition == "lo.emo.sur_MAD", "Low",
+                            ifelse(MAD.long$Condition == "lo.neu.sur_MAD", "Low", "High"))
+MAD.long$type <- ifelse(MAD.long$Condition == "lo.emo.sur_MAD", "Emo",
+                            ifelse(MAD.long$Condition == "hi.emo.sur_MAD", "Emo", "Neu"))
 
-MAD.anova <- aov(MAD ~ load * type, data = results.long)
+MAD.anova <- aov(MAD ~ load * type, data = MAD.long)
 summary.aov(MAD.anova)
-
-res.long.sum <- summarySE(results.long, measurevar="MAD", groupvars = "Condition")
+MAD.anova <- tidy(MAD.anova)
 ```
@@
 ``` {r MAD plot, include = TRUE}
-ggplot(res.long.sum, aes(Condition, MAD, fill = as.factor(Condition))) +
+ggplot(MAD.long, aes(Condition, MAD, fill = as.factor(Condition))) +
   geom_bar(stat = "summary", fun.y = "mean") +
-  geom_errorbar(aes(ymin=`MAD`-se, ymax=`MAD`+se), width=.1)
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
+```
+``` {r MAD map, include = FALSE}
+suppressPackageStartupMessages(library(mousetrap)) 
+# source MADFigure.R ???
+
 ```
 Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
+While one of the conditions, low emotional MDs, was not normally distributed (p = .024), all other conditions were normally distributed and repeated-measures ANOVA was used to analyze the MDs across conditions.
+There was a significant effect of load, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "load")])`,`r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "load")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "load")])`, such that MDs under high load were larger than trials with low load.
+There was no significant effect of domain on MDs, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "type")])` `r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "type")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "type")])`, nor an interaction of load by domain, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "load:type")])` `r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "load:type")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "load:type")])`.
 
+``` {r MAD resp, include = FALSE}
+### assess for normality ###
+shapiro.test(data$lo.neu.sur_n_MAD) ## normal
+shapiro.test(data$lo.neu.sur_p_MAD) ## non-normal
+shapiro.test(data$hi.neu.sur_n_MAD) ## barely normal (.058)
+shapiro.test(data$hi.neu.sur_p_MAD) ## normal
+shapiro.test(data$lo.emo.sur_n_MAD) ## non-normal
+shapiro.test(data$lo.emo.sur_p_MAD) ## barely normal (.068)
+shapiro.test(data$hi.emo.sur_n_MAD) ## non-normal
+shapiro.test(data$hi.emo.sur_p_MAD) ## normal
+
+### t-test for pos ratings vs. neg ratings
+wilcox.test(data$lo.neu.sur_n_MAD, data$lo.neu.sur_p_MAD, paired = TRUE) ### different 
+wilcox.test(data$hi.neu.sur_n_MAD, data$hi.neu.sur_p_MAD, paired = TRUE) ### trending
+wilcox.test(data$lo.emo.sur_n_MAD, data$lo.emo.sur_p_MAD, paired = TRUE) ### non-sig
+wilcox.test(data$hi.emo.sur_n_MAD, data$hi.emo.sur_p_MAD, paired = TRUE) ### non-sig
+
+t.test(data$lo.neu.sur_n_MAD, data$lo.neu.sur_p_MAD, paired = TRUE) ### different 
+t.test(data$hi.neu.sur_n_MAD, data$hi.neu.sur_p_MAD, paired = TRUE) ### trending
+t.test(data$lo.emo.sur_n_MAD, data$lo.emo.sur_p_MAD, paired = TRUE) ### non-sig
+t.test(data$hi.emo.sur_n_MAD, data$hi.emo.sur_p_MAD, paired = TRUE) ### non-sig
+
+### make long ###
+lo.neu.resp.MAD <- gather(data, key = "Condition", value =  "MAD",
+                    lo.neu.sur_n_MAD, lo.neu.sur_p_MAD)
+lo.emo.resp.MAD  <- gather(data, key = "Condition", value =  "MAD",
+                    lo.emo.sur_n_MAD, lo.emo.sur_p_MAD)
+hi.neu.resp.MAD  <- gather(data, key = "Condition", value =  "MAD",
+                    hi.neu.sur_n_MAD, hi.neu.sur_p_MAD)
+hi.emo.resp.MAD  <- gather(data, key = "Condition", value =  "MAD",
+                    hi.emo.sur_n_MAD, hi.emo.sur_p_MAD)
+
+lo.neu.resp.MAD$Condition <- as.factor(lo.neu.resp.MAD$Condition)
+lo.emo.resp.MAD$Condition <- as.factor(lo.emo.resp.MAD$Condition)
+hi.neu.resp.MAD$Condition <- as.factor(hi.neu.resp.MAD$Condition)
+hi.emo.resp.MAD$Condition <- as.factor(hi.emo.resp.MAD$Condition)
+
+lo.neu.resp.MAD.plot <- ggplot(lo.neu.resp.MAD, aes(Condition, MAD, fill = as.factor(Condition))) +
+  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
+
+lo.emo.resp.MAD.plot <- ggplot(lo.emo.resp.MAD, aes(Condition, MAD, fill = as.factor(Condition))) +
+  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
+
+hi.neu.resp.MAD.plot <- ggplot(hi.neu.resp.MAD, aes(Condition, MAD, fill = as.factor(Condition))) +
+  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
+
+hi.emo.resp.MAD.plot <- ggplot(hi.emo.resp.MAD, aes(Condition, MAD, fill = as.factor(Condition))) +
+  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
+
+lo.neu.resp.MAD.plot
+lo.emo.resp.MAD.plot
+hi.neu.resp.MAD.plot
+hi.emo.resp.MAD.plot
+```
 # Discussion

### 2019-08-15 Manuscript/Manuscript.tex
Updating analyses and markdown
Finalizing results section

@@
 
-We used R (Version 3.6.0; {\textbf{???}}) and the R-packages * \}dplyr* {[}@ \}R-dplyr{]}, \emph{broom} (Version 0.5.2; {\textbf{???}}), \emph{forcats} (Version 0.4.0; {\textbf{???}}), \emph{ggplot2} (Version 3.1.1; {\textbf{???}}), \emph{lattice} (Version 0.20.38; {\textbf{???}}), \emph{openxlsx} (Version 4.1.0; {\textbf{???}}), \emph{papaja} (Version 0.1.0.9842; {\textbf{???}}), \emph{plyr} (Version 1.8.4; @ \}R-dplyr; {\textbf{???}}), \emph{purrr} (Version 0.3.2; {\textbf{???}}), \emph{readr} (Version 1.3.1; {\textbf{???}}), \emph{readxl} (Version 1.3.1; {\textbf{???}}), \emph{Rmisc} (Version 1.5; {\textbf{???}}), \emph{stringr} (Version 1.4.0; {\textbf{???}}), \emph{tibble} (Version 2.1.3; {\textbf{???}}), \emph{tidyr} (Version 0.8.3.9000; {\textbf{???}}), and \emph{tidyverse} (Version 1.2.1; {\textbf{???}}) for all our analyses.
+We used R (Version 3.6.0; {\textbf{???}}) and the R-packages * \}dplyr* {[}@ \}R-dplyr{]}, \emph{broom} (Version 0.5.2; {\textbf{???}}), \emph{forcats} (Version 0.4.0; {\textbf{???}}), \emph{ggplot2} (Version 3.1.1; {\textbf{???}}), \emph{lattice} (Version 0.20.38; {\textbf{???}}), \emph{mousetrap} (Version 3.1.2; {\textbf{???}}), \emph{openxlsx} (Version 4.1.0; {\textbf{???}}), \emph{papaja} (Version 0.1.0.9842; {\textbf{???}}), \emph{plyr} (Version 1.8.4; @ \}R-dplyr; {\textbf{???}}), \emph{purrr} (Version 0.3.2; {\textbf{???}}), \emph{readr} (Version 1.3.1; {\textbf{???}}), \emph{readxl} (Version 1.3.1; {\textbf{???}}), \emph{Rmisc} (Version 1.5; {\textbf{???}}), \emph{stringr} (Version 1.4.0; {\textbf{???}}), \emph{tibble} (Version 2.1.3; {\textbf{???}}), \emph{tidyr} (Version 0.8.3.9000; {\textbf{???}}), and \emph{tidyverse} (Version 1.2.1; {\textbf{???}}) for all our analyses.
 Data preprocessing was completed in R using the mousetrap package ({\textbf{???}}).
@@
 The results of all four tests were highly significant (p's \textless{} .001), so non-parametric tests were used for data analysis.
-Friedman's test results showed significantly different distributions across the conditions \(\chi^{2}\)(3.00) = 27.41, p \textless{} .001.
+Friedman's test results showed significantly different distributions across the conditions \(\chi^{2}\)(3.00) = 27.79, p \textless{} .001.
 Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content.
-Low emotional load ratings were significantly more negative than low, Z = 3.31, p = .001, neutral and high, Z = 3.62, p \textless{} .001, neutral loads.
-The same was true for high emotional load ratings and low, Z = 4.52, p \textless{} .001, and high, Z = 3.72, p \textless{} .001, neutral loads.
+Low emotional load ratings were significantly more negative than low, Z = 3.27, p = .001, neutral and high, Z = 3.67, p \textless{} .001, neutral loads.
+The same was true for high emotional load ratings and low, Z = 4.55, p \textless{} .001, and high, Z = 3.81, p \textless{} .001, neutral loads.
 However, there was no discernable effect of load.
-That is, the comparisons between low and high load ratings for both emotional, Z = -1.10, p = .273, and neutral, Z = -0.03, p = .975, load ratings were not significantly different.\footnote{These results are qualitatively the same when analyzing these data with a repeated measures ANOVA.}
+That is, the comparisons between low and high load ratings for both emotional, Z = -1.35, p = .176, and neutral, Z = -0.06, p = .954, load ratings were not significantly different.\footnote{These results are qualitatively the same when analyzing these data with a repeated measures ANOVA.}
 
@@
 
-To assess for normality, the data were first tested with Shapiro-Wilk's test.
-Two conditions did not appear to be sampled from normal distributions, so non-parametric tests were used.
-Overall, there was a trending difference across the four conditions, \(\chi^{2}\)(3.00) = 7.15, p .067.
-Wilcoxon signed rank tests were used to assess post-hoc comparisons and Bonferroni corrected p-value = 0.01.
-While none of the post-hoc comparisons reached the adjusted significance level, there was a trending difference between emotional and neutral RTs in the high load condition, Z = 2.51, p = .012, such that high emotional WM loads had slower RTs.
-Two other comparisons were trending for traditional levels of significance.
-Low emotional WM loads tended to take marginally longer than high neutral WM loads, Z = 1.96, p = .050, and low neutral WM loads took marginally longer than high neutral WM laods, Z = -1.75, p = 0.08.
-All other comparisons were not significant.
+To assses for normality, the data were first tested with Shapiro-Wilk's test.
+All conditions appeared to be sampled from normal distributions (p's \textgreater{} .08).
+A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs.
+There was a trend towards a main effect of type, F(1, 49) = 2.97, p = 0.09.
+However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons.
+There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = .
+One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = .
+All other comparisons were non-significant (p's \textgreater{} .
 
@@
 
-Next, we tested for reaciton time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition.
+Next, we tested for reaction time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition.
 Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs.
@@
 Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
+While one of the conditions, low emotional MDs, was not normally distributed (p = .024), all other conditions were normally distributed and repeated-measures ANOVA was used to analyze the MDs across conditions.
+There was a significant effect of load, F(1.00,196.00) = 5.51, p = .020, such that MDs under high load were larger than trials with low load.
+There was no significant effect of domain on MDs, F(1.00 196.00) = 0.01, p = .912, nor an interaction of load by domain.
+\# Discussion
 The effect of high vs.~low load is still not apparent in these data, just like Mattek et al.~2016.

### 2019-08-15 Data_Cleaning.R

@@ -3,35 +3,6 @@ setwd("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/A
 
 if (!require("processx")) install.packages("processx")
 
-{### install MouseTrap... This only needs to be done once. ###
-### ... and readbulk for applying to a set of files ###
-#install.packages("mousetrap")
-#install.packages("readbulk")
-#install.packages("here")
-#install.packages("foreach")
-#install.packages("tidyverse")
-#install.packages("plyr")
-#install.packages("utils")
-#install.packages("stats")
-#install.packages("pracma")
-#install.packages("tidyr")
-#install.packages("magrittr")
-#install.packages("graphics")
-#install.packages("grDevices")
-#install.packages("ggplot2")
-#install.packages("scales")
-#install.packages("psych")
-#install.packages("Rcpp")
-#install.packages("diptest")
-#install.packages("RColorBrewer")
-#install.packages("cstab")
-#install.packages("fastcluster")
-#install.packages("parallel")
-#install.packages("fields")
-#install.packages("orca")
-#install.packages("plotly")
-#install.packages("weights")
-}
 ### load the packages... This needs to be done every time. ###
 {suppressPackageStartupMessages(library(mousetrap)) 
   suppressPackageStartupMessages(library(foreach))
@@ -245,7 +216,7 @@ session1.data.persub <- mt_aggregate_per_subject(session1.data, use = "measures"
 ### merge MT measures w/ rating data ###
 session1.ratings.table <- merge(session1.data.persub, session1.ratings.table, by = "subjID")
 ### write output for session1 ###
-write.csv(session1.ratings.table, "WM.Session1.csv")
+#write.csv(session1.ratings.table, "WM.Session1.csv")
 
 
 
@@ -578,7 +549,7 @@ outlier <- meanrt + (3*sdrt)
 #print(outlier)
 
 ### remove trials > outlierRT ###
-MT.data$data <- subset(MT.data$data, RT <= outlier)
+MT.data$data <-MT.data$data[!(MT.data$data$RT >= outlier),]
 
[…]

### 2019-08-19 Manuscript/Manuscript.Rmd
remove analyses
Settled on subj ratings and MD overall for the two MERP findings.

@@
 
-### force normality ###
-# RTz.long <- gather(data, key = Condition, value = RTz,
-#                     lo.neu.sur_RTz,
-#                     hi.neu.sur_RTz,
-#                     lo.emo.sur_RTz,
-#                     hi.emo.sur_RTz)
-
-# ### run Friedman's test and store results ###
-# RTz.friedman <- friedman.test(RTz ~ Condition|subjID, data = RTz.long)
-# lo.emo.v.lo.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-# lo.emo.v.hi.neu.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-# lo.emo.v.hi.emo.RTz <- wilcox_test(data$lo.emo.sur_RTz, data$hi.emo.sur_RTz, paired = TRUE, conf.int = TRUE)
-# hi.emo.v.lo.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-# hi.emo.v.hi.neu.RTz <- wilcox_test(data$hi.emo.sur_RTz, data$hi.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-# lo.neu.v.hi.neu.RTz <- wilcox_test(data$hi.neu.sur_RTz, data$lo.neu.sur_RTz, paired = TRUE, conf.int = TRUE)
-# 
-# # RTz.long$RTz <- ave(RTz.long$RTz, RTz.long$subjID, FUN=scale)
-# 
-# # wide <- spread(RTz.long, key = Condition, value = RTz)
-# # hapiro.test(wide$lo.emo.sur_RT)
-### make factors ###
-# RTz.long$Load <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Low",
-#                           ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Low",
-#                                  ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "High",
-#                                         ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "High", ""))))
-#  
-# RTz.long$Type <- ifelse(RTz.long$Condition == "lo.neu.sur_RTz", "Neutral",
-#                           ifelse(RTz.long$Condition == "lo.emo.sur_RTz", "Emotional",
-#                                  ifelse(RTz.long$Condition == "hi.neu.sur_RTz", "Neutral",
-#                                         ifelse(RTz.long$Condition == "hi.emo.sur_RTz", "Emotional", ""))))
-#  
-# ### make w/in subjs factors ###
-# RTz.long$subjID <- as.factor(RTz.long$subjID)
-#  
-# ### traditional ANOVA ###
-# RTaov <- with(RTz.long,
-#                     aov(RTz ~ (Load * Type) +
-#                         Error(subjID / (Load * Type))), contrasts = contr.sum())
-# summary(RTaov)
-# RTaov <- tidy(RTaov)
-
 ### make long ###
@@
 A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs.
-There was a trend towards a main effect of type, F(`r (RTaov$df[which(RTaov$term == "Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Type")])`.
-There was no effect of domain, F(`r (RTaov$df[which(RTaov$term == "Load")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Load")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Load")])`, nor any interaction between load and domain, F(`r (RTaov$df[which(RTaov$term == "Load:Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Load:Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Load:Type")])`.
+There was a trend towards a main effect of domain, F(`r (RTaov$df[which(RTaov$term == "Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Type")])`.
+There was no effect of load, F(`r (RTaov$df[which(RTaov$term == "Load")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Load")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Load")])`, nor any interaction between load and domain, F(`r (RTaov$df[which(RTaov$term == "Load:Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Load:Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Load:Type")])`.
 
@@
   stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-```
-
-``` {r RT by ratings, include = FALSE}
-### assess for normality ###
-shapiro.test(data$lo.neu.sur_n_RT) ## non-normal
-shapiro.test(data$lo.neu.sur_p_RT) ## normal
-shapiro.test(data$hi.neu.sur_n_RT) ## non-normal
-shapiro.test(data$hi.neu.sur_p_RT) ## normal
-shapiro.test(data$lo.emo.sur_n_RT) ## non-normal
-shapiro.test(data$lo.emo.sur_p_RT) ## non-normal
-shapiro.test(data$hi.emo.sur_n_RT) ## barely normal
-shapiro.test(data$hi.emo.sur_p_RT) ## non-normal
-
-### t-test for pos ratings vs. neg ratings
-lo.neu.RT.pvn <- wilcox.test(data$lo.neu.sur_n_RT, data$lo.neu.sur_p_RT, paired = TRUE)
-wilcox.test(data$hi.neu.sur_n_RT, data$hi.neu.sur_p_RT, paired = TRUE)
-wilcox.test(data$lo.emo.sur_n_RT, data$lo.emo.sur_p_RT, paired = TRUE)
-wilcox.test(data$hi.emo.sur_n_RT, data$hi.emo.sur_p_RT, paired = TRUE)
-
-### make long ###
-lo.neu.resp <- gather(data, key = "Condition", value =  "ReactionTime",
-                    lo.neu.sur_n_RT, lo.neu.sur_p_RT)
-lo.emo.resp <- gather(data, key = "Condition", value =  "ReactionTime",
-                    lo.emo.sur_n_RT, lo.emo.sur_p_RT)
-hi.neu.resp <- gather(data, key = "Condition", value =  "ReactionTime",
-                    hi.neu.sur_n_RT, hi.neu.sur_p_RT)
-hi.emo.resp <- gather(data, key = "Condition", value =  "ReactionTime",
-                    hi.emo.sur_n_RT, hi.emo.sur_p_RT)
-
-lo.neu.resp$Condition <- as.factor(lo.neu.resp$Condition)
-lo.emo.resp$Condition <- as.factor(lo.emo.resp$Condition)
-hi.neu.resp$Condition <- as.factor(hi.neu.resp$Condition)
-hi.emo.resp$Condition <- as.factor(hi.emo.resp$Condition)
-
-lo.neu.resp.plot <- ggplot(lo.neu.resp, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-
-lo.emo.resp.plot <- ggplot(lo.emo.resp, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-
-hi.neu.resp.plot <- ggplot(hi.neu.resp, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-
-hi.emo.resp.plot <- ggplot(hi.emo.resp, aes(Condition, ReactionTime, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-
-# lo.neu.resp.plot
-
-# hi.neu.resp.plot
-
-#lo.emo.resp.plot
-
-# hi.emo.resp.plot
-
 ```
@@
 
-``` {r MAD resp, include = FALSE}
-### assess for normality ###
-shapiro.test(data$lo.neu.sur_n_MAD) ## normal
-shapiro.test(data$lo.neu.sur_p_MAD) ## non-normal
-shapiro.test(data$hi.neu.sur_n_MAD) ## barely normal (.058)
-shapiro.test(data$hi.neu.sur_p_MAD) ## normal
-shapiro.test(data$lo.emo.sur_n_MAD) ## non-normal
-shapiro.test(data$lo.emo.sur_p_MAD) ## barely normal (.068)
-shapiro.test(data$hi.emo.sur_n_MAD) ## non-normal
-shapiro.test(data$hi.emo.sur_p_MAD) ## normal
-
-### t-test for pos ratings vs. neg ratings
-wilcox.test(data$lo.neu.sur_n_MAD, data$lo.neu.sur_p_MAD, paired = TRUE) ### different 
-wilcox.test(data$hi.neu.sur_n_MAD, data$hi.neu.sur_p_MAD, paired = TRUE) ### trending
-wilcox.test(data$lo.emo.sur_n_MAD, data$lo.emo.sur_p_MAD, paired = TRUE) ### non-sig
-wilcox.test(data$hi.emo.sur_n_MAD, data$hi.emo.sur_p_MAD, paired = TRUE) ### non-sig
-
-t.test(data$lo.neu.sur_n_MAD, data$lo.neu.sur_p_MAD, paired = TRUE) ### different 
-t.test(data$hi.neu.sur_n_MAD, data$hi.neu.sur_p_MAD, paired = TRUE) ### trending
-t.test(data$lo.emo.sur_n_MAD, data$lo.emo.sur_p_MAD, paired = TRUE) ### non-sig
-t.test(data$hi.emo.sur_n_MAD, data$hi.emo.sur_p_MAD, paired = TRUE) ### non-sig
-
-### make long ###
-lo.neu.resp.MAD <- gather(data, key = "Condition", value =  "MAD",
-                    lo.neu.sur_n_MAD, lo.neu.sur_p_MAD)
-lo.emo.resp.MAD  <- gather(data, key = "Condition", value =  "MAD",
-                    lo.emo.sur_n_MAD, lo.emo.sur_p_MAD)
-hi.neu.resp.MAD  <- gather(data, key = "Condition", value =  "MAD",
-                    hi.neu.sur_n_MAD, hi.neu.sur_p_MAD)
-hi.emo.resp.MAD  <- gather(data, key = "Condition", value =  "MAD",
-                    hi.emo.sur_n_MAD, hi.emo.sur_p_MAD)
-
-lo.neu.resp.MAD$Condition <- as.factor(lo.neu.resp.MAD$Condition)
-lo.emo.resp.MAD$Condition <- as.factor(lo.emo.resp.MAD$Condition)
-hi.neu.resp.MAD$Condition <- as.factor(hi.neu.resp.MAD$Condition)
-hi.emo.resp.MAD$Condition <- as.factor(hi.emo.resp.MAD$Condition)
-
-lo.neu.resp.MAD.plot <- ggplot(lo.neu.resp.MAD, aes(Condition, MAD, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-
-lo.emo.resp.MAD.plot <- ggplot(lo.emo.resp.MAD, aes(Condition, MAD, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-
-hi.neu.resp.MAD.plot <- ggplot(hi.neu.resp.MAD, aes(Condition, MAD, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-
-hi.emo.resp.MAD.plot <- ggplot(hi.emo.resp.MAD, aes(Condition, MAD, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean", na.rm = TRUE) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-
-lo.neu.resp.MAD.plot
-lo.emo.resp.MAD.plot
-hi.neu.resp.MAD.plot
-hi.emo.resp.MAD.plot
-```
 # Discussion

### 2019-09-06 Manuscript/Manuscript.Rmd
Cleaned up scripts
Made a MERP specific data cleaning script...

Starting to polish methods & results.

@@
 classoption       : "man"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 ---
@@
 ## Participants
-58 subjects were recruited from the University of Nebraska-Lincoln.
+``` {r read data}
+data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-09-06_12-18-56.csv")
+```
+Fifty-eight subjects were recruited from the undergraduate research pool at the University of Nebraska-Lincoln.
+The data from eight subjects were excluded due to technical difficulties resulting from an error in one of the experiment scripts.
+This left 50 individuals in the final sample for analysis.
+The mean age of the remaining sample was `r printnum(mean(data$age))` (`r printnum(sd(data$age))`), a majority of participants were female (`r printnum((sum(data$sex == "Female") / nrow(data))*100)`%), and all were white/caucasian without hispanic/Latinx ethnicity.
 All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the local Institutional Review Board (Approval #20141014670EP).
-The data from eight subjects were excluded due to technical difficulties or an error in the experiment script.
-This left 50 individuals in the final sample.
+Each participant received course credit for completing the study.
 
@@
 ```
-The stimuli included faces taken from the NimStim [@tottenham_nimstim_2009] and Karolinska Directed Emotional Faces [@lundqvist_karolinska_1998] stimuli sets.
+The stimuli included faces taken from the NimStim [@tottenham_nimstim_2009] and Karolinska Directed Emotional Faces [@lundqvist_karolinska_1998] stimuli sets, as in previous work [@neta_primacy_2010; @brown_cortisol_2017].
 The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly.
-The scenes were taken from the International Affective Picture System [@lang_international_2008].
+The scene stimuli were selected from the International Affective Picture System [@lang_international_2008].
 A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices.
@@
 ## Procedure
-Participants were randomly assigned to complete one of the task versions.
-The tasks included 144 [^1] trials split between working memory probe and face rating trials.
-On each trial, participants first viewed an image matrix of either neutral or emotional images, which the participants were instructed to remember for the duration of the trial.
-The image matrix was presented for four seconds and the images were swapped from low and high load matrices across versions of the task.
+After arriving at the lab, participants provided informed consent prior to completing the task.
+Participants were randomly assigned to complete one of the task versions, which included 144 [^1] trials split between working memory probe and face rating trials.
+The trials were self-initiated; the participant clicked a "start" button at the bottom of the screen at the beginning of each trial.
+After initiating the trial, participants viewed an image matrix of either neutral or emotional images, which the participants were instructed to remember for the duration of the trial.
+The image matrix was presented for four seconds and the image was either a low or high load matrix consisting of either emotional (equal positive and negative) or neutral images.
 After the image matrix a happy, angry, or surprised face appeared for one second and the participants rated the face by clicking on either the positive or negative response option.
@@
 ```{r import data and analyze ratings, include = FALSE, echo = TRUE}
-data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-08-14_08-52-46.csv")
+
 ### remove psych disorders ### Ask maital?
@@
 [^2]: These results are qualitatively the same when analyzing these data with a repeated measures ANOVA.
-
-## Reaction times
-```{r analyze RTs, include = FALSE}
-## assess normality ###
-shapiro.test(data$lo.neu.sur_RT)
-shapiro.test(data$hi.neu.sur_RT)
-shapiro.test(data$lo.emo.sur_RT)
-shapiro.test(data$hi.emo.sur_RT)
-
-### make long ###
-data.long <- gather(data, key = "Condition", value = "ReactionTime",
-                    lo.neu.sur_RT, hi.neu.sur_RT,
-                    lo.emo.sur_RT, hi.emo.sur_RT)
-
-### make factors ###
-data.long$Load <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Low",
-                         ifelse(data.long$Condition == "lo.emo.sur_RT", "Low",
-                                ifelse(data.long$Condition == "hi.neu.sur_RT", "High",
-                                       ifelse(data.long$Condition == "hi.emo.sur_RT", "High", ""))))
-
-data.long$Type <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Neutral",
-                         ifelse(data.long$Condition == "lo.emo.sur_RT", "Emotional",
-                                ifelse(data.long$Condition == "hi.neu.sur_RT", "Neutral",
-                                       ifelse(data.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
-
-### make w/in subjs factors ###
-data.long$subjID <- as.factor(data.long$subjID)
-
-### traditional ANOVA ###
-RTaov <- with(data.long,
-                   aov(ReactionTime ~ (Load * Type) +
-                       Error(subjID / (Load * Type))), contrasts = contr.sum())
-summary(RTaov)
-RTaov <- tidy(RTaov)
-```
-To assses for normality, the data were first tested with Shapiro-Wilk's test.
-All conditions appeared to be sampled from normal distributions (p's > .300).
-A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs.
-There was a trend towards a main effect of domain, F(`r (RTaov$df[which(RTaov$term == "Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Type")])`.
-There was no effect of load, F(`r (RTaov$df[which(RTaov$term == "Load")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Load")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Load")])`, nor any interaction between load and domain, F(`r (RTaov$df[which(RTaov$term == "Load:Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Load:Type")])`, p = `r printnum(RTaov$p.value[which(RTaov$term == "Load:Type")])`.
-
-```{r plot RT data, include = TRUE}
-ggplot(data.long, aes(Condition, `ReactionTime`, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean") +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
-```
-Next, we tested for reaction time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition.
-A large proportion of the conditions were not normally distributed, thus we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs.
-This difference was significant *only* for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (`r printp(lo.neu.RT.pvn$p.value)`).
-All other comparisons were not significant (p's > .200).
-Further, this effect survived Bonferroni correction (p = `r printp(.05 / 4)`).
 

### 2019-09-06 Manuscript/Manuscript.tex
Cleaned up scripts
Made a MERP specific data cleaning script...

Starting to polish methods & results.

@@
 
-58 subjects were recruited from the University of Nebraska-Lincoln.
+Fifty-eight subjects were recruited from the undergraduate research pool at the University of Nebraska-Lincoln.
+The mean age of the sample was 18.82 (1.19), a majority of participants were female (82.00\%).
 All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the local Institutional Review Board (Approval \#20141014670EP).
+All participants received course credit for completing the study.
 The data from eight subjects were excluded due to technical difficulties or an error in the experiment script.
@@
 
-We used R (Version 3.6.0; {\textbf{???}}) and the R-packages * \}dplyr* {[}@ \}R-dplyr{]}, \emph{broom} (Version 0.5.2; {\textbf{???}}), \emph{forcats} (Version 0.4.0; {\textbf{???}}), \emph{ggplot2} (Version 3.1.1; {\textbf{???}}), \emph{lattice} (Version 0.20.38; {\textbf{???}}), \emph{mousetrap} (Version 3.1.2; {\textbf{???}}), \emph{openxlsx} (Version 4.1.0; {\textbf{???}}), \emph{papaja} (Version 0.1.0.9842; {\textbf{???}}), \emph{plyr} (Version 1.8.4; @ \}R-dplyr; {\textbf{???}}), \emph{purrr} (Version 0.3.2; {\textbf{???}}), \emph{readr} (Version 1.3.1; {\textbf{???}}), \emph{readxl} (Version 1.3.1; {\textbf{???}}), \emph{Rmisc} (Version 1.5; {\textbf{???}}), \emph{stringr} (Version 1.4.0; {\textbf{???}}), \emph{tibble} (Version 2.1.3; {\textbf{???}}), \emph{tidyr} (Version 0.8.3.9000; {\textbf{???}}), and \emph{tidyverse} (Version 1.2.1; {\textbf{???}}) for all our analyses.
+We used R (Version 3.6.0; {\textbf{???}}) and the R-packages * \}dplyr* {[}@ \}R-dplyr{]}, \emph{BayesFactor} (Version 0.9.12.4.2; {\textbf{???}}), \emph{broom} (Version 0.5.2; {\textbf{???}}), \emph{circlize} (Version 0.4.6; {\textbf{???}}), \emph{coda} (Version 0.19.2; {\textbf{???}}), \emph{cstab} (Version 0.2.2; {\textbf{???}}), \emph{diptest} (Version 0.75.7; {\textbf{???}}), \emph{dotCall64} (Version 1.0.0; {\textbf{???}}; {\textbf{???}}), \emph{fastcluster} (Version 1.1.25; {\textbf{???}}), \emph{fields} (Version 9.8.3; {\textbf{???}}), \emph{forcats} (Version 0.4.0; {\textbf{???}}), \emph{foreach} (Version 1.4.7; {\textbf{???}}), \emph{ggplot2} (Version 3.1.1; {\textbf{???}}), \emph{jpeg} (Version 0.1.8; {\textbf{???}}), \emph{lattice} (Version 0.20.38; {\textbf{???}}), \emph{magrittr} (Version 1.5; {\textbf{???}}), \emph{maps} (Version 3.3.0; {\textbf{???}}), \emph{Matrix} (Version 1.2.17; {\textbf{???}}), \emph{mousetrap} (Version 3.1.2; {\textbf{???}}), \emph{openxlsx} (Version 4.1.0; {\textbf{???}}), \emph{papaja} (Version 0.1.0.9842; {\textbf{???}}), \emph{plyr} (Version 1.8.4; @ \}R-dplyr; {\textbf{???}}), \emph{pracma} (Version 2.2.5; {\textbf{???}}), \emph{processx} (Version 3.3.1; {\textbf{???}}), \emph{psych} (Version 1.8.12; {\textbf{???}}), \emph{purrr} (Version 0.3.2; {\textbf{???}}), \emph{RColorBrewer} (Version 1.1.2; {\textbf{???}}), \emph{Rcpp} (Version 1.0.1; {\textbf{???}}; {\textbf{???}}), \emph{readbulk} (Version 1.1.2; {\textbf{???}}), \emph{readr} (Version 1.3.1; {\textbf{???}}), \emph{readxl} (Version 1.3.1; {\textbf{???}}), \emph{Rmisc} (Version 1.5; {\textbf{???}}), \emph{scales} (Version 1.0.0; {\textbf{???}}), \emph{spam} (Version 2.2.2; {\textbf{???}}; {\textbf{???}}; {\textbf{???}}), \emph{stringr} (Version 1.4.0; {\textbf{???}}), \emph{tibble} (Version 2.1.3; {\textbf{???}}), \emph{tidyr} (Version 0.8.3.9000; {\textbf{???}}), \emph{tidyverse} (Version 1.2.1; {\textbf{???}}), and \emph{yarrr} (Version 0.1.5; {\textbf{???}}) for all our analyses.
 Data preprocessing was completed in R using the mousetrap package ({\textbf{???}}).
@@
 Distributions of ratings were first tested for normality using Shapiro-Wilk's test.
-The results of all four tests were highly significant (p's \textless{} .001), so non-parametric tests were used for data analysis.
-Friedman's test results showed significantly different distributions across the conditions \(\chi^{2}\)(3.00) = 27.79, p \textless{} .001.
-Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content.
+The results of all four tests were significant (p's \textless{} .001), so non-parametric tests were used for data analysis.
+Friedman's test results showed significantly different rank-order distributions across the conditions \(\chi^{2}\)(3.00) = 27.79, p \textless{} .001.
+Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content, and this was true for both low and high loads.
 Low emotional load ratings were significantly more negative than low, Z = 3.27, p = .001, neutral and high, Z = 3.67, p \textless{} .001, neutral loads.
@@
 
-\hypertarget{reaction-times}{%
-\subsection{Reaction times}\label{reaction-times}}
-
-To assses for normality, the data were first tested with Shapiro-Wilk's test.
-All conditions appeared to be sampled from normal distributions (p's \textgreater{} .08).
-A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs.
-There was a trend towards a main effect of type, F(1, 49) = 2.97, p = 0.09.
-However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons.
-There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = .
-One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = .
-All other comparisons were non-significant (p's \textgreater{} .
-
-\includegraphics{Manuscript_files/figure-latex/plot RT data-1.pdf}
-
-Next, we tested for reaction time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition.
-Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs.
-This difference was significant \emph{only} for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (.009).
-All other comparisons were not significant (p's \textgreater{} .200).
-Further, this effect survived Bonferroni correction (p = .012).
-
 \includegraphics{Manuscript_files/figure-latex/MAD plot-1.pdf}
@@
 There was a significant effect of load, F(1.00,196.00) = 5.51, p = .020, such that MDs under high load were larger than trials with low load.
-There was no significant effect of domain on MDs, F(1.00 196.00) = 0.01, p = .912, nor an interaction of load by domain.
-\# Discussion
+There was no significant effect of domain on MDs, F(1.00 196.00) = 0.01, p = .912, nor an interaction of load by domain, F(1.00 196.00) = 0.00, p = .960.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
 The effect of high vs.~low load is still not apparent in these data, just like Mattek et al.~2016.

### 2019-09-06 ExtraAnalyses_FromMS.R

@@ -1,0 +1,51 @@
+## Reaction times
+```{r analyze RTs, include = FALSE}
+## assess normality ###
+shapiro.test(data$lo.neu.sur_RT)
+shapiro.test(data$hi.neu.sur_RT)
+shapiro.test(data$lo.emo.sur_RT)
+shapiro.test(data$hi.emo.sur_RT)
+
+### make long ###
+data.long <- gather(data, key = "Condition", value = "ReactionTime",
+                    lo.neu.sur_RT, hi.neu.sur_RT,
+                    lo.emo.sur_RT, hi.emo.sur_RT)
+
+### make factors ###
+data.long$Load <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Low",
+                         ifelse(data.long$Condition == "lo.emo.sur_RT", "Low",
+                                ifelse(data.long$Condition == "hi.neu.sur_RT", "High",
+                                       ifelse(data.long$Condition == "hi.emo.sur_RT", "High", ""))))
+
+data.long$Type <- ifelse(data.long$Condition == "lo.neu.sur_RT", "Neutral",
+                         ifelse(data.long$Condition == "lo.emo.sur_RT", "Emotional",
+                                ifelse(data.long$Condition == "hi.neu.sur_RT", "Neutral",
+                                       ifelse(data.long$Condition == "hi.emo.sur_RT", "Emotional", ""))))
+
+### make w/in subjs factors ###
+data.long$subjID <- as.factor(data.long$subjID)
+
+### traditional ANOVA ###
+RTaov <- with(data.long,
+              aov(ReactionTime ~ (Load * Type) +
+                    Error(subjID / (Load * Type))), contrasts = contr.sum())
+summary(RTaov)
+RTaov <- tidy(RTaov)
+```
+
+To assses for normality, the data were first tested with Shapiro-Wilk's test. All conditions appeared to be sampled from normal distributions (p's > .300). 
+A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs. There was a trend towards a main effect of
+domain, F(`r (RTaov$df[which(RTaov$term == "Type")])`, `r (RTaov$df[which(RTaov$stratum == "subjID")])`) = `r printnum(RTaov$statistic[which(RTaov$term == "Type")])`,
[…]

### 2019-09-06 data_cleaning_MERP.R

@@ -1,0 +1,419 @@
+### set working directory to MouseTrap Demo folder ###
+setwd("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads")
+
+if (!require("processx")) install.packages("processx")
+
+### load the packages... This needs to be done every time. ###
+{suppressPackageStartupMessages(library(mousetrap)) 
+  suppressPackageStartupMessages(library(foreach))
+  suppressPackageStartupMessages(library(tidyverse))
+  suppressPackageStartupMessages(library(readbulk))
+  suppressPackageStartupMessages(library(plyr))
+  suppressPackageStartupMessages(library(utils))
+  suppressPackageStartupMessages(library(stats))
+  suppressPackageStartupMessages(library(pracma))
+  suppressPackageStartupMessages(library(tidyr))
+  suppressPackageStartupMessages(library(magrittr))
+  suppressPackageStartupMessages(library(graphics))
+  suppressPackageStartupMessages(library(grDevices))
+  suppressPackageStartupMessages(library(ggplot2))
+  suppressPackageStartupMessages(library(scales))
+  suppressPackageStartupMessages(library(psych))
+  suppressPackageStartupMessages(library(Rcpp))
+  suppressPackageStartupMessages(library(diptest))
+  suppressPackageStartupMessages(library(RColorBrewer))
+  suppressPackageStartupMessages(library(cstab))
+  suppressPackageStartupMessages(library(fastcluster))
+  suppressPackageStartupMessages(library(parallel))
+  suppressPackageStartupMessages(library(fields))
+  suppressPackageStartupMessages(library(readxl))
+  suppressPackageStartupMessages(library(yarrr))
+}
+
+### import session two files ###
+{### set1va ###
+  set1.va.files.list <- list.files(path = "/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/set1_task_vA", pattern = "*.mt", full.names = TRUE,
+                                   recursive = FALSE)
+  set1.va.files <- read_bulk("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/set1_task_vA/", fun = read_mt, 
+                             extension = ".mt")
+  ### set1.va has incorrectly labelled trials... we'll need to import the correct trial order from another file ###
[…]

### 2019-09-11 Manuscript/Manuscript.Rmd
finalizing word list

@@
 The mean age of the remaining sample was `r printnum(mean(data$age))` (`r printnum(sd(data$age))`), a majority of participants were female (`r printnum((sum(data$sex == "Female") / nrow(data))*100)`%), and all were white/caucasian without hispanic/Latinx ethnicity.
-All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the local Institutional Review Board (Approval #20141014670EP).
+All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the University of Nebraska-Lincoln Institutional Review Board (Approval #20141014670EP).
 Each participant received course credit for completing the study.
@@
 ```
-The stimuli included faces taken from the NimStim [@tottenham_nimstim_2009] and Karolinska Directed Emotional Faces [@lundqvist_karolinska_1998] stimuli sets, as in previous work [@neta_primacy_2010; @brown_cortisol_2017].
+The stimuli included faces from the NimStim [@tottenham_nimstim_2009] and Karolinska Directed Emotional Faces [@lundqvist_karolinska_1998] stimuli sets, as in previous work [@neta_primacy_2010; @brown_cortisol_2017].
 The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly.
@@
 
-### Software
-The task was completed in MouseTracker [@freeman_mousetracker:_2010] and participants used a mouse to click the appropriate response for the face ratings (i.e., "POSITIVE" or "NEGATIVE") and the memory probe (i.e., "YES" or "NO").
-
 ## Procedure
@@
 Participants were randomly assigned to complete one of the task versions, which included 144 [^1] trials split between working memory probe and face rating trials.
-The trials were self-initiated; the participant clicked a "start" button at the bottom of the screen at the beginning of each trial.
-After initiating the trial, participants viewed an image matrix of either neutral or emotional images, which the participants were instructed to remember for the duration of the trial.
-The image matrix was presented for four seconds and the image was either a low or high load matrix consisting of either emotional (equal positive and negative) or neutral images.
-After the image matrix a happy, angry, or surprised face appeared for one second and the participants rated the face by clicking on either the positive or negative response option.
-After the face rating, a single image probe appeared, and participants indicated whether or not the image probe was present in the previous image matrix.
+The task was completed using MouseTracker software [@freeman_mousetracker:_2010] and participants responded with a mouse to indicate the appropriate response for the face ratings (i.e., "POSITIVE" or "NEGATIVE") and the memory probe (i.e., "YES" or "NO").
+The trials were self-initiated; that is, the participant clicked a "start" button at the bottom of the screen at the beginning of each trial at their own pace.
+After initiating the trial, a fixation cross appeared (1000 ms), then participants viewed an image matrix, which the participants were instructed to remember for the duration of the trial.
+The image matrix was presented for 4000 ms and the image was either a low or high load matrix consisting of either emotional (equal positive and negative) or neutral images.
+After the image matrix a happy, angry, or surprised face appeared for 1000 ms and the participants rated the face by clicking on either the positive or negative response option.
+After the face rating, a single image probe appeared (5000 ms), and participants indicated whether or not the image probe was present in the previous image matrix.
 
@@
 
-Prior to completing the analyses, the data were assessed for normality using the Shapiro-Wilks test.
-Data that met the normality assumption were submitted to repeated measures ANOVA, while data that failed to meet this assumption was analyzed using non-parametric tests.
+Prior to completing the analyses, all data were assessed for normality using Shapiro-Wilks tests.
 We tested for differences in valence bias among the different working memory load conditions.
 Friedman's test was used to assess overall differences and pairwise comparisons were completed using Wilcoxon signed rank tests using Bonferroni correction.
-The same analysis strategy was also used to assess differences in reaction times, collapsed across both positive and negative interpretations of surprised facial expressions.
-Finally, we checked for differences between reaction times for both positive and negative ratings of surprise in each working memory load condition.
-Due to a large amount of missing data (almost 50% of the subjects), as a result of some subjects only choosing the positive or negative response option in a given working memory load condition, we were unable to analyze these data with Friedman's test.
-Thus, we conducted a series of Wilcoxon signed rank tests for each of the four conditions with Bonferroni correction.
+Next, we tested for differences among maximum deviations in each working memory load condition using a load (low, high) X domain (emotional, neutral) repeated-measures ANOVA.
 
@@
 Distributions of ratings were first tested for normality using Shapiro-Wilk's test.
-The results of all four tests were significant (p's < .001), so non-parametric tests were used for data analysis.
+The results of all four tests were highly significant (p's < .001), so non-parametric tests were used for data analysis.
 Friedman's test results showed significantly different rank-order distributions across the conditions $\chi^{2}$(`r (printnum(friedman.results$parameter))`) = `r printnum(friedman.results$statistic)`, p `r printp(friedman.results$p.value)`.
@@
 The same was true for high emotional load ratings and low, Z = `r (printnum(hi.emo.v.lo.neu$z_val))`, p `r (printp(hi.emo.v.lo.neu$p.value))`, and high, Z = `r (printnum(hi.emo.v.hi.neu$z_val))`, p `r (printp(hi.emo.v.hi.neu$p.value))`, neutral loads.
-However, there was no discernable effect of load.
+However, there was no effect of load.
 That is, the comparisons between low and high load ratings for both emotional, Z = `r (printnum(lo.emo.v.hi.emo$z_val))`, p = `r (printp(lo.emo.v.hi.emo$p.value))`, and neutral, Z = `r (printnum(lo.neu.v.hi.neu$z_val))`, p = `r (printp(lo.neu.v.hi.neu$p.value))`, load ratings were not significantly different [^2].
+<!-- double check that this is true for the repeated measures ANOVA analysis too -->
+``` {r plot figure 1, include = TRUE}
+friedman.data$Condition <- factor(friedman.data$Condition, levels = c("lo.emo.sur_rate", "hi.emo.sur_rate",
+                                                                      "lo.neu.sur_rate", "hi.neu.sur_rate"))
+friedman.data$Condition <- recode(friedman.data$Condition, "lo.emo.sur_rate" = "Low Emotional", "hi.emo.sur_rate" = "High Emotional",
+                                                            "lo.neu.sur_rate" = "Low Neutral", "hi.neu.sur_rate" = "High Neutral")
+friedman.data$`Percent Negative Ratings` <- friedman.data$`Percent Negative Ratings` * 100
+ggplot(friedman.data, aes(Condition, `Percent Negative Ratings`, fill = Condition)) +
+  geom_bar(stat = "summary", fun.y = "mean") +
+  scale_fill_manual(values = c("#0d7378", "#21e1eb", "#498526", "#65e01d")) + 
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1) +
+  expand_limits(y=c(0, 100)) +
+  theme(axis.text.x=element_blank()) +
+  theme_apa()
 
-``` {r plot figure 1, include = TRUE}
-ggplot(friedman.data, aes(Condition, `Percent Negative Ratings`, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean") +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
 ```
@@
 ```
+Next, we assessed differences in maximum absolute deviation (MD) across the working memory trial conditions.
+While one of the conditions, low emotional MD, was not normally distributed (p = .024), all other conditions were normally distributed and repeated-measures ANOVA was used to analyze the MDs across conditions.
+There was a significant effect of load, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "load")])`,`r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "load")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "load")])`, such that MDs under high load were larger than trials with low load.
+There was no significant effect of domain on MDs, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "type")])` `r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "type")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "type")])`, nor an interaction of load by domain, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "load:type")])` `r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "load:type")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "load:type")])`.
+``` {r MAD plot, include = TRUE}
+MAD.long$Condition <- factor(MAD.long$Condition, levels = c("lo.emo.sur_MAD", "hi.emo.sur_MAD",
+                                                                      "lo.neu.sur_MAD", "hi.neu.sur_MAD"))
+MAD.long$Condition <- recode(MAD.long$Condition, "lo.emo.sur_MAD" = "Low Emotional", "hi.emo.sur_MAD" = "High Emotional",
+                                                            "lo.neu.sur_MAD" = "Low Neutral", "hi.neu.sur_MAD" = "High Neutral")
+ggplot(MAD.long, aes(Condition, MAD, fill = Condition)) +
+  geom_bar(stat = "summary", fun.y = "mean") +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1) +
+  scale_fill_manual(values = c("#0d7378", "#21e1eb", "#498526", "#65e01d")) + 
+  theme_apa() +
+  theme(axis.text.x=element_blank())
 
-``` {r MAD plot, include = TRUE}
-ggplot(MAD.long, aes(Condition, MAD, fill = as.factor(Condition))) +
-  geom_bar(stat = "summary", fun.y = "mean") +
-  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1)
 ```
@@
 ```
-Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
-While one of the conditions, low emotional MDs, was not normally distributed (p = .024), all other conditions were normally distributed and repeated-measures ANOVA was used to analyze the MDs across conditions.
-There was a significant effect of load, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "load")])`,`r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "load")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "load")])`, such that MDs under high load were larger than trials with low load.
-There was no significant effect of domain on MDs, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "type")])` `r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "type")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "type")])`, nor an interaction of load by domain, F(`r printnum(MAD.anova$df[which(MAD.anova$term == "load:type")])` `r printnum(MAD.anova$df[which(MAD.anova$term == "Residuals")])`) = `r printnum(MAD.anova$statistic[which(MAD.anova$term == "load:type")])`, p = `r printp(MAD.anova$p.value[which(MAD.anova$term == "load:type")])`.
 

### 2019-09-11 Manuscript/Manuscript.tex
finalizing word list

@@
 Fifty-eight subjects were recruited from the undergraduate research pool at the University of Nebraska-Lincoln.
-The mean age of the sample was 18.82 (1.19), a majority of participants were female (82.00\%).
-All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the local Institutional Review Board (Approval \#20141014670EP).
-All participants received course credit for completing the study.
-The data from eight subjects were excluded due to technical difficulties or an error in the experiment script.
-This left 50 individuals in the final sample.
+The data from eight subjects were excluded due to technical difficulties resulting from an error in one of the experiment scripts.
+This left 50 individuals in the final sample for analysis.
+The mean age of the remaining sample was 18.82 (1.19), a majority of participants were female (82.00\%), and all were white/caucasian without hispanic/Latinx ethnicity.
+All subjects provided written informed consent in accordance with the Declaration of Helsinki and all procedures were approved by the University of Nebraska-Lincoln Institutional Review Board (Approval \#20141014670EP).
+Each participant received course credit for completing the study.
 
@@
 
-The stimuli included faces taken from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets.
+The stimuli included faces from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets, as in previous work ({\textbf{???}}; Brown et al., 2017).
 The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly.
-The scenes were taken from the International Affective Picture System (Lang, Bradley, \& Cuthbert, 2008).
+The scene stimuli were selected from the International Affective Picture System (Lang, Bradley, \& Cuthbert, 2008).
 A total of 288 scenes (72 positive, 72 negative, and 144 neutral) were selected for the image matrices.
@@
 
-\hypertarget{software}{%
-\subsubsection{Software}\label{software}}
-
-The task was completed in MouseTracker (Freeman \& Ambady, 2010) and participants used a mouse to click the appropriate response for the face ratings (i.e., \enquote{POSITIVE} or \enquote{NEGATIVE}) and the memory probe (i.e., \enquote{YES} or \enquote{NO}).
-
 \hypertarget{procedure}{%
@@
 
-Participants were randomly assigned to complete one of the task versions.
-The tasks included 144\footnote{Some versions of the task only included 142 trials due to a programming error.} trials split between working memory probe and face rating trials.
-On each trial, participants first viewed an image matrix of either neutral or emotional images, which the participants were instructed to remember for the duration of the trial.
-The image matrix was presented for four seconds and the images were swapped from low and high load matrices across versions of the task.
-After the image matrix a happy, angry, or surprised face appeared for one second and the participants rated the face by clicking on either the positive or negative response option.
-After the face rating, a single image probe appeared, and participants indicated whether or not the image probe was present in the previous image matrix.
+After arriving at the lab, participants provided informed consent prior to completing the task.
+Participants were randomly assigned to complete one of the task versions, which included 144\footnote{Some versions of the task only included 142 trials due to a programming error.} trials split between working memory probe and face rating trials.
+The task was completed using MouseTracker software (Freeman \& Ambady, 2010) and participants responded with a mouse to indicate the appropriate response for the face ratings (i.e., \enquote{POSITIVE} or \enquote{NEGATIVE}) and the memory probe (i.e., \enquote{YES} or \enquote{NO}).
+The trials were self-initiated; that is, the participant clicked a \enquote{start} button at the bottom of the screen at the beginning of each trial at their own pace.
+After initiating the trial, a fixation cross appeared (1000 ms), then participants viewed an image matrix, which the participants were instructed to remember for the duration of the trial.
+The image matrix was presented for 4000 ms and the image was either a low or high load matrix consisting of either emotional (equal positive and negative) or neutral images.
+After the image matrix a happy, angry, or surprised face appeared for 1000 ms and the participants rated the face by clicking on either the positive or negative response option.
+After the face rating, a single image probe appeared (5000 ms), and participants indicated whether or not the image probe was present in the previous image matrix.
 
@@
 
-Prior to completing the analyses, the data were assessed for normality using the Shapiro-Wilks test.
-Data that met the normality assumption were submitted to repeated measures ANOVA, while data that failed to meet this assumption was analyzed using non-parametric tests.
+Prior to completing the analyses, all data were assessed for normality using Shapiro-Wilks tests.
 We tested for differences in valence bias among the different working memory load conditions.
 Friedman's test was used to assess overall differences and pairwise comparisons were completed using Wilcoxon signed rank tests using Bonferroni correction.
-The same analysis strategy was also used to assess differences in reaction times, collapsed across both positive and negative interpretations of surprised facial expressions.
-Finally, we checked for differences between reaction times for both positive and negative ratings of surprise in each working memory load condition.
-Due to a large amount of missing data (almost 50\% of the subjects), as a result of some subjects only choosing the positive or negative response option in a given working memory load condition, we were unable to analyze these data with Friedman's test.
-Thus, we conducted a series of Wilcoxon signed rank tests for each of the four conditions with Bonferroni correction.
+Next, we tested for differences among maximum deviations in each working memory load condition using a load (low, high) X domain (emotional, neutral) repeated-measures ANOVA.
 
@@
 Distributions of ratings were first tested for normality using Shapiro-Wilk's test.
-The results of all four tests were significant (p's \textless{} .001), so non-parametric tests were used for data analysis.
+The results of all four tests were highly significant (p's \textless{} .001), so non-parametric tests were used for data analysis.
 Friedman's test results showed significantly different rank-order distributions across the conditions \(\chi^{2}\)(3.00) = 27.79, p \textless{} .001.
@@
 The same was true for high emotional load ratings and low, Z = 4.55, p \textless{} .001, and high, Z = 3.81, p \textless{} .001, neutral loads.
-However, there was no discernable effect of load.
+However, there was no effect of load.
 That is, the comparisons between low and high load ratings for both emotional, Z = -1.35, p = .176, and neutral, Z = -0.06, p = .954, load ratings were not significantly different.\footnote{These results are qualitatively the same when analyzing these data with a repeated measures ANOVA.}
-
 \includegraphics{Manuscript_files/figure-latex/plot figure 1-1.pdf}
 
-\includegraphics{Manuscript_files/figure-latex/MAD plot-1.pdf}
-
-Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.
-While one of the conditions, low emotional MDs, was not normally distributed (p = .024), all other conditions were normally distributed and repeated-measures ANOVA was used to analyze the MDs across conditions.
+Next, we assessed differences in maximum absolute deviation (MD) across the working memory trial conditions.
+While one of the conditions, low emotional MD, was not normally distributed (p = .024), all other conditions were normally distributed and repeated-measures ANOVA was used to analyze the MDs across conditions.
 There was a significant effect of load, F(1.00,196.00) = 5.51, p = .020, such that MDs under high load were larger than trials with low load.
 There was no significant effect of domain on MDs, F(1.00 196.00) = 0.01, p = .912, nor an interaction of load by domain, F(1.00 196.00) = 0.00, p = .960.
+\includegraphics{Manuscript_files/figure-latex/MAD plot-1.pdf}
 

### 2019-09-16 Manuscript/Manuscript.Rmd
Update MS

@@
 
-bibliography      : ["CANLab_UNL.bib"]
+bibliography      : ["HarpNetaInPrep.bib"]
 
@@
 Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.
-In fact, facial expressions are seen across cultures [@ekman_constants_1971] and some evidence suggests expressions are innate (cite).
 Often, facial expressions serve as a clear social signal, but this is not always the case.
-While a smile from a friend likely expresses a positive affective state, other cues are not so clear.
-For instance, a surprised facial expression could signal either a positive (e.g., winning the lottery) or negative (e.g., a snake in the woods) affective state.
-In the absence of a larger context, individuals differ in their tendency to interpret surprised facial expressions as either positive or negative.
-Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to both surprised faces and ambiguous scenes [@neta_neural_2013].
-This bias towards positive or negative interpretations is known as one's valence bias.
-Interpreting facial expressions requires both bottom-up (e.g., perceptual input) and top-down (e.g., emotion regulation strategies) processes.
-A growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes, and that arriving at a positive interpretation requires additional, top-down regulatory processes.
-For example, participants reliably rate surprise as negative faster than positive [@neta_dont_2016].
-In fact, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018].
-Perceptual input also contributes to valence bias.
+While a smile likely expresses a positive affective state, other cues are not so clear.
+For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
+When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative.
+Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes [@neta_neural_2013] or even words (Harp, Petro, Brown & Neta, in prep).
+This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.
+
+Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes.
+For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016].
+Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010].
+Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well.
+For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018].
+Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018].
+<!-- Perceptual input also contributes to valence bias.
 In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions.
-In short,
-Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations.
+THIS NEEDS TO BE REWORKED --> In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.
+
+<!-- Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations.
 As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018].
@@
 Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.
+-->
+
+Recent work suggests that working memory, while a functional (single?) system, may be distributed and divisible into domain-specific subsystems (e.g., affective working memory; see @mikels_affective_2019).
+While it is possible to (mostly) isolate perceptual processses (e.g., interpreting emotional facial expressions) under strict laboratory conditions, attention "in the real world" is typically distributed across competing exogenous (e.g., noticing a plane fly above you) and endogenous stimuli (e.g., interoception) (cite).
+Further, these competing stimuli may be either task-revelevant or task-irrelevant (cite).
+The literature reports conflicting results for the role of affect on working memory (see @jackson_enhanced_2009 and @mather_emotional_2006), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes.
+Similarly, working memory also affects emotional processes--converging work suggests that cognitive demands can mitigate negative emotional effects [@dillen_tuning_2008].
+Lavie and colleagues -[@lavie_load_2004] suggest a load theory in which cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands.
+But, how might concurrent working memory demands affect a more malleable process, like interpreting emotional ambiguity?
+
+Obviously, psychological processes do not occur in a void--that is, it would be quite rare to engage only in a face interpretation task. Instead, people are
 
@@
 
+Future work should consider whether the representations of these emotional images in AWM (Reuter-Lorenz), or
+
 \newpage

### 2019-09-19 Manuscript/Manuscript.Rmd
reworking introduction

@@
 # Introduction
+Completion of even simple tasks in daily life require regular recruitment of working memory, and this often happens without consideration of how these working memory demands may affect concurrent processes.
+Many types of information can be held in working memory: strings of numbers, neutral and emotional images, stimulus characteristics like brightness, spatial locations, and more.
+There is debate in the literature around the neurophysiological substrates of working memory and whether this construct is a unified system or comprised of several domain-specific subsystems (see Baddeley, 1986; Shah & Mikaye, 1996).
+Recent work suggests though that working memory does indeed contain domain-specific subsystems (e.g., affective working memory; see @mikels_affective_2019)--or at least that interactions between working memory and visual or affective tasks are variable depending on working memory content.
+Similar domain-specific effects have been observed in a number of other lines of research, including those outside of the working memory domain.
+For example, the Stroop task [@stroop_studies_1935] has been modified to include emotional stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
+Further, neuroimaging work supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.
+non-emotional) task relevancy [@egner_dissociable_2008].
+The present work aims to clarify the interaction of working memory demands on a concurrent and ecologically valid emotionoal task (i.e., interpretations of emotional facial expressions), specifically when that content varies in both amount and affective quality.
+
+There is a large body of research concerning the effects of distractor and task irrelevant stimuli on performance in a variety of tasks [cite, cite].
+Notably, domain-specific interference may further exacerbate these effects compared to domain-general stimuli [@gruber_effects_2001].
+Within an affect-specific context, the literature reports conflicting results for the role of affective stimuli on working memory processing (see @jackson_enhanced_2009 and @mather_emotional_2006), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes.
+The relationship between these systems is bidirectional though, and often times working memory affects affective processing.
+One such way is through dampening emotional responses, and converging work suggests that cognitive demands can mitigate negative emotional effects [@dillen_tuning_2008].
+One explanation for mitigated emotional responding during concurrent working memory demands is load theory.
+This theory posits that cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands [@lavie_load_2004].
+One limitation to this previous work is that the affective processes under study involved clearly interpretable stimuli/feelings.
+A more malleable affective process, such as interpreting ambiguously valenced emotional facial expressions, may offer better understanding of how concurrent working memory demands affect emotional processes.
+
 Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.
@@
 
+Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference.
+Mattek and colleagues [-@mattek_differential_2016] recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories.
+While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias.
+Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
+
+In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains.
+We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials.
+Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
+
 <!-- Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations.
@@
 
-Recent work suggests that working memory, while a functional (single?) system, may be distributed and divisible into domain-specific subsystems (e.g., affective working memory; see @mikels_affective_2019).
-While it is possible to (mostly) isolate perceptual processses (e.g., interpreting emotional facial expressions) under strict laboratory conditions, attention "in the real world" is typically distributed across competing exogenous (e.g., noticing a plane fly above you) and endogenous stimuli (e.g., interoception) (cite).
-Further, these competing stimuli may be either task-revelevant or task-irrelevant (cite).
-The literature reports conflicting results for the role of affect on working memory (see @jackson_enhanced_2009 and @mather_emotional_2006), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes.
-Similarly, working memory also affects emotional processes--converging work suggests that cognitive demands can mitigate negative emotional effects [@dillen_tuning_2008].
-Lavie and colleagues -[@lavie_load_2004] suggest a load theory in which cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands.
-But, how might concurrent working memory demands affect a more malleable process, like interpreting emotional ambiguity?
-
-Obviously, psychological processes do not occur in a void--that is, it would be quite rare to engage only in a face interpretation task. Instead, people are
-
-Understanding the influences on decision making under ambiguous contexts sheds light on the mechanisms responsible for these individual differences.
-in the present study we aim to better understand how concurrent task demands (i.e., working memory load) may influence the cognitive resources used to arrive at more top-down driven interpetations of ambiguity, specifically in an emotional context.
 Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces [@mattek_differential_2016; @neta_dont_2016]. 
@@
 
-Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks [; cite, cite].
+<!-- Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks [; cite, cite].
 Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli [@gruber_effects_2001].
@@
 non-emotional) task relevancy [@egner_dissociable_2008].
-Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference.
-Mattek and colleagues [-@mattek_differential_2016] recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories.
-While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias.
-Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
-In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains.
-We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials.
-Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
-<!-- Even simple tasks (e.g., remembering a phone number) reveal the limits of  human cognition.
-In fact, many researchers believe that there is a magic number of the amount of information able to be held in working memory (7 +- 2 paper).
-Others have focused on the limits of working memory and successful task performance to inform industrial and organizational policies [@sweller_cognitive_1998].
-Despite the large amount of research around working memory and cognitive control, much controversy remains around the mechanisms through which attention to perceptually salient stimuli affect attentional processes and subsequent cognitive control [@lavie_load_2004].
-Specifically, there is a divide amongst researchers that believe cognitive loads either inhibit perceptions of non-relevant stimuli -->
+-->
 

### 2019-09-19 Manuscript/Manuscript.tex
reworking introduction

@@
 
+Completion of even simple tasks in daily life require regular recruitment of working memory, and this often happens without consideration of how these working memory demands may affect concurrent processes.
+Many types of information can be held in working memory: strings of numbers, neutral and emotional images, stimulus characteristics like brightness, spatial locations, and more.
+There is debate in the literature around the neurophysiological substrates of working memory and whether this construct is a unified system or comprised of several domain-specific subsystems (see Baddeley, 1986; Shah \& Mikaye, 1996).
+Recent work suggests though that working memory does indeed contain domain-specific subsystems (e.g., affective working memory; see Mikels and Reuter-Lorenz (2019))--or at least that interactions between working memory and visual or affective tasks are variable depending on working memory content.
+Similar domain-specific effects have been observed in a number of other lines of research, including those outside of the working memory domain.
+For example, the Stroop task (Stroop, 1935) has been modified to include emotional stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
+Further, neuroimaging work supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008).
+The present work aims to clarify the interaction of working memory demands on a concurrent and ecologically valid emotionoal task (i.e., interpretations of emotional facial expressions), specifically when that content varies in both amount and affective quality.
+
+There is a large body of research concerning the effects of distractor and task irrelevant stimuli on performance in a variety of tasks {[}cite, cite{]}.
+Notably, domain-specific interference may further exacerbate these effects compared to domain-general stimuli (Gruber, 2001).
+Within an affect-specific context, the literature reports conflicting results for the role of affective stimuli on working memory processing (see ({\textbf{???}}) and ({\textbf{???}})), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes.
+The relationship between these systems is bidirectional though, and often times working memory affects affective processing.
+One such way is through dampening emotional responses, and converging work suggests that cognitive demands can mitigate negative emotional effects ({\textbf{???}}).
+One explanation for mitigated emotional responding during concurrent working memory demands is load theory.
+This theory posits that cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands (Lavie, Hirst, Fockert, \& Viding, 2004).
+One limitation to this previous work is that the affective processes under study involved clearly interpretable stimuli/feelings.
+A more malleable affective process, such as interpreting ambiguously valenced emotional facial expressions, may offer better understanding of how concurrent working memory demands affect emotional processes.
+
 Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.
-In fact, facial expressions are seen across cultures ({\textbf{???}}) and some evidence suggests expressions are innate (cite).
 Often, facial expressions serve as a clear social signal, but this is not always the case.
-While a smile from a friend likely expresses a positive affective state, other cues are not so clear.
-For instance, a surprised facial expression could signal either a positive (e.g., winning the lottery) or negative (e.g., a snake in the woods) affective state.
-In the absence of a larger context, individuals differ in their tendency to interpret surprised facial expressions as either positive or negative.
-Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to both surprised faces and ambiguous scenes (Neta, Kelley, \& Whalen, 2013).
-This bias towards positive or negative interpretations is known as one's valence bias.
-Interpreting facial expressions requires both bottom-up (e.g., perceptual input) and top-down (e.g., emotion regulation strategies) processes.
-A growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes, and that arriving at a positive interpretation requires additional, top-down regulatory processes.
-For example, participants reliably rate surprise as negative faster than positive (Neta \& Tong, 2016).
-In fact, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity ({\textbf{???}}).
-Perceptual input also contributes to valence bias.
-In one recent study, Neta and colleagues ({\textbf{???}}) showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions.
-In short,\\
-Despite the trait-like nature of this bias (Neta, Norris, \& Whalen, 2009), valence bias may be shifted, at least temporarily, by a number of experimental manipulations.
-As mentioned above, simple manipulations like slowing response times will shift bias ({\textbf{???}}).
-Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor (Brown, Raio, \& Neta, 2017).
-Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock ({\textbf{???}}), suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.
+While a smile likely expresses a positive affective state, other cues are not so clear.
+For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
+When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative.
+Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes (Neta, Kelley, \& Whalen, 2013) or even words (Harp, Petro, Brown \& Neta, in prep).
+This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.
 
-Understanding the influences on decision making under ambiguous contexts sheds light on the mechanisms responsible for these individual differences.
-in the present study we aim to better understand how concurrent task demands (i.e., working memory load) may influence the cognitive resources used to arrive at more top-down driven interpetations of ambiguity, specifically in an emotional context.\\
-Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces (Mattek, Whalen, Berkowitz, \& Freeman, 2016; Neta \& Tong, 2016).
-The valence bias is trait-like (Neta et al., 2009) and generalizes to non-face stimuli (Neta et al., 2013); however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding (Brown et al., 2017; Neta \& Tong, 2016).
-Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology ({\textbf{???}}), at least in children.
-Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety ({\textbf{???}}).
+Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes.
+For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) (Neta \& Tong, 2016).
+Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity ({\textbf{???}}).
+Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well.
+For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity (Neta, Tong, \& Henley, 2018).
+Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation ({\textbf{???}}).
+In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.
 
-Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks {[}; cite, cite{]}.
-Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli (Gruber, 2001).
-This effect holds up in the emotional domain; for example, the Stroop task (Stroop, 1935) has been modified by some researchers to include emotional stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Indeed, neuroimaging work supports the idea that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008).
 Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference.
@@
 While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias.
-Given the task irrelevance of the numeric distractors in Mattek and colleagues' (2016) work, it follows that the resources required for interpreting ambiguity as positive (Neta et al., 2009) may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
+Given the task irrelevance of the numeric distractors in Mattek and colleagues' (2016) work, it follows that the resources required for interpreting ambiguity as positive (Neta, Norris, \& Whalen, 2009) may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
+
 In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains.
@@
 Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
+
+Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces (Mattek et al., 2016; Neta \& Tong, 2016).
+The valence bias is trait-like (Neta et al., 2009) and generalizes to non-face stimuli (Neta et al., 2013); however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding (Brown, Raio, \& Neta, 2017; Neta \& Tong, 2016).
+Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology ({\textbf{???}}), at least in children.
+Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety ({\textbf{???}}).
 
@@
 
+\leavevmode\hypertarget{ref-lavie_load_2004}{}%
+Lavie, N., Hirst, A., Fockert, J.
+W.
+de, \& Viding, E.
+(2004).
+Load theory of selective attention and cognitive control.
+\emph{Journal of Experimental Psychology: General}, \emph{133}(3), 339--354.
+doi:\href{https://doi.org/10.1037/0096-3445.133.3.339}{10.1037/0096-3445.133.3.339}
+
 \leavevmode\hypertarget{ref-lundqvist_karolinska_1998}{}%
@@
 doi:\href{https://doi.org/10.1037/emo0000148}{10.1037/emo0000148}
+
+\leavevmode\hypertarget{ref-mikels_affective_2019}{}%
+Mikels, J.
+A., \& Reuter-Lorenz, P.
+A.
+(2019).
+Affective working memory: An integrative psychological construct.
+\emph{Perspectives on Psychological Science: A Journal of the Association for Psychological Science}, \emph{14}(4), 543--559.
+doi:\href{https://doi.org/10.1177/1745691619837597}{10.1177/1745691619837597}
 
@@
 doi:\href{https://doi.org/10.1037/emo0000181}{10.1037/emo0000181}
+
+\leavevmode\hypertarget{ref-neta_its_2018}{}%
+Neta, M., Tong, T.
+T., \& Henley, D.
+J.
+(2018).
+It's a matter of time (perspectives): Shifting valence responses to emotional ambiguity.
+\emph{Motivation and Emotion}, \emph{42}, 258--266.
+doi:\href{https://doi.org/10.1007/s11031-018-9665-7}{10.1007/s11031-018-9665-7}
 

### 2019-09-24 Manuscript/Manuscript.Rmd
Updated intro

@@
 # Introduction
-Completion of even simple tasks in daily life require regular recruitment of working memory, and this often happens without consideration of how these working memory demands may affect concurrent processes.
-Many types of information can be held in working memory: strings of numbers, neutral and emotional images, stimulus characteristics like brightness, spatial locations, and more.
-There is debate in the literature around the neurophysiological substrates of working memory and whether this construct is a unified system or comprised of several domain-specific subsystems (see Baddeley, 1986; Shah & Mikaye, 1996).
-Recent work suggests though that working memory does indeed contain domain-specific subsystems (e.g., affective working memory; see @mikels_affective_2019)--or at least that interactions between working memory and visual or affective tasks are variable depending on working memory content.
-Similar domain-specific effects have been observed in a number of other lines of research, including those outside of the working memory domain.
-For example, the Stroop task [@stroop_studies_1935] has been modified to include emotional stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Further, neuroimaging work supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.
+## Working memory and load theory
+Despite extensive research on the interaction of working memory and affective processes, there is still debate in the literature concerning how this cognitive process and emotional processes affect one another.
+Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues -[@schmeichel_working_2008] reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli.
+This suggests a connection--perhaps through some shared resource pool--between mitigated emotional responding and larger working memory resource availablility.
+Other work has focused on the effects of moods or affective states on working memory performance.
+For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory [@yang_positive_2012].
+Similarly, working memory processes may alter concurrent affective processes.
+For instance, actively engaging working memory can mitigate emotional responses.
+Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase [@dillen_tuning_2008].
+Additionally, depending on one's levels of trait-rumination, low trait-ruminators are better able to return heart rate and blood pressure to baseline levels when provided with a distractor task following an anger induction [@gerin_role_2006].
+Together, these studies suggest a resource competition between cognitive and emotional processing; that is, when cognitive load demands are high (e.g., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes.
+
+While previous work clearly suggests an inhibitory role for cognitive demands on emotional responses, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli.
+For instance, Schmeichel and colleagues -[@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral and negative sitmuli [@dillen_tuning_2008], or even reducing symptoms of disorders with affective symptoms, such as anxiety [@spangler_little_2017].
+However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the types of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies).
+For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food would be (in)congruent with one's current goals.
+This emotional appraisal is completed under concurrent laod demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.
+If maintaining a goal state or some stimulus in working memory results in a large cognitive (not perceptual) load, then  Lavie's -[@lavie_load_2004] load theory posits that less executive resources are available to regulate incoming perceptual information.
+In turn, this could mean that more readily processed perceptual input (e.g., low spatial frequency images; LSF) might drive decisions under working memory loads.
+
+Emotional stimuli readily capture attention compared to neutral stimuli, even in participants with amygdala damage [@hodsol_attentional_2011; @piech_attentional_2011].
+Given emotional stimuli's priority position in the information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals.
+Indeed, negative emotional content slows performance on an n-back task [@kensinger_effect_2003].
+Other domain-specific effects have been observed in many lines of research, including those beyond the working memory domain.
+For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
+Neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.
 non-emotional) task relevancy [@egner_dissociable_2008].
-The present work aims to clarify the interaction of working memory demands on a concurrent and ecologically valid emotionoal task (i.e., interpretations of emotional facial expressions), specifically when that content varies in both amount and affective quality.
+Given the behavioral and neurological evidence for dissociations of emotional and non-emotional information domains in executive functions (e.g., working memory, inhibitory control), the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent emotional judgments.
 
-There is a large body of research concerning the effects of distractor and task irrelevant stimuli on performance in a variety of tasks [cite, cite].
-Notably, domain-specific interference may further exacerbate these effects compared to domain-general stimuli [@gruber_effects_2001].
+<!-- Frequently, tasks in daily life require recruitment of working memory, but active working memory demands may affect concurrent processing.
+Many types of information can be held in working memory: strings of numbers, images, stimulus characteristics like brightness, spatial locations, and more.
+There is debate in the literature around the substrates of working memory and how this seemingly unitary construct is distributed across domain-specific subsystems (see [@baddeley_working_1986; @shah_separability_1996]).
+Recent work suggests though that working memory may contain more domain-specific subsystems than previously believed (e.g., affective working memory; e.g., @mikels_affective_2019).
+Similar to the work of Shah and colleagues -[@baddeley_working_1986], Mikels (find acutal study) showed ?double dissociation?
+of the affective working memory system from a more visually based working memory (i.e., maintenance of image brightness in memory).
+Similar domain-specific effects have been observed in many other lines of research, including those beyond the working memory domain.
+For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
+Neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.
+non-emotional) task relevancy [@egner_dissociable_2008], suggesting a division of subsystems.
+Given the behavioral and neurological evidence for dissociations of information domains in working memory, task interference and more, the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent emotional judgments (i.e., interpretations of emotional facial expressions).
+-->
+
+<!-- While it is well known that distractors can undermine task performance [@hagen_effect_1967; cite, cite), some evidence suggests a role for domain-specificity in task interference.
+For instance, domain-specific interference further exacerbates these task effects compared to domain-general stimuli [@gruber_effects_2001].
 Within an affect-specific context, the literature reports conflicting results for the role of affective stimuli on working memory processing (see @jackson_enhanced_2009 and @mather_emotional_2006), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes.
@@
 A more malleable affective process, such as interpreting ambiguously valenced emotional facial expressions, may offer better understanding of how concurrent working memory demands affect emotional processes.
+-->
 
-Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.
-Often, facial expressions serve as a clear social signal, but this is not always the case.
-While a smile likely expresses a positive affective state, other cues are not so clear.
-For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
+## The contribution of valence bias
+<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> As mentioned above, individuals differ in their tendency to interpret ambiguously valenced stimuli, like a tempting food item, as either positive or negative.
+<!-- Additionally, facial expressions can serve as ambiguously valenced stimuli.
+While most facial expressions send a clear social signal, this is not always the case.
+While a smile likely expresses a positive affective state, other cues are not so clear.--> This tendency is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes (or items) to quantify this individual difference (CITE).
+Biases towards negativity are related to psychopathology, such as depression and anxiety [@matthews_cognitive_2005]
+
+<!--For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
 When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative.
@@
 This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.
+-->
 
@@
 
+## The present study
 In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains.
@@
 
+Increased working memory demands (i.e., a higher cognitive load) do not always result in poorer performance on concurrent tasks.
+For instance Baddeley -[@baddeley_working_1986] reported that increasing load by adding digits to a rehearsed number did not affect accuracy on a concurrent verbal reasoning task--instead, there was an increase in the latency of response, a potential interference effect that did not alter overall accuracy.
+
 Previous work has shown that more positive interpretations of surprised faces are related to slower RTs.

### 2019-09-24 Manuscript/Manuscript.tex
Updated intro

@@
 
-Completion of even simple tasks in daily life require regular recruitment of working memory, and this often happens without consideration of how these working memory demands may affect concurrent processes.
-Many types of information can be held in working memory: strings of numbers, neutral and emotional images, stimulus characteristics like brightness, spatial locations, and more.
-There is debate in the literature around the neurophysiological substrates of working memory and whether this construct is a unified system or comprised of several domain-specific subsystems (see Baddeley, 1986; Shah \& Mikaye, 1996).
-Recent work suggests though that working memory does indeed contain domain-specific subsystems (e.g., affective working memory; see Mikels and Reuter-Lorenz (2019))--or at least that interactions between working memory and visual or affective tasks are variable depending on working memory content.
-Similar domain-specific effects have been observed in a number of other lines of research, including those outside of the working memory domain.
-For example, the Stroop task (Stroop, 1935) has been modified to include emotional stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Further, neuroimaging work supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008).
-The present work aims to clarify the interaction of working memory demands on a concurrent and ecologically valid emotionoal task (i.e., interpretations of emotional facial expressions), specifically when that content varies in both amount and affective quality.
+\hypertarget{working-memory-and-load-theory}{%
+\subsection{Working memory and load theory}\label{working-memory-and-load-theory}}
 
-There is a large body of research concerning the effects of distractor and task irrelevant stimuli on performance in a variety of tasks {[}cite, cite{]}.
-Notably, domain-specific interference may further exacerbate these effects compared to domain-general stimuli (Gruber, 2001).
-Within an affect-specific context, the literature reports conflicting results for the role of affective stimuli on working memory processing (see ({\textbf{???}}) and ({\textbf{???}})), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes.
-The relationship between these systems is bidirectional though, and often times working memory affects affective processing.
-One such way is through dampening emotional responses, and converging work suggests that cognitive demands can mitigate negative emotional effects ({\textbf{???}}).
-One explanation for mitigated emotional responding during concurrent working memory demands is load theory.
-This theory posits that cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands (Lavie, Hirst, Fockert, \& Viding, 2004).
-One limitation to this previous work is that the affective processes under study involved clearly interpretable stimuli/feelings.
-A more malleable affective process, such as interpreting ambiguously valenced emotional facial expressions, may offer better understanding of how concurrent working memory demands affect emotional processes.
+Despite extensive research on the interaction of working memory and affective processes, there is still debate in the literature concerning how this cognitive process and emotional processes affect one another.
+Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues -({\textbf{???}}) reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli.
+This suggests a connection--perhaps through some shared resource pool--between mitigated emotional responding and larger working memory resource availablility.
+Other work has focused on the effects of moods or affective states on working memory performance.
+For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory ({\textbf{???}}).
+Similarly, working memory processes may alter concurrent affective processes.
+For instance, actively engaging working memory can mitigate emotional responses.
+Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase ({\textbf{???}}).
+Additionally, depending on one's levels of trait-rumination, low trait-ruminators are better able to return heart rate and blood pressure to baseline levels when provided with a distractor task following an anger induction ({\textbf{???}}).
+Together, these studies suggest resource competition between cognitive tasks and emotional processing; that is, when cognitive load demands are high (i.e., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes.
+
+While previous work clearly suggests an inhibitory role for cognitive demands on emotional responses, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli.
+For instance, Schmeichel and colleagues -({\textbf{???}}) showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral and negative sitmuli ({\textbf{???}}), or even reducing symptoms of disorders with affective symptoms, such as anxiety ({\textbf{???}}).
+However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the types of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies).
+For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food would be (in)congruent with one's current goals.
+This emotional appraisal is completed under concurrent laod demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.
+If maintaining a goal state or some stimulus in working memory results in a large cognitive (not perceptual) load, then Lavie's -(Lavie, Hirst, Fockert, \& Viding, 2004) load theory posits that less executive resources are available to regulate incoming perceptual information.
+
+Emotional stimuli readily capture attention compared to neutral stimuli, even in participants with amygdala damage {[}({\textbf{???}}); piech\_attentional\_2011{]}.
+Given emotional stimuli's priority position in the processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals.
+Indeed, negative emotional content slows performance on an n-back task ({\textbf{???}}).
+domain-specific effects have been observed in many other lines of research, including those beyond the working memory domain.
+For example, the Stroop task (Stroop, 1935), a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
+Neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008), suggesting a division of subsystems.
+Given the behavioral and neurological evidence for dissociations of information domains in working memory, task interference and more, the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent emotional judgments.
+
+\hypertarget{the-contribution-of-valence-bias}{%
+\subsection{The contribution of valence bias}\label{the-contribution-of-valence-bias}}
 
@@
 Given the task irrelevance of the numeric distractors in Mattek and colleagues' (2016) work, it follows that the resources required for interpreting ambiguity as positive (Neta, Norris, \& Whalen, 2009) may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
+
+\hypertarget{the-present-study}{%
+\subsection{The present study}\label{the-present-study}}
 
@@
 
+Increased working memory demands (i.e., a higher cognitive load) do not always result in poorer performance on concurrent tasks.
+For instance Baddeley -({\textbf{???}}) reported that increasing load by adding digits to a rehearsed number did not affect accuracy on a concurrent verbal reasoning task--instead, there was an increase in the latency of response, a potential interference effect that did not alter overall accuracy.
+
 Previous work has shown that more positive interpretations of surprised faces are related to slower RTs.
@@
 
-\leavevmode\hypertarget{ref-gruber_effects_2001}{}%
-Gruber, O.
-(2001).
-Effects of domain-specific interference on brain activation associated with verbal working memory task performance.
-\emph{Cerebral Cortex (New York, N.Y.: 1991)}, \emph{11}(11), 1047--1055.
-doi:\href{https://doi.org/10.1093/cercor/11.11.1047}{10.1093/cercor/11.11.1047}
-
 \leavevmode\hypertarget{ref-lang_international_2008}{}%
@@
 doi:\href{https://doi.org/10.1037/emo0000148}{10.1037/emo0000148}
-
-\leavevmode\hypertarget{ref-mikels_affective_2019}{}%
-Mikels, J.
-A., \& Reuter-Lorenz, P.
-A.
-(2019).
-Affective working memory: An integrative psychological construct.
-\emph{Perspectives on Psychological Science: A Journal of the Association for Psychological Science}, \emph{14}(4), 543--559.
-doi:\href{https://doi.org/10.1177/1745691619837597}{10.1177/1745691619837597}
 

### 2019-10-01 Manuscript/Manuscript.Rmd
working on intro

@@
 
-bibliography      : ["HarpNetaInPrep.bib"]
+bibliography      : ["CANLab_UNL.bib"]
 
@@
 ## Working memory and load theory
-Despite extensive research on the interaction of working memory and affective processes, there is still debate in the literature concerning how this cognitive process and emotional processes affect one another.
-Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues -[@schmeichel_working_2008] reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli.
+Despite extensive research on the interaction of working memory and affective processes, there is much to learn concerning how cognitive and emotional processes affect one another.
+Executive functions, including working memory, are related to successful self-regulation, and in turn emotion regulation [@hofmann_executive_2012].
+Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues [-@schmeichel_working_2008] reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli.
 This suggests a connection--perhaps through some shared resource pool--between mitigated emotional responding and larger working memory resource availablility.
 Other work has focused on the effects of moods or affective states on working memory performance.
-For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory [@yang_positive_2012].
-Similarly, working memory processes may alter concurrent affective processes.
-For instance, actively engaging working memory can mitigate emotional responses.
-Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase [@dillen_tuning_2008].
-Additionally, depending on one's levels of trait-rumination, low trait-ruminators are better able to return heart rate and blood pressure to baseline levels when provided with a distractor task following an anger induction [@gerin_role_2006].
-Together, these studies suggest a resource competition between cognitive and emotional processing; that is, when cognitive load demands are high (e.g., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes.
+For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory [@yang_positive_2013].
+Similarly, active working memory processes may alter concurrent affective processes.
+For instance, actively engaging working memory can mitigate emotional responses, particularly to negative stimuli.
+Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase [@van_dillen_tuning_2009].
+Additionally, following an anger induction, those with low trait rumination show faster blood pressure recovery when provided with a distractor task [@gerin_role_2006].
+Together, these studies suggest a resource competition between cognitive and emotional processes; in other words, when cognitive load demands are high (e.g., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes.
 
-While previous work clearly suggests an inhibitory role for cognitive demands on emotional responses, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli.
-For instance, Schmeichel and colleagues -[@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral and negative sitmuli [@dillen_tuning_2008], or even reducing symptoms of disorders with affective symptoms, such as anxiety [@spangler_little_2017].
-However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the types of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies).
-For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food would be (in)congruent with one's current goals.
-This emotional appraisal is completed under concurrent laod demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.
-If maintaining a goal state or some stimulus in working memory results in a large cognitive (not perceptual) load, then  Lavie's -[@lavie_load_2004] load theory posits that less executive resources are available to regulate incoming perceptual information.
-In turn, this could mean that more readily processed perceptual input (e.g., low spatial frequency images; LSF) might drive decisions under working memory loads.
+While previous work suggests an inhibitory effect on some emotional responses during periods with high cognitive demands, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli.
+For instance, Schmeichel and colleagues [-@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral compared to negative sitmuli [@van_dillen_tuning_2009].<!--  Others have even measured symptoms during working memory maintenance of affective symptoms (i.e., typically increased negative affect), such as anxiety [@spangler_little_2017].--> However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the images of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies).
+For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food is (in)congruent with one's current goals.
+This emotional appraisal is completed under concurrent load demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.
+Maintenance of one's goal state, such as a diet, can reduce performance on some components of executive functioning tasks [@shaw_dieting_2004].
+These observations are in line with Lavie and colleague's [-@lavie_load_2004] load theory, which posits that under a large cognitive load less executive resources are available to regulate incoming stimulus information.
+<!-- In turn, this could mean that more readily processed perceptual input (e.g., low spatial frequency images; LSF) might drive decisions under working memory loads.
+-->
 
-Emotional stimuli readily capture attention compared to neutral stimuli, even in participants with amygdala damage [@hodsol_attentional_2011; @piech_attentional_2011].
+Recently, cognitive load theory researchers have tested, and demonstrated, the domain-specificity of load and distractor interference in visual, spatial, and phonological domains [@burnham_components_2014].
+Load interference effects may also transverse other domain componenets, such as emotional compared to neutral memory content.
+Emotional stimuli readily capture attention compared to neutral stimuli, and this is true even in participants with amygdala damage [@hodsoll_attentional_2011; @piech_attentional_2011].
 Given emotional stimuli's priority position in the information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals.
-Indeed, negative emotional content slows performance on an n-back task [@kensinger_effect_2003].
-Other domain-specific effects have been observed in many lines of research, including those beyond the working memory domain.
+Indeed, Kensigner and colleagues [-@kensinger_effect_2003] showed that negative emotional content slows performance on the n-back task.
+Other domain-specific effects have been observed in many lines of executive functions research, including those beyond the working memory domain.
 For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.
+Other neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.
 non-emotional) task relevancy [@egner_dissociable_2008].
-Given the behavioral and neurological evidence for dissociations of emotional and non-emotional information domains in executive functions (e.g., working memory, inhibitory control), the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent emotional judgments.
+Given this evidence for dissociations of emotional and non-emotional information domains in executive functions (e.g., working memory, inhibitory control), the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent interpretations of emotional stimuli with ambiguous valence.
 
@@
 
-## The contribution of valence bias
-<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> As mentioned above, individuals differ in their tendency to interpret ambiguously valenced stimuli, like a tempting food item, as either positive or negative.
+## Interpreting ambiguity
+<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> Individuals differ in their tendency to interpret ambiguously valenced stimuli, like a tempting food item or a surprised facial expression, as either positive or negative.
 <!-- Additionally, facial expressions can serve as ambiguously valenced stimuli.
 While most facial expressions send a clear social signal, this is not always the case.
-While a smile likely expresses a positive affective state, other cues are not so clear.--> This tendency is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes (or items) to quantify this individual difference (CITE).
-Biases towards negativity are related to psychopathology, such as depression and anxiety [@matthews_cognitive_2005]
+While a smile likely expresses a positive affective state, other cues are not so clear.--> This is attributable to these stimuli's predictive value for both positive and negative outcomes.
+For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events.
+This affective bias is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes to quantify this individual difference [@neta_corrugator_2009; @neta_primacy_2010; @neta_neural_2013].
+Chronic negativity biases in memory and attention are related to psychopathology, such as depression and anxiety [@mathews_cognitive_2005], suggesting the importance of understanding the factors that contribute to individuals' biases.
+Importantly, the valence bias is a stable measure with participants showing positively correlated scores across a one year time gap [@neta_corrugator_2009].
+Despite the relative stability of the measure, experimental manipulations are capable of shifting an individuals bias [@brown_cortisol_2017; @neta_through_2018; @neta_its_2018].
 
+Myriad factors contribute to an individual's bias, but the initial interpretation is thought to be negative across individuals.
+Data supporting this initial negativity hypothesis come from many studies.
+For instance, reaction times are faster for negative interpretations of ambiguous stimuli [@neta_dont_2016].
+Additionally, presentation of surprised facial expressions as low spatial frequency images, which are processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010].
+Under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes, and there is evidence to support this as well.
+For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018].
+Evidence from the neuroimaging literature supports the initial negativity hypothesis as well; more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018].
+Perceptual input also contributes to valence bias.
+In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation on the mouth is related to more positive interpretations of surprised faces [@neta_all_2017].
+Further, forcing gaze patterns to match those of the participants with the most negative or positive bias modulated interpretations of surprised expressions [@neta_through_2018].
+In all, valence bias is a useful metric for understanding both trait-like components of individuals' affective biases, as well as gauging the effects of other experimental maniuplations on affective biases.
 <!--For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
@@
 -->
-
-Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes.
+<!-- Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes.
 For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016].
@@
 In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions.
-THIS NEEDS TO BE REWORKED --> In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.
+THIS NEEDS TO BE REWORKED In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.
+-->
 
-Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference.
-Mattek and colleagues [-@mattek_differential_2016] recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories.
-While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias.
-Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
-
-## The present study
-In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains.
-We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials.
+Given the evidence that a regulatory mechanism is necessary for positive interpretations of ambiguity, a demanding cognitive load might interfere with successful regulation.
+Indeed, Mattek and colleagues [-@mattek_differential_2016] recently showed that high levels of cognitive load (i.e., holding either a single or seven digit number in working memory) mitigates mouse trajectory deviations to the modal response.
+However, there was no effect on subjective valence interpretations.
+Just as phonological and visual cognitive loads and distractors showed domain-specificity [@burnham_components_2014], and that domain-speicificity is observed in BOLD data [@egner_dissociable_2008], a domain-specific cognitive load may differentially affect interpretations of ambiguity.
+In other words, there is likely a relationship between the qualities of stimuli held in working memory and effects on concurrent task processing.
+Here, we aim to test the effects of low and high working memory loads in both emotional and neutral domains on valence bias.
+We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials, as the high cognitive demand interferes with the regulatory mechanisms used to arrive at a positive interpretation.
 Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
 
+<!-- domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference.
+Mattek and colleagues [-@mattek_differential_2016]  While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias.
+Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
+-->
 <!-- Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations.
@@
 -->
-
-Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces [@mattek_differential_2016; @neta_dont_2016]. 
-The valence bias is trait-like [@neta_corrugator_2009] and generalizes to non-face stimuli [@neta_neural_2013]; however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding [@brown_cortisol_2017; @neta_dont_2016].
-Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology [@petro_initial_2018], at least in children.
-Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety [@matthews_cognitive_2005].
-
 <!-- Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks [; cite, cite].
@@
 -->
-
 <!-- Notes: Allie showed that depletion doesn't affect ratings, but we thought that there may be an effect of specific domains of depletion (i.e., neutral vs.
@@
 -->
-
 # Methods
@@
   expand_limits(y=c(0, 100)) +
-  theme(axis.text.x=element_blank()) +
-  theme_apa()
+  theme_apa() +
+  theme(axis.text.x=element_blank())
 

### 2019-10-01 Manuscript/Manuscript.tex
working on intro

--- 2019-09-11 Manuscript/Manuscript.tex
@@
 
-Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.
-In fact, facial expressions are seen across cultures ({\textbf{???}}) and some evidence suggests expressions are innate (cite).
-Often, facial expressions serve as a clear social signal, but this is not always the case.
-While a smile from a friend likely expresses a positive affective state, other cues are not so clear.
-For instance, a surprised facial expression could signal either a positive (e.g., winning the lottery) or negative (e.g., a snake in the woods) affective state.
-In the absence of a larger context, individuals differ in their tendency to interpret surprised facial expressions as either positive or negative.
-Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to both surprised faces and ambiguous scenes (Neta, Kelley, \& Whalen, 2013).
-This bias towards positive or negative interpretations is known as one's valence bias.
-Interpreting facial expressions requires both bottom-up (e.g., perceptual input) and top-down (e.g., emotion regulation strategies) processes.
-A growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes, and that arriving at a positive interpretation requires additional, top-down regulatory processes.
-For example, participants reliably rate surprise as negative faster than positive (Neta \& Tong, 2016).
-In fact, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity ({\textbf{???}}).
+\hypertarget{working-memory-and-load-theory}{%
+\subsection{Working memory and load theory}\label{working-memory-and-load-theory}}
+
+Despite extensive research on the interaction of working memory and affective processes, there is much to learn concerning how cognitive and emotional processes affect one another.
+Executive functions, including working memory, are related to successful self-regulation, and in turn emotion regulation (Hofmann, Schmeichel, \& Baddeley, 2012).
+Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues (2008) reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli.
+This suggests a connection--perhaps through some shared resource pool--between mitigated emotional responding and larger working memory resource availablility.
+Other work has focused on the effects of moods or affective states on working memory performance.
+For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory (Yang, Yang, \& Isen, 2013).
+Similarly, active working memory processes may alter concurrent affective processes.
+For instance, actively engaging working memory can mitigate emotional responses, particularly to negative stimuli.
+Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase (Van Dillen, Heslenfeld, \& Koole, 2009).
+Additionally, following an anger induction, those with low trait rumination show faster blood pressure recovery when provided with a distractor task (Gerin, Davidson, Christenfeld, Goyal, \& Schwartz, 2006).
+Together, these studies suggest a resource competition between cognitive and emotional processes; in other words, when cognitive load demands are high (e.g., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes.
+
+While previous work suggests an inhibitory effect on some emotional responses during periods with high cognitive demands, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli.
+For instance, Schmeichel and colleagues (2008) showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral compared to negative sitmuli (Van Dillen et al., 2009).
+However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the images of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies).
+For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food is (in)congruent with one's current goals.
+This emotional appraisal is completed under concurrent load demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.
+Maintenance of one's goal state, such as a diet, can reduce performance on some components of executive functioning tasks (Shaw \& Tiggemann, 2004).
+These observations are in line with Lavie and colleague's (2004) load theory, which posits that under a large cognitive load less executive resources are available to regulate incoming stimulus information.
+
+Recently, cognitive load theory researchers have tested, and demonstrated, the domain-specificity of load and distractor interference in visual, spatial, and phonological domains (Burnham, Sabia, \& Langan, 2014).
+Load interference effects may also transverse other domain componenets, such as emotional compared to neutral memory content.
+Emotional stimuli readily capture attention compared to neutral stimuli, and this is true even in participants with amygdala damage (Hodsoll, Viding, \& Lavie, 2011; Piech et al., 2011).
+Given emotional stimuli's priority position in the information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals.
+Indeed, Kensigner and colleagues (2003) showed that negative emotional content slows performance on the n-back task.
+Other domain-specific effects have been observed in many lines of executive functions research, including those beyond the working memory domain.
+For example, the Stroop task (Stroop, 1935), a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
+Other neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008).
+Given this evidence for dissociations of emotional and non-emotional information domains in executive functions (e.g., working memory, inhibitory control), the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent interpretations of emotional stimuli with ambiguous valence.
+
+\hypertarget{interpreting-ambiguity}{%
+\subsection{Interpreting ambiguity}\label{interpreting-ambiguity}}
+
+Individuals differ in their tendency to interpret ambiguously valenced stimuli, like a tempting food item or a surprised facial expression, as either positive or negative.
+This is attributable to these stimuli's predictive value for both positive and negative outcomes.
+For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events.
+This affective bias is known as one's \emph{valence bias}, and a growing body of work has used both facial expressions and scenes to quantify this individual difference (Neta, Kelley, \& Whalen, 2013; Neta, Norris, \& Whalen, 2009; Neta \& Whalen, 2010).
+Chronic negativity biases in memory and attention are related to psychopathology, such as depression and anxiety (Mathews \& MacLeod, 2005), suggesting the importance of understanding the factors that contribute to individuals' biases.
+Importantly, the valence bias is a stable measure with participants showing positively correlated scores across a one year time gap (Neta et al., 2009).
+Despite the relative stability of the measure, experimental manipulations are capable of shifting an individuals bias (Brown, Raio, \& Neta, 2017; Neta \& Dodd, 2018; Neta et al., 2018).
+
+Myriad factors contribute to an individual's bias, but the initial interpretation is thought to be negative across individuals.
+Data supporting this initial negativity hypothesis come from many studies.
+For instance, reaction times are faster for negative interpretations of ambiguous stimuli (Neta \& Tong, 2016).
+Additionally, presentation of surprised facial expressions as low spatial frequency images, which are processed more readily than high spatial frequency images, biased interpretations towards negativity (Neta \& Whalen, 2010).
+Under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes, and there is evidence to support this as well.
+For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity (Neta et al., 2018).
+Evidence from the neuroimaging literature supports the initial negativity hypothesis as well; more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation (Petro, Tong, Henley, \& Neta, 2018).
 Perceptual input also contributes to valence bias.
-In one recent study, Neta and colleagues ({\textbf{???}}) showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions.
-In short,\\
-Despite the trait-like nature of this bias (Neta, Norris, \& Whalen, 2009), valence bias may be shifted, at least temporarily, by a number of experimental manipulations.
-As mentioned above, simple manipulations like slowing response times will shift bias ({\textbf{???}}).
-Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor (Brown, Raio, \& Neta, 2017).
-Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock ({\textbf{???}}), suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.
+In one recent study, Neta and colleagues (2017) showed that faster intial fixation on the mouth is related to more positive interpretations of surprised faces(Neta et al., 2017).
+Further, forcing gaze patterns to match those of the participants with the most negative or positive bias modulated interpretations of surprised expressions (Neta \& Dodd, 2018).
+In all, valence bias is a useful metric for understanding both trait-like components of individuals' affective biases, as well as gauging the effects of other experimental maniuplations on affective biases.
 
-Understanding the influences on decision making under ambiguous contexts sheds light on the mechanisms responsible for these individual differences.
-in the present study we aim to better understand how concurrent task demands (i.e., working memory load) may influence the cognitive resources used to arrive at more top-down driven interpetations of ambiguity, specifically in an emotional context.\\
-Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces (Mattek, Whalen, Berkowitz, \& Freeman, 2016; Neta \& Tong, 2016).
-The valence bias is trait-like (Neta et al., 2009) and generalizes to non-face stimuli (Neta et al., 2013); however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding (Brown et al., 2017; Neta \& Tong, 2016).
-Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology ({\textbf{???}}), at least in children.
-Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety ({\textbf{???}}).
-
-Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks {[}; cite, cite{]}.
-Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli (Gruber, 2001).
-This effect holds up in the emotional domain; for example, the Stroop task (Stroop, 1935) has been modified by some researchers to include emotional stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Indeed, neuroimaging work supports the idea that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008).
-Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference.
-Mattek and colleagues (2016) recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories.
-While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias.
-Given the task irrelevance of the numeric distractors in Mattek and colleagues' (2016) work, it follows that the resources required for interpreting ambiguity as positive (Neta et al., 2009) may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
-In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains.
-We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials.
+Given the evidence that a regulatory mechanism is necessary for positive interpretations of ambiguity, a demanding cognitive load might interfere with successful regulation.
+Indeed, Mattek and colleagues (2016) recently showed that high levels of cognitive load (i.e., holding either a single or seven digit number in working memory) mitigates mouse trajectory deviations to the modal response.
+However, there was no effect on subjective valence interpretations.
+Just as phonological and visual cognitive loads and distractors showed domain-specificity (Burnham et al., 2014), and that domain-speicificity is observed in BOLD data (Egner et al., 2008), a domain-specific cognitive load may differentially affect interpretations of ambiguity.
+In other words, there is likely a relationship between the qualities of stimuli held in working memory and effects on concurrent task processing.
+Here, we aim to test the effects of low and high working memory loads in both emotional and neutral domains on valence bias.
+We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials, as the high cognitive demand interferes with the regulatory mechanisms used to arrive at a positive interpretation.
 Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
@@
 
-The stimuli included faces from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets, as in previous work ({\textbf{???}}; Brown et al., 2017).
+The stimuli included faces from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets, as in previous work (Brown et al., 2017; Neta \& Whalen, 2010).
 The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly.
@@
 
+Increased working memory demands (i.e., a higher cognitive load) do not always result in poorer performance on concurrent tasks.
+For instance Baddeley -(Baddeley, 1986) reported that increasing load by adding digits to a rehearsed number did not affect accuracy on a concurrent verbal reasoning task--instead, there was an increase in the latency of response, a potential interference effect that did not alter overall accuracy.
+
 Previous work has shown that more positive interpretations of surprised faces are related to slower RTs.
@@
 For instance, \ldots{}
+
+Future work should consider whether the representations of these emotional images in AWM (Reuter-Lorenz), or
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-baddeley_working_1986}{}%
+Baddeley, A. D. (1986). Working memory. \emph{Philosophical Transactions of the Royal Society of London}, \emph{302}(110), 311--324.
+
 \leavevmode\hypertarget{ref-brown_cortisol_2017}{}%
@@
 doi:\href{https://doi.org/10.1038/s41598-017-14846-3}{10.1038/s41598-017-14846-3}
+
+\leavevmode\hypertarget{ref-burnham_components_2014}{}%
+Burnham, B.
+R., Sabia, M., \& Langan, C.
+(2014).
+Components of working memory and visual selective attention.
+\emph{Journal of Experimental Psychology.
+Human Perception and Performance}, \emph{40}(1), 391--403.
+doi:\href{https://doi.org/10.1037/a0033753}{10.1037/a0033753}
 
@@
 
-\leavevmode\hypertarget{ref-gruber_effects_2001}{}%
-Gruber, O.
-(2001).
-Effects of domain-specific interference on brain activation associated with verbal working memory task performance.
-\emph{Cerebral Cortex (New York, N.Y.: 1991)}, \emph{11}(11), 1047--1055.
-doi:\href{https://doi.org/10.1093/cercor/11.11.1047}{10.1093/cercor/11.11.1047}
+\leavevmode\hypertarget{ref-gerin_role_2006}{}%
+Gerin, W., Davidson, K.
+W., Christenfeld, N.
+J.
+S., Goyal, T., \& Schwartz, J.
+E.
+(2006).
+The role of angry rumination and distraction in blood pressure recovery from emotional arousal.
+\emph{Psychosomatic Medicine}, \emph{68}(1), 64--72.
+doi:\href{https://doi.org/10.1097/01.psy.0000195747.12404.aa}{10.1097/01.psy.0000195747.12404.aa}
+
+\leavevmode\hypertarget{ref-hodsoll_attentional_2011}{}%
+Hodsoll, S., Viding, E., \& Lavie, N.
+(2011).
+Attentional capture by irrelevant emotional distractor faces.
+\emph{Emotion}, \emph{11}(2), 346--353.
+doi:\href{https://doi.org/10.1037/a0022771}{10.1037/a0022771}
+
+\leavevmode\hypertarget{ref-hofmann_executive_2012}{}%
+Hofmann, W., Schmeichel, B.
+J., \& Baddeley, A.
+D.
+(2012).
+Executive functions and self-regulation.
+\emph{Trends in Cognitive Sciences}, \emph{16}(3), 174--180.
+doi:\href{https://doi.org/10.1016/j.tics.2012.01.006}{10.1016/j.tics.2012.01.006}
+
+\leavevmode\hypertarget{ref-kensinger_effect_2003}{}%
+Kensinger, E. A., \& Corkin, S. (2003). Effect of negative emotional content on working memory and long-term memory. \emph{Emotion}, 378--393.
 
@@
 
+\leavevmode\hypertarget{ref-lavie_load_2004}{}%
+Lavie, N., Hirst, A., Fockert, J.
+W.
+de, \& Viding, E.
+(2004).
+Load theory of selective attention and cognitive control.
+\emph{Journal of Experimental Psychology: General}, \emph{133}(3), 339--354.
+doi:\href{https://doi.org/10.1037/0096-3445.133.3.339}{10.1037/0096-3445.133.3.339}
+
 \leavevmode\hypertarget{ref-lundqvist_karolinska_1998}{}%
 Lundqvist, D., Flykt, A., \& Öhman, A. (1998). The karolinska directed emotional faces---KDEF (CD ROM)., Stockholm: Karolinska Institute, Departmentof Clinical Neuroscience, PsychologySection.
+
+\leavevmode\hypertarget{ref-mathews_cognitive_2005}{}%
+Mathews, A., \& MacLeod, C.
+(2005).
+Cognitive vulnerability to emotional disorders.
+\emph{Annual Review of Clinical Psychology}, \emph{1}, 167--195.
+doi:\href{https://doi.org/10.1146/annurev.clinpsy.1.102803.143916}{10.1146/annurev.clinpsy.1.102803.143916}
 
@@
 doi:\href{https://doi.org/10.1037/emo0000148}{10.1037/emo0000148}
+
+\leavevmode\hypertarget{ref-neta_through_2018}{}%
+Neta, M., \& Dodd, M.
+D.
+(2018).
+Through the eyes of the beholder: Simulated eye-movement experience (``SEE'') modulates valence bias in response to emotional ambiguity.
+\emph{Emotion}, \emph{18}(8), 1122--1127.
+doi:\href{https://doi.org/10.1037/emo0000421}{10.1037/emo0000421}
 
@@
 
+\leavevmode\hypertarget{ref-neta_its_2018}{}%
+Neta, M., Tong, T.
+T., \& Henley, D.
+J.
+(2018).
+It's a matter of time (perspectives): Shifting valence responses to emotional ambiguity.
+\emph{Motivation and Emotion}, \emph{42}, 258--266.
+doi:\href{https://doi.org/10.1007/s11031-018-9665-7}{10.1007/s11031-018-9665-7}
+
+\leavevmode\hypertarget{ref-neta_all_2017}{}%
+Neta, M., Tong, T.
+T., Rosen, M.
+L., Enersen, A., Kim, M.
+J., \& Dodd, M.
+D.
+(2017).
+All in the first glance: First fixation predicts individual differences in valence bias.
+\emph{Cognition \& Emotion}, \emph{31}(4), 772--780.
+doi:\href{https://doi.org/10.1080/02699931.2016.1152231}{10.1080/02699931.2016.1152231}
+
+\leavevmode\hypertarget{ref-neta_primacy_2010}{}%
+Neta, M., \& Whalen, P.
+J.
+(2010).
+The primacy of negative interpretations when resolving the valence of ambiguous facial expressions.
+\emph{Psychological Science}, \emph{21}(7), 901--907.
+doi:\href{https://doi.org/10.1177/0956797610373934}{10.1177/0956797610373934}
+
+\leavevmode\hypertarget{ref-petro_individual_2018}{}%
+Petro, N.
+M., Tong, T.
+T., Henley, D.
+J., \& Neta, M.
+(2018).
+Individual differences in valence bias: fMRI evidence of the initial negativity hypothesis.
+\emph{Social Cognitive and Affective Neuroscience}, \emph{13}(7), 687--698.
+doi:\href{https://doi.org/10.1093/scan/nsy049}{10.1093/scan/nsy049}
+
+\leavevmode\hypertarget{ref-piech_attentional_2011}{}%
+Piech, R.
+M., McHugo, M., Smith, S.
+D., Dukic, M.
+S., Van Der Meer, J., Abou-Khalil, B., \ldots{} Zald, D.
+H.
+(2011).
+Attentional capture by emotional stimuli is preserved in patients with amygdala lesions.
+\emph{Neuropsychologia}, \emph{49}(12), 3314--3319.
+doi:\href{https://doi.org/10.1016/j.neuropsychologia.2011.08.004}{10.1016/j.neuropsychologia.2011.08.004}
+
+\leavevmode\hypertarget{ref-schmeichel_working_2008}{}%
+Schmeichel, B.
+J., Volokhov, R.
+N., \& Demaree, H.
+A.
+(2008).
+Working memory capacity and the self-regulation of emotional expression and experience.
+\emph{Journal of Personality and Social Psychology}, \emph{95}(6), 1526--1540.
+doi:\href{https://doi.org/10.1037/a0013345}{10.1037/a0013345}
+
+\leavevmode\hypertarget{ref-shaw_dieting_2004}{}%
+Shaw, J., \& Tiggemann, M.
+(2004).
+Dieting and working memory: Preoccupying cognitions and the role of the articulatory control process.
+\emph{British Journal of Health Psychology}, \emph{9}(Pt 2), 175--185.
+doi:\href{https://doi.org/10.1348/135910704773891032}{10.1348/135910704773891032}
+
 \leavevmode\hypertarget{ref-stroop_studies_1935}{}%
@@
 
+\leavevmode\hypertarget{ref-van_dillen_tuning_2009}{}%
+Van Dillen, L.
+F., Heslenfeld, D.
+J., \& Koole, S.
+L.
+(2009).
+Tuning down the emotional brain: An fMRI study of the effects of cognitive load on the processing of affective images.
+\emph{NeuroImage}, \emph{45}(4), 1212--1219.
+doi:\href{https://doi.org/10.1016/j.neuroimage.2009.01.016}{10.1016/j.neuroimage.2009.01.016}
+
 \leavevmode\hypertarget{ref-whalen_emotional_2006}{}%
@@
 
+\leavevmode\hypertarget{ref-yang_positive_2013}{}%
+Yang, H., Yang, S., \& Isen, A.
+M.
+(2013).
+Positive affect improves working memory: Implications for controlled cognitive processing.
+\emph{Cognition and Emotion}, \emph{27}(3), 474--482.
+doi:\href{https://doi.org/10.1080/02699931.2012.713325}{10.1080/02699931.2012.713325}
+
 \endgroup

### 2019-10-01 Manuscript/Manuscript.Rmd
reorganized intro

@@
 ---
-title             : "Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions"
+title             : "Domain-specific working memory loads selectively increase negative interpretations of surprised facial expressions"
 shorttitle        : "DOMAIN-SPECIFIC WORKING MEMORY AND SURPRISED EXPRESSIONS"
@@
 # Introduction
-## Working memory and load theory
-Despite extensive research on the interaction of working memory and affective processes, there is much to learn concerning how cognitive and emotional processes affect one another.
+## Facial expressions and individual differences
+<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> Facial expressions are a mechanism for communicating emotion during social interactions.
+While the use of facial expressions as an information exchange may be universal [@izard_innate_1994], there are notable differences in interpretations of facial expressions [@green_factors_2018; @neta_corrugator_2009].
+One such difference is in valence judgments of emotional facial expressions.
+The affective circumplex model posits that two independent neurophysiological systems give rise to emotional experience which are known as valence and arousal [@posner_circumplex_2005].
+Valence is the inherent positive (i.e., pleasant) or negative (i.e., unpleasant) qualities of a stimulus, feeling, or state.
+Importantly, individuals differ in their tendency to interpret ambiguously valenced stimuli, such as a tempting food item or a surprised facial expression, as either positive or negative.
+<!-- Additionally, facial expressions can serve as ambiguously valenced stimuli.
+While most facial expressions send a clear social signal, this is not always the case.
+While a smile likely expresses a positive affective state, other cues are not so clear.--> This is attributable to such stimuli's predictive value for both positive and negative outcomes in an individual's previous experience.
+For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events.
+This affective bias is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes to better understand this individual difference [@neta_corrugator_2009; @neta_primacy_2010; @neta_neural_2013].
+
+Previous work shows that valence bias is both a stable, trait-like measure [@neta_corrugator_2009], but also malleable due to its susceptibility to laboratory manipulations [@brown_cortisol_2017; @neta_through_2018; @neta_its_2018].
+The trait-like nature of valence bias is useful for understanding chronic affective biases.
+Negativity biases, which may be adaptive in the short-term (e.g., heightened attention to negative stimuli in a potentially dangerous situation), can undermine healthy psychological functioning over time.
+For instance, negativity biases in memory and attention are related to an increased risk for psychopathology, such as depression and anxiety [@mathews_cognitive_2005].
+<!-- suggesting the importance of understanding the factors that contribute to individuals' biases.
+--> Alternatively, the malleability of valence bias offers insight into mechanisms or interventions that may be capable of shifting bias.
+Several brief, laboratory interventions are known to shift bias.
+For example, instructing participants to slow responding will lead to more positive interpretations of ambiguity [@neta_dont_2016].
+Alternatively, manipulating participant gaze to match that of extremely negative (or positive) individuals modulates individuals' bias [@neta_through_2018].
+In short, valence bias offers insight into both state- and trait-like components of individuals behavior, but through what mechanisms might an individual arrive at either a positive or negative interpretation?
+
+## Initial negativity hypothesis
+Myriad factors contribute to an individual's bias, but research suggests the initial interpretation is negative across people.
+Data supporting this initial negativity hypothesis come from many studies.
+As mentioned above, reaction times are faster for negative interpretations of ambiguous stimuli [@neta_dont_2016].
+If negative interpretations occur faster than positive interpretations, then there may be an initial, automatic process resulting in the negativity.
+In turn, positive interpretations would require some override or regulation of this initial process.
+Supporting this idea, presentation of surprised facial expressions as low spatial frequency images, which are processed more readily than high spatial frequency images, bias interpretations towards negativity [@neta_primacy_2010].
+Again, this supports the automaticity of negative interpretations, and suggests that high spatial frequency components, which are processed later, may be helpful for overriding negativity.
+<!-- Under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes, and there is evidence to support this as well.
+For example, shifting participants time perspectives shifts interpretations of ambiguous images as well [@neta_its_2018].--> Evidence from the neuroimaging literature supports the initial negativity hypothesis as well; more positive individuals show higher levels of BOLD activation, when passively viewing surprised expressions, in brain regions recruited during emotion regulation of negative images [@petro_individual_2018].
+Emotion regulation, and more specifically reappraisal, may be an underlying mechanism of a more positive valence bias.
+
+<!-- Perceptual input also contributes to valence bias.
+In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation on the mouth is related to more positive interpretations of surprised faces.
+In all, valence bias is a useful metric for understanding both trait-like components of individuals' affective biases, as well as gauging the effects of other experimental maniuplations on affective biases.
+-->
+<!--For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
+When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative.
+Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes [@neta_neural_2013] or even words (Harp, Petro, Brown & Neta, in prep).
+This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.
+-->
+<!-- Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes.
+For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016].
+Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010].
+Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well.
+For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018].
+Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018].
+<!-- Perceptual input also contributes to valence bias.
+In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions.
+THIS NEEDS TO BE REWORKED In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.
+-->
+
+## Cognitive loads and task interference
 Executive functions, including working memory, are related to successful self-regulation, and in turn emotion regulation [@hofmann_executive_2012].
@@
 Similarly, active working memory processes may alter concurrent affective processes.
-For instance, actively engaging working memory can mitigate emotional responses, particularly to negative stimuli.
+For instance, actively engaging working memory can mitigate emotional responses, particularly to negative stimuli [@macnamara_working_2011].
 Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase [@van_dillen_tuning_2009].
@@
 While previous work suggests an inhibitory effect on some emotional responses during periods with high cognitive demands, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli.
-For instance, Schmeichel and colleagues [-@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral compared to negative sitmuli [@van_dillen_tuning_2009].<!--  Others have even measured symptoms during working memory maintenance of affective symptoms (i.e., typically increased negative affect), such as anxiety [@spangler_little_2017].--> However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the images of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies).
-For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food is (in)congruent with one's current goals.
-This emotional appraisal is completed under concurrent load demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.
-Maintenance of one's goal state, such as a diet, can reduce performance on some components of executive functioning tasks [@shaw_dieting_2004].
-These observations are in line with Lavie and colleague's [-@lavie_load_2004] load theory, which posits that under a large cognitive load less executive resources are available to regulate incoming stimulus information.
-<!-- In turn, this could mean that more readily processed perceptual input (e.g., low spatial frequency images; LSF) might drive decisions under working memory loads.
--->
+For instance, Schmeichel and colleagues [-@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral compared to negative sitmuli [@van_dillen_tuning_2009].<!--  Others have even measured symptoms during working memory maintenance of affective symptoms (i.e., typically increased negative affect), such as anxiety [@spangler_little_2017].--> However, many emotional appraisals, such as interpreting the valence of emotionally ambiguous stimuli, are more nuanced.
+<!-- For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food is (in)congruent with one's current goals.
+This emotional appraisal is completed under concurrent load demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.--> Maintenance of goal states can reduce performance on some components of executive functioning tasks [@shaw_dieting_2004], which is in line with Lavie and colleague's [-@lavie_load_2004] load theory.
+Cognitive load theory posits that under a large cognitive load less executive resources are available to regulate incoming stimulus information.
+In turn, this means that more bottom-up, automatic processes (e.g., more readily processed perceptual input such as low spatial frequency information) might drive decisions under working memory loads.
 
-Recently, cognitive load theory researchers have tested, and demonstrated, the domain-specificity of load and distractor interference in visual, spatial, and phonological domains [@burnham_components_2014].
-Load interference effects may also transverse other domain componenets, such as emotional compared to neutral memory content.
+## Domain-specific interference
+Recently, cognitive load theory researchers have tested, and demonstrated, the domain-specificity of cognitive load and distractor interference effects in visual, spatial, and phonological domains [@burnham_components_2014].
+Load interference effects may also transverse other domain components, such as maintaining emotional compared to neutral memory content.
 Emotional stimuli readily capture attention compared to neutral stimuli, and this is true even in participants with amygdala damage [@hodsoll_attentional_2011; @piech_attentional_2011].
-Given emotional stimuli's priority position in the information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals.
+Given the preference for emotional stimuli in the brain's information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals.
 Indeed, Kensigner and colleagues [-@kensinger_effect_2003] showed that negative emotional content slows performance on the n-back task.
@@
 
-## Interpreting ambiguity
-<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> Individuals differ in their tendency to interpret ambiguously valenced stimuli, like a tempting food item or a surprised facial expression, as either positive or negative.
-<!-- Additionally, facial expressions can serve as ambiguously valenced stimuli.
-While most facial expressions send a clear social signal, this is not always the case.
-While a smile likely expresses a positive affective state, other cues are not so clear.--> This is attributable to these stimuli's predictive value for both positive and negative outcomes.
-For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events.
-This affective bias is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes to quantify this individual difference [@neta_corrugator_2009; @neta_primacy_2010; @neta_neural_2013].
-Chronic negativity biases in memory and attention are related to psychopathology, such as depression and anxiety [@mathews_cognitive_2005], suggesting the importance of understanding the factors that contribute to individuals' biases.
-Importantly, the valence bias is a stable measure with participants showing positively correlated scores across a one year time gap [@neta_corrugator_2009].
-Despite the relative stability of the measure, experimental manipulations are capable of shifting an individuals bias [@brown_cortisol_2017; @neta_through_2018; @neta_its_2018].
-
-Myriad factors contribute to an individual's bias, but the initial interpretation is thought to be negative across individuals.
-Data supporting this initial negativity hypothesis come from many studies.
-For instance, reaction times are faster for negative interpretations of ambiguous stimuli [@neta_dont_2016].
-Additionally, presentation of surprised facial expressions as low spatial frequency images, which are processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010].
-Under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes, and there is evidence to support this as well.
-For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018].
-Evidence from the neuroimaging literature supports the initial negativity hypothesis as well; more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018].
-Perceptual input also contributes to valence bias.
-In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation on the mouth is related to more positive interpretations of surprised faces [@neta_all_2017].
-Further, forcing gaze patterns to match those of the participants with the most negative or positive bias modulated interpretations of surprised expressions [@neta_through_2018].
-In all, valence bias is a useful metric for understanding both trait-like components of individuals' affective biases, as well as gauging the effects of other experimental maniuplations on affective biases.
-<!--For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
-When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative.
-Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes [@neta_neural_2013] or even words (Harp, Petro, Brown & Neta, in prep).
-This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.
--->
-<!-- Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes.
-For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016].
-Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010].
-Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well.
-For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018].
-Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018].
-<!-- Perceptual input also contributes to valence bias.
-In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions.
-THIS NEEDS TO BE REWORKED In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.
--->
-
-Given the evidence that a regulatory mechanism is necessary for positive interpretations of ambiguity, a demanding cognitive load might interfere with successful regulation.
-Indeed, Mattek and colleagues [-@mattek_differential_2016] recently showed that high levels of cognitive load (i.e., holding either a single or seven digit number in working memory) mitigates mouse trajectory deviations to the modal response.
+## The present study
+Given the evidence that positive interpretations of ambiguity rely on a regulatory mechanism, a demanding cognitive load could interfere with successful implementation of regulation strategies.
+Recently, Mattek and colleagues [-@mattek_differential_2016] showed that high levels of cognitive load (i.e., holding either a single or seven digit number in working memory) mitigates mouse trajectory deviations to modal responses during interpretations of surprised expressions.
 However, there was no effect on subjective valence interpretations.
-Just as phonological and visual cognitive loads and distractors showed domain-specificity [@burnham_components_2014], and that domain-speicificity is observed in BOLD data [@egner_dissociable_2008], a domain-specific cognitive load may differentially affect interpretations of ambiguity.
-In other words, there is likely a relationship between the qualities of stimuli held in working memory and effects on concurrent task processing.
-Here, we aim to test the effects of low and high working memory loads in both emotional and neutral domains on valence bias.
+Further, <!-- Just as phonological and visual cognitive loads and distractors showed domain-specificity [@burnham_components_2014], and--> domain-specificity effects in both behavioral and BOLD data [@kensinger_effect_2003; @whalen_emotional_2006 ;@egner_dissociable_2008] suggest that a domain-specific (i.e., emotional) cognitive load may differentially affect emotional judgments during interpretations of ambiguity.
+<!--In other words, there is likely a relationship between the qualities of stimuli held in working memory and effects on concurrent task processing.--> Here, we aim to test the effects of low and high working memory loads in both emotional and neutral domains on valence bias.
 We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials, as the high cognitive demand interferes with the regulatory mechanisms used to arrive at a positive interpretation.
-Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
+Further, we predict that higher working memory load trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
 

### 2019-10-08 Manuscript/Manuscript.Rmd
update intro

--- 2019-09-24 Manuscript/Manuscript.Rmd
@@
 # Introduction
-## Working memory and load theory
-Despite extensive research on the interaction of working memory and affective processes, there is still debate in the literature concerning how this cognitive process and emotional processes affect one another.
-Directly comparing working memory and self-regulation of emotional responses, Schmeichel and colleagues -[@schmeichel_working_2008] reported that individuals with higher levels of working memory capacity demonstrated improved self-regulation towards the emotional stimuli.
-This suggests a connection--perhaps through some shared resource pool--between mitigated emotional responding and larger working memory resource availablility.
-Other work has focused on the effects of moods or affective states on working memory performance.
-For instance, some reports claim that both positive and negative mood interfere with working memory (Eyesenck and Calvo, 1992); however, others suggest benefits of positive mood on working memory [@yang_positive_2012].
-Similarly, working memory processes may alter concurrent affective processes.
-For instance, actively engaging working memory can mitigate emotional responses.
-Recent neuroimaging work reports that negative emotional responses decrease as the cognitive demands of a working memory task increase [@dillen_tuning_2008].
-Additionally, depending on one's levels of trait-rumination, low trait-ruminators are better able to return heart rate and blood pressure to baseline levels when provided with a distractor task following an anger induction [@gerin_role_2006].
-Together, these studies suggest a resource competition between cognitive and emotional processing; that is, when cognitive load demands are high (e.g., during active working memory maintenance), there are fewer resources available for other (i.e., affective) processes.
+## Facial expressions and individual differences
 
-While previous work clearly suggests an inhibitory role for cognitive demands on emotional responses, researchers have primarily focused on emotional responses to clearly valenced emotional stimuli.
-For instance, Schmeichel and colleagues -[@schmeichel_working_2008] showed participants videos intended to elicit strong negative responses (e.g., disgust) or positive responses (e.g., humor), while others have focused on comparing responses to neutral and negative sitmuli [@dillen_tuning_2008], or even reducing symptoms of disorders with affective symptoms, such as anxiety [@spangler_little_2017].
-However, many emotional appraisals in day-to-day life are more nuanced than those invoked by many of the types of negative stimuli one might encounter in the lab (e.g., snakes, mutilated bodies).
-For example, one may appraise the content of a billboard displaying a large order of french fries as either negative or positive depending on whether or not consuming that food would be (in)congruent with one's current goals.
-This emotional appraisal is completed under concurrent laod demands--that is, the perceiver must process both the emotional stimulus (i.e., the fries) as well as actively maintain their current goal state.
-If maintaining a goal state or some stimulus in working memory results in a large cognitive (not perceptual) load, then  Lavie's -[@lavie_load_2004] load theory posits that less executive resources are available to regulate incoming perceptual information.
-In turn, this could mean that more readily processed perceptual input (e.g., low spatial frequency images; LSF) might drive decisions under working memory loads.
+### Facial expressions are an important social signal
+Facial expressions are important social signals, often communicating emotion between individuals and even sparking emotional responses in the perceiver [@frith_role_2009].
+Researchers have long argued that facial expressions are universal signals of emotion, positing humans' innate ability to associate facial expressions with emotional experience [@darwin_expression_1872; @ekman_constants_1971; @izard_innate_1994].
+More recently, Barrett and colleagues suggested that the relationship between facial expressions and emotions is more complex, stating that expression of an emotion may vary across cultures, social context, or even individuals -[@barrett_emotional_2019].
+Other work has shown individual differences in interpretations of facial expressions [@green_factors_2018; @neta_corrugator_2009].
+Regardless of this variability in emotional expressions, experience, and interpretations, humans readily make judgments about personality traits (e.g., trustworthiness), aesthetics (e.g., attractiveness), and emotions from faces [@todorov_evaluating_2008; @said_statistical_2011; @carroll_facil_1996].
+Interpretations of valence, that is the inherent positive or negative emotional value of a stimulus, are one instance of judgments of facial expressions guiding potential social (i.e., approach-avoidance) behavior <!-- not sure if this is truly social?
+--> [@krieglmeyer_being_2010].
 
-Emotional stimuli readily capture attention compared to neutral stimuli, even in participants with amygdala damage [@hodsol_attentional_2011; @piech_attentional_2011].
-Given emotional stimuli's priority position in the information processing stream, it may be that cognitive loads with emotional content, compared to neutral, differentially affect concurrent emotional appraisals.
-Indeed, negative emotional content slows performance on an n-back task [@kensinger_effect_2003].
-Other domain-specific effects have been observed in many lines of research, including those beyond the working memory domain.
-For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.
-non-emotional) task relevancy [@egner_dissociable_2008].
-Given the behavioral and neurological evidence for dissociations of emotional and non-emotional information domains in executive functions (e.g., working memory, inhibitory control), the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent emotional judgments.
+### Individuals differ (trait) in their tendency to interpret ambiguous images, like a surprised face
+While most people can accurately differentiate the emotional valence of many facial expressions [CITE], such as consistently interpreting angry (happy) faces as negative (positive), there are individual differences in valence judgments of emotionally ambiguous facial expressions, like a surprised face [@neta_corrugator_2009; @petro_individual_2018 <!-- right citations?-->].
+This difference in valence interpretations of surprised expressions is attributable to such stimuli's predictive value for both positive and negative outcomes in an individual's previous experience.
+For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events.
+These differences in valence interpretations represent an important individual difference, as the same stimulus can result in two alternative interpretations between individuals--likely leading to different downstream behaviors [e.g., @krieglmeyer_being_2010].
+This individual difference in interpretations of emotionally ambiguous stimuli is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes to better understand this individual difference [@neta_corrugator_2009; @neta_primacy_2010; @neta_neural_2013].
 
-<!-- Frequently, tasks in daily life require recruitment of working memory, but active working memory demands may affect concurrent processing.
-Many types of information can be held in working memory: strings of numbers, images, stimulus characteristics like brightness, spatial locations, and more.
-There is debate in the literature around the substrates of working memory and how this seemingly unitary construct is distributed across domain-specific subsystems (see [@baddeley_working_1986; @shah_separability_1996]).
-Recent work suggests though that working memory may contain more domain-specific subsystems than previously believed (e.g., affective working memory; e.g., @mikels_affective_2019).
-Similar to the work of Shah and colleagues -[@baddeley_working_1986], Mikels (find acutal study) showed ?double dissociation?
-of the affective working memory system from a more visually based working memory (i.e., maintenance of image brightness in memory).
-Similar domain-specific effects have been observed in many other lines of research, including those beyond the working memory domain.
-For example, the Stroop task [@stroop_studies_1935], a common measurement tool for inhibitory control, has been modified to include both emotional and non-emotional (neutral) stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Neuroimaging work also supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.
-non-emotional) task relevancy [@egner_dissociable_2008], suggesting a division of subsystems.
-Given the behavioral and neurological evidence for dissociations of information domains in working memory, task interference and more, the present work aims to clarify the interaction of emotional and non-emotional visual working memory demands on concurrent emotional judgments (i.e., interpretations of emotional facial expressions).
+### Despite the bias, everyone seems to show an initial negativity--positivity is associated with emotion regulation
+Despite one's valence bias, the initial response to ambiguity appears to be negativity [@neta_corrugator_2009; @neta_primacy_2010; @neta_valence_2011; @petro_individual_2018].
+Under this framework, which is known as the *initial negativity* hypothesis, positive interpretations rely on the implementation of some emotion regulation strategy, perhaps similar to cognitive reappraisal.
+During cognitive reappraisal, individuals work to change intial perceptions of an emotional stimulus [@lazarus_short_1964].
+Similarly, the initial negativity hypothesis posits that individuals' initial perception of surprised expressions is negative, and that those arriving at a positive interpretation must implement a regulatory mechanism to alter their interpretation.
+
+### Behavioral and brain data supports the initial negativity hypothesis
+Both behavioral and brain data in support of the initial negativity hypothesis come from many studies.
+For instance, reaction time (RT) data show that individuals with more positive biases take longer to reach a valence judgment for surprised expressions than those with a more negative bias [@neta_corrugator_2009], suggesting a more time-intensive (regulatory) process for positive interpretations.
+Other work demonstrates the automaticity of negative interpretations through presenting either low- (LSF) or high-spatial frequency (HSF) images of surprised expressions.
+The images with only LSF information, which is processed earlier than its HSF counterpart, were rated more negatively than the HSF images [@neta_primacy_2010].
+Additionally, surprised facial expressions are more quickly detected among happy (positive) than angry (negative) faces [@neta_valence_2011].
+The results from this emotional oddball paradigm suggest that surprised expressions are more readily perceived as similar to angry faces (i.e., perceived as negative) than happy faces.
+There is also support for the initial negativity hypothesis in studies with brain data.
+Ventromedial prefrontal cortex, a putative regulatory region, and the amygdala actively are inversely correlated, and participants with more negative biases show higher activity in the amygdala while more positive participants show higher activity in vmPFC [@kim_inverse_2003].
+More recently, Petro and colleagues showed that participants with a more positive valence bias show more activity for surprised faces in emotion regulation-related brain regions -[vmPFC; @petro_individual_2018].Taken together, these effects support the idea that negative interpretations of surprised faces are faster and default process, while positive interpretations rely on slower regulatory processes.
+<!-- is it okay to combine these sections?
 -->
 
-<!-- While it is well known that distractors can undermine task performance [@hagen_effect_1967; cite, cite), some evidence suggests a role for domain-specificity in task interference.
-For instance, domain-specific interference further exacerbates these task effects compared to domain-general stimuli [@gruber_effects_2001].
-Within an affect-specific context, the literature reports conflicting results for the role of affective stimuli on working memory processing (see @jackson_enhanced_2009 and @mather_emotional_2006), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes.
-The relationship between these systems is bidirectional though, and often times working memory affects affective processing.
-One such way is through dampening emotional responses, and converging work suggests that cognitive demands can mitigate negative emotional effects [@dillen_tuning_2008].
-One explanation for mitigated emotional responding during concurrent working memory demands is load theory.
-This theory posits that cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands [@lavie_load_2004].
-One limitation to this previous work is that the affective processes under study involved clearly interpretable stimuli/feelings.
-A more malleable affective process, such as interpreting ambiguously valenced emotional facial expressions, may offer better understanding of how concurrent working memory demands affect emotional processes.
--->
+## Cognitive loads and task interference
+### In our daily lives, these resources are not always available
 
-## The contribution of valence bias
-<!-- Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.--> As mentioned above, individuals differ in their tendency to interpret ambiguously valenced stimuli, like a tempting food item, as either positive or negative.
-<!-- Additionally, facial expressions can serve as ambiguously valenced stimuli.
-While most facial expressions send a clear social signal, this is not always the case.
-While a smile likely expresses a positive affective state, other cues are not so clear.--> This tendency is known as one's *valence bias*, and a growing body of work has used both facial expressions and scenes (or items) to quantify this individual difference (CITE).
-Biases towards negativity are related to psychopathology, such as depression and anxiety [@matthews_cognitive_2005]
+### Active WM maintenance affects concurrent processes
 
-<!--For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
-When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative.
-Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes [@neta_neural_2013] or even words (Harp, Petro, Brown & Neta, in prep).
-This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.
--->
-
-Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes.
-For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) [@neta_dont_2016].
-Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity [@neta_primacy_2010].
-Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well.
-For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity [@neta_its_2018].
-Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation [@petro_individual_2018].
-<!-- Perceptual input also contributes to valence bias.
-In one recent study, Neta and colleagues [-@neta_all_2017] showed that faster intial fixation, as well as longer overall fixation, on the mouth is related to more positive interpretations of surprised faces and that forcing gaze patterns to match those of modulated interpretations of surprised expressions.
-THIS NEEDS TO BE REWORKED --> In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.
-
-Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference.
-Mattek and colleagues [-@mattek_differential_2016] recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories.
-While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias.
-Given the task irrelevance of the numeric distractors in Mattek and colleagues' [-@mattek_differential_2016] work, it follows that the resources required for interpreting ambiguity as positive [@neta_corrugator_2009] may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
+### Other work has tested the effects of cognitive load on valence bias, but did not find an effect for interpretations of surprise. This could be due to domain-specific effects of cognitive load.
 
 ## The present study
-In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains.
-We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials.
-Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
 
-<!-- Despite the trait-like nature of this bias [@neta_corrugator_2009], valence bias may be shifted, at least temporarily, by a number of experimental manipulations.
-As mentioned above, simple manipulations like slowing response times will shift bias [@neta_its_2018].
-Additional work has shown that increases in salivary cortisol after a stressor relate to more negative interpretations of surprised faces from baseline to post-stressor [@brown_cortisol_2017].
-Similarly, participants with positive biases at baseline will interpret surprise as more negative under threat of shock [@neta_impact_2017], suggesting that taxing cognitive resources, in this case attention, reduces the ability of individuals to interpret surprised faces as positive.
--->
+### h1: domain main effect
 
-Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces [@mattek_differential_2016; @neta_dont_2016]. 
-The valence bias is trait-like [@neta_corrugator_2009] and generalizes to non-face stimuli [@neta_neural_2013]; however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding [@brown_cortisol_2017; @neta_dont_2016].
-Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology [@petro_initial_2018], at least in children.
-Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety [@matthews_cognitive_2005].
-
-<!-- Distractors and task irrelevant stimuli often have detrimental effects on performance in a variety of tasks [; cite, cite].
-Further, domain-specific interference may further exacerbate these effects compared to domain-general stimuli [@gruber_effects_2001].
-This effect holds up in the emotional domain; for example, the Stroop task [@stroop_studies_1935] has been modified by some researchers to include emotional stimuli [@whalen_emotional_2006] which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Indeed, neuroimaging work supports the idea that separate systems handle attentional biasing for domain-specific (emotional vs.
-non-emotional) task relevancy [@egner_dissociable_2008].
--->
-
-<!-- Notes: Allie showed that depletion doesn't affect ratings, but we thought that there may be an effect of specific domains of depletion (i.e., neutral vs.
-emotional) on ratings.
-Focus on EMO > NEU ratings and POS > NEG MDs.
-MT analyses could be supplementary material, but you'll be going down the rabbit hole.
--->
-<!-- Recently, others have suggested a dynamic social trait space model for judgments of faces [@stolier_dynamic_2018], and it may be important to consider additional components of the categorization process, such as domain-specific loads.
--->
+### h2: domain x load interaction
 

### 2020-08-14 Manuscript/Manuscript.Rmd
QJES Submission - Initial

@@
 ## Facial expressions and individual differences
-
-### Facial expressions are an important social signal
-Facial expressions are important social signals, often communicating emotion between individuals and even sparking emotional responses in the perceiver [@frith_role_2009].
+Facial expressions are important social signals; they communicate emotion between individuals and even spark emotional responses in others [@frith_role_2009].
 Researchers have long argued that facial expressions are universal signals of emotion, positing humans' innate ability to associate facial expressions with emotional experience [@darwin_expression_1872; @ekman_constants_1971; @izard_innate_1994].
-More recently, Barrett and colleagues suggested that the relationship between facial expressions and emotions is more complex, stating that expression of an emotion may vary across cultures, social context, or even individuals -[@barrett_emotional_2019].
+More recently, Barrett and colleagues suggested that the relationship between facial expressions and emotions is more complex, stating that facial expression of an emotion may vary across cultures, social context, or even individuals [@barrett_emotional_2019].
 Other work has shown individual differences in interpretations of facial expressions [@green_factors_2018; @neta_corrugator_2009].
-Regardless of this variability in emotional expressions, experience, and interpretations, humans readily make judgments about personality traits (e.g., trustworthiness), aesthetics (e.g., attractiveness), and emotions from faces [@todorov_evaluating_2008; @said_statistical_2011; @carroll_facil_1996].
-Interpretations of valence, that is the inherent positive or negative emotional value of a stimulus, are one instance of judgments of facial expressions guiding potential social (i.e., approach-avoidance) behavior <!-- not sure if this is truly social?
+Regardless of this variability in emotional expressions, experience, and interpretations, humans readily make judgments about personality traits (e.g., trustworthiness), aesthetics (e.g., attractiveness), and emotions from faces [@todorov_evaluating_2008; @said_statistical_2011; @carroll_facial_1996].
+Interpretations of valence (i.e., the inherent positive or negative emotional value of a stimulus) are one instance of judgments of facial expressions guiding potential social (i.e., approach-avoidance) behavior <!-- not sure if this is truly social?
 --> [@krieglmeyer_being_2010].
 
-### Individuals differ (trait) in their tendency to interpret ambiguous images, like a surprised face
-While most people can accurately differentiate the emotional valence of many facial expressions [CITE], such as consistently interpreting angry (happy) faces as negative (positive), there are individual differences in valence judgments of emotionally ambiguous facial expressions, like a surprised face [@neta_corrugator_2009; @petro_individual_2018 <!-- right citations?-->].
+While most people can accurately differentiate the emotional valence of many facial expressions, such as consistently interpreting angry (happy) faces as negative (positive), there are individual differences in valence judgments of emotionally ambiguous facial expressions, like a surprised face [@neta_corrugator_2009; @petro_individual_2018 <!-- right citations?-->].
 This difference in valence interpretations of surprised expressions is attributable to such stimuli's predictive value for both positive and negative outcomes in an individual's previous experience.
@@
 
-### Despite the bias, everyone seems to show an initial negativity--positivity is associated with emotion regulation
 Despite one's valence bias, the initial response to ambiguity appears to be negativity [@neta_corrugator_2009; @neta_primacy_2010; @neta_valence_2011; @petro_individual_2018].
 Under this framework, which is known as the *initial negativity* hypothesis, positive interpretations rely on the implementation of some emotion regulation strategy, perhaps similar to cognitive reappraisal.
-During cognitive reappraisal, individuals work to change intial perceptions of an emotional stimulus [@lazarus_short_1964].
+During cognitive reappraisal, individuals work to change intial perceptions of an emotional stimulus [@lazarus_short-circuiting_1964].
 Similarly, the initial negativity hypothesis posits that individuals' initial perception of surprised expressions is negative, and that those arriving at a positive interpretation must implement a regulatory mechanism to alter their interpretation.
 
-### Behavioral and brain data supports the initial negativity hypothesis
-Both behavioral and brain data in support of the initial negativity hypothesis come from many studies.
-For instance, reaction time (RT) data show that individuals with more positive biases take longer to reach a valence judgment for surprised expressions than those with a more negative bias [@neta_corrugator_2009], suggesting a more time-intensive (regulatory) process for positive interpretations.
-Other work demonstrates the automaticity of negative interpretations through presenting either low- (LSF) or high-spatial frequency (HSF) images of surprised expressions.
-The images with only LSF information, which is processed earlier than its HSF counterpart, were rated more negatively than the HSF images [@neta_primacy_2010].
-Additionally, surprised facial expressions are more quickly detected among happy (positive) than angry (negative) faces [@neta_valence_2011].
-The results from this emotional oddball paradigm suggest that surprised expressions are more readily perceived as similar to angry faces (i.e., perceived as negative) than happy faces.
-There is also support for the initial negativity hypothesis in studies with brain data.
-Ventromedial prefrontal cortex, a putative regulatory region, and the amygdala actively are inversely correlated, and participants with more negative biases show higher activity in the amygdala while more positive participants show higher activity in vmPFC [@kim_inverse_2003].
-More recently, Petro and colleagues showed that participants with a more positive valence bias show more activity for surprised faces in emotion regulation-related brain regions -[vmPFC; @petro_individual_2018].Taken together, these effects support the idea that negative interpretations of surprised faces are faster and default process, while positive interpretations rely on slower regulatory processes.
-<!-- is it okay to combine these sections?
--->
+Behavioral evidence supports the initial negativity hypothesis.
+For instance, reaction time data show that individuals with more positive biases take longer to reach a valence judgment for surprised expressions than those with a more negative bias [@neta_corrugator_2009], suggesting a more time-intensive (regulatory) process for positive interpretations.
+Other work demonstrates the faster and default nature of negative interpretations through manipulating the spatial frequency of images of surprised expressions.
+The images with only low spatial frequency information, which is processed earlier than  high spatial frequency information, were rated more negatively than the high spatial frequency images [@neta_primacy_2010].
+Additionally, surprised facial expressions are more quickly detected in an emotional oddball paradigm among happy (positive) than angry (negative) faces [@neta_valence_2011], suggesting that surprised expressions are more readily perceived as similar to angry faces (i.e., perceived as negative) than happy faces.
+
+There is also support for the initial negativity hypothesis in neuroimaging studies.
+Ventromedial prefrontal cortex, a putative regulatory region, and amygdala actively are inversely correlated, and participants with more negative biases show higher activity in the amygdala while more positive participants show higher activity in vmPFC [@kim_inverse_2003].
+More recently, Petro and colleagues [-@petro_individual_2018] showed that participants with a more positive valence bias show more activity for surprised faces in emotion regulation-related brain regions (vmPFC).Taken together, both behavioral and brain data support the notion that negative interpretations of surprised faces are a faster, default process and positive interpretations rely on slower regulatory processes, which may be susceptible to demands from other cognitive processes.
 
 ## Cognitive loads and task interference
-### In our daily lives, these resources are not always available
+In daily life, cognitive resources are often shared among several processes as stimuli compete for our attention.
+For example, imagine a student attending a lecture.
+If the student is frequently distracted by notifications and directing cognitive resources towards a text message conversation or computer applications, then the student's ability to understand and remember the lecture will likely suffer.
+Indeed, cognitive resource competition leads to a phenomenon known as cognitive load, which negatively impacts executive processes [@murphy_twenty_2016; @lavie_load_2004].
+High levels of cognitive load alter performance on a variety of tasks, including those in both cognitive and emotional domains [@pontari_influence_2000; @jiaping_empathy_2017; @thomas_impact_2017; @nagamatsu_increased_2011; @kron_feelings_2010].
+Working memory tasks, which require participants to maintain some stimulus representation in working memory, are often used for testing cognitive load effects [e.g., @burnham_cognitive_2010; @lavie_role_2005; or see @murphy_twenty_2016 for a review].
 
-### Active WM maintenance affects concurrent processes
+The cognitive demands of active working memory maintenance often interact with concurrent affective processes (e.g., face categorization, subjective emotional experience), perhaps as a result of a shared resource pool for these processes.
+For instance, Ahmed [-@ahmed_knowing_2018] showed that performance on a facial expression categorization task suffers when participants are under high cognitive load.
+Other work has linked cognitive load to changes in emotional responses [@van_dillen_tuning_2009; @blair_modulation_2007].
+For example, higher loads during a working memory task reduce subjective emotional experience, as well as amygdala activity [@van_dillen_tuning_2009].
+Other neuroimaging work has shown that Stroop interference effects were exaggerated during trials temporally surrounded by emotional stimuli, while emotional responses in the brain (i.e., amygdala and inferior frontal gyrus activation) were lower during trials with Stroop task demands compared to trials with no concurrent task demands [@blair_modulation_2007].
+Other work highlights the importance of cognitive load task characteristics on a syllogistic reasoning task, demonstrating that participants perform worse on tasks with emotional, rather than neutral, content when under high cognitive load  [@tremoliere_cognitive_2016].
+Together, these effects suggest an overlap between cognitive demands and emotional processes, with high cognitive demands interfering with typical emotion processing.
 
-### Other work has tested the effects of cognitive load on valence bias, but did not find an effect for interpretations of surprise. This could be due to domain-specific effects of cognitive load.
+Previous work has tested the effects of cognitive load on valence bias to assess both subjective ratings of surprise and the underlying cognitive-motor dynamics of the ratings via mousetracking.
+While there was no effect of load on subjective interpretations of surprised expressions, participants did show altered mouse trajectories, such that mouse movements were less drawn towards the response option (i.e., positive or negative) in line with one's bias [@mattek_differential_2016].
+<!-- The researchers also collected mouse trajectories, using MouseTracker [@freeman_mousetracker:_2010], to quantify the cognitive-motor attraction towards ultimately unselected responses [CITE, CITE].--> One potential explanation for the null effect of load on ratings is the domain-specificity of the cognitive load.
+While there are some domain-general effects of cognitive load on emotional processing [@blair_modulation_2007; @van_dillen_tuning_2009], which helps explain the effects of load on mouse trajectories, other lines of work have shown dissociable processing of emotional and non-emotional task stimuli [@egner_dissociable_2008].
+Critically, Mattek and colleagues [-@mattek_differential_2016] used non-emotional stimuli (i.e., number sequence) in their manipulation of cognitive load during interpretations of surprised facial expressions.
+The cognitive demand required for maintaining emotional information in working memory may tax resources used for emotion regulation more so than non-emotional information.
+Under the initial negativity framework, this would lead to more negative interpretations of surprise during cognitive load with emotional stimuli.
 
 ## The present study
-
-### h1: domain main effect
-
-### h2: domain x load interaction
+In the present study we test the effects of both low and high cognitive load across emotional and non-emotional domains.
+We expect to find a main effect of load domain, emotional or non-emotional, on interpretations of surprise, such that interpretations made under emotional working memory loads are more negative than those made under non-emotional working memory loads.
+Further, we predict an interaction effect, such that emotional working memory loads with more content (high load) will result in more negative interpetations than emotional working memory loads with less content (low load).
 
@@
 
+[@frith_role_2009]
+[@carrol_facial_1996]
+[@bar_very_2006]
+[@said_statistical_2011]
+[@todorov_evaluating_2008]
+[@krieglmeyer_being_2010]
+[@neta_corrugator_2009]
+[@petro_individual_2018]
+[@neta_neural_2013]
+[@neta_primacy_2010]
+
+[@frijda_emotions_1986]
+[@neta_valence_2011]
+[@neta_dont_2016-1]
+[@kim_contextual_2004]
+[@richard_emotion_2000]
+[@sheppes_divergent_2008]
+[@baumeister_self-regulation_1996]
+
+[@storbeck_performance_2012]
+[@scalf_competition_2013]
+[@lavie_load_2004]
+[@murphy_twenty_2016]
+[@pontari_influence_2000; @jiaping_empathy_2017; @thomas_impact_2017; @nagamatsu_increased_2011; @kron_feelings_2010]
+[@mather_aging_2005]
+[@knight_aging_2007]
+[@chandler_cognitive_1991]
+[@tremoliere_cognitive_2016]
+[@ahmed_knowing_2018]
+[@blair_modulation_2007]
+[@muraven_self-control_1998]
+[@van_dillen_tuning_2009]
+[@mattek_differential_2016]
+[@egner_dissociable_2008]
+[@tottenham_nimstim_2009-1]
+[@lundqvist_karolinska_1998]
+[@lang_international_2008]
+[@freeman_mousetracker: 2010]
+[@flexas_affective_2013]
+[@lavie_role_2005]
+[@bundt_early_2018]
+[@burnham_cognitive_2010]
+[@etkin_resolving_2006]
+[@kujawa_altered_2016]
+[@calcagni_analyzing_2017]
+[@freeman_hand_2011]
+[@hehman_advanced_2015]
+[@spivey_continuous_2005]
+[@lavie_load_2004]
+[@neta_separable_2014]
+[@sterzer_neural_2002]
+[@thompson-schill_role_1997]
+[@duncan_common_2000]
+[@nee_interference_2007]
+
 \newpage

### 2020-08-14 Manuscript/Manuscript.tex
QJES Submission - Initial

--- 2019-09-19 Manuscript/Manuscript.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions},
+            pdftitle={Domain-specific working memory loads selectively increase negative interpretations of surprised facial expressions},
             pdfauthor={Nicholas R. Harp~\& Maital Neta},
@@
 
-  \title{Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions}
+  \title{Domain-specific working memory loads selectively increase negative interpretations of surprised facial expressions}
     \author{Nicholas R. Harp\textsuperscript{1}~\& Maital Neta\textsuperscript{1}}
@@
 
-Completion of even simple tasks in daily life require regular recruitment of working memory, and this often happens without consideration of how these working memory demands may affect concurrent processes.
-Many types of information can be held in working memory: strings of numbers, neutral and emotional images, stimulus characteristics like brightness, spatial locations, and more.
-There is debate in the literature around the neurophysiological substrates of working memory and whether this construct is a unified system or comprised of several domain-specific subsystems (see Baddeley, 1986; Shah \& Mikaye, 1996).
-Recent work suggests though that working memory does indeed contain domain-specific subsystems (e.g., affective working memory; see Mikels and Reuter-Lorenz (2019))--or at least that interactions between working memory and visual or affective tasks are variable depending on working memory content.
-Similar domain-specific effects have been observed in a number of other lines of research, including those outside of the working memory domain.
-For example, the Stroop task (Stroop, 1935) has been modified to include emotional stimuli (Whalen, Bush, Shin, \& Rauch, 2006) which has pronounced effects when the emotional words are population specific (e.g., trauma words in a PTSD sample).
-Further, neuroimaging work supports the notion that separate systems handle attentional biasing for domain-specific (emotional vs.~non-emotional) task relevancy (Egner, Etkin, Gale, \& Hirsch, 2008).
-The present work aims to clarify the interaction of working memory demands on a concurrent and ecologically valid emotionoal task (i.e., interpretations of emotional facial expressions), specifically when that content varies in both amount and affective quality.
+\hypertarget{facial-expressions-and-individual-differences}{%
+\subsection{Facial expressions and individual differences}\label{facial-expressions-and-individual-differences}}
 
-There is a large body of research concerning the effects of distractor and task irrelevant stimuli on performance in a variety of tasks {[}cite, cite{]}.
-Notably, domain-specific interference may further exacerbate these effects compared to domain-general stimuli (Gruber, 2001).
-Within an affect-specific context, the literature reports conflicting results for the role of affective stimuli on working memory processing (see ({\textbf{???}}) and ({\textbf{???}})), with some suggesting ehnaced recall for emotional stimuli and others reporting impairment in working memory processes.
-The relationship between these systems is bidirectional though, and often times working memory affects affective processing.
-One such way is through dampening emotional responses, and converging work suggests that cognitive demands can mitigate negative emotional effects ({\textbf{???}}).
-One explanation for mitigated emotional responding during concurrent working memory demands is load theory.
-This theory posits that cognitive resources are finite, thus limiting the availability for simultaneous processing under large task demands (Lavie, Hirst, Fockert, \& Viding, 2004).
-One limitation to this previous work is that the affective processes under study involved clearly interpretable stimuli/feelings.
-A more malleable affective process, such as interpreting ambiguously valenced emotional facial expressions, may offer better understanding of how concurrent working memory demands affect emotional processes.
+Facial expressions are important social signals, often communicating emotion between individuals and even sparking emotional responses in the perceiver (Frith, 2009).
+Researchers have long argued that facial expressions are universal signals of emotion, positing humans' innate ability to associate facial expressions with emotional experience (Darwin, 1872; Ekman \& Friesen, 1971; Izard, 1994).
+More recently, Barrett and colleagues suggested that the relationship between facial expressions and emotions is more complex, stating that expression of an emotion may vary across cultures, social context, or even individuals (Barrett, Adolphs, Marsella, Martinez, \& Pollak, 2019).
+Other work has shown individual differences in interpretations of facial expressions (Green \& Guo, 2018; Neta, Norris, \& Whalen, 2009).
+Regardless of this variability in emotional expressions, experience, and interpretations, humans readily make judgments about personality traits (e.g., trustworthiness), aesthetics (e.g., attractiveness), and emotions from faces (Carroll \& Russell, 1996; Said \& Todorov, 2011; Todorov, Baron, \& Oosterhof, 2008).
+Interpretations of valence (i.e., the inherent positive or negative emotional value of a stimulus) are one instance of judgments of facial expressions guiding potential social (i.e., approach-avoidance) behavior (Krieglmeyer, Deutsch, De Houwer, \& De Raedt, 2010).
 
-Facial expressions are rich with affective information, and correctly interpreting these social cues is critical for successfully navigating the social world.
-Often, facial expressions serve as a clear social signal, but this is not always the case.
-While a smile likely expresses a positive affective state, other cues are not so clear.
-For instance, a surprised expression could signal either a positive (e.g., winning the lottery) or negative (e.g., seeing a snake in the woods) affective state in the expresser.
-When contextual information is limited, individuals differ in their tendency to interpret surprised facial expressions as positive or negative.
-Importantly, this affective bias extends beyond facial expressions, as individuals often show a similar bias to surprised faces as they do for ambiguous scenes (Neta, Kelley, \& Whalen, 2013) or even words (Harp, Petro, Brown \& Neta, in prep).
-This bias towards positive or negative interpretations is known as one's valence bias and myriad factors contribute to one's bias.
+While most people can accurately differentiate the emotional valence of many facial expressions, such as consistently interpreting angry (happy) faces as negative (positive), there are individual differences in valence judgments of emotionally ambiguous facial expressions, like a surprised face (Neta et al., 2009; Petro, Tong, Henley, \& Neta, 2018 ).
+This difference in valence interpretations of surprised expressions is attributable to such stimuli's predictive value for both positive and negative outcomes in an individual's previous experience.
+For instance, a surprised expression could signal positive (e.g., winning the lottery) or negative (e.g., a car accident) events.
+These differences in valence interpretations represent an important individual difference, as the same stimulus can result in two alternative interpretations between individuals--likely leading to different downstream behaviors (e.g., Krieglmeyer et al., 2010).
+This individual difference in interpretations of emotionally ambiguous stimuli is known as one's \emph{valence bias}, and a growing body of work has used both facial expressions and scenes to better understand this individual difference (Neta, Kelley, \& Whalen, 2013; Neta et al., 2009; Neta \& Whalen, 2010).
 
-Both bottom-up (e.g., perceptual input) and top-down (e.g., stereotypes) processes are recruited for interpretation of facial expressions, and a growing body of work suggests that the initial interpretation of emotionally ambiguous stimuli is negative and driven by bottom-up processes.
-For instance, reaction times are faster for negative interpretations of ambiguous stimuli (just faces??) (Neta \& Tong, 2016).
-Additionally, presentation of surprised facial expressions as low spatial frequency images, which is processed more readily than high spatial frequency images, biased interpretations towards negativity ({\textbf{???}}).
-Consequently, under this framework, arriving at a positive interpretation requires additional, top-down regulatory processes and there is evidence to support this as well.
-For example, forcing participants to slow their responding during interpretations of ambiguous images shifts individuals' biases towards positivity (Neta, Tong, \& Henley, 2018).
-Neuroimaging evidence supports this initial negativity hypothesis as well, more positive individuals show higher levels of BOLD activation in brain regions recruited during emotion regulation ({\textbf{???}}).
-In short, slowing response time allows individuals to better regulate the potentially negative information in surprised expressions and to see it in a more positive light.
+Despite one's valence bias, the initial response to ambiguity appears to be negativity (Neta, Davis, \& Whalen, 2011; Neta et al., 2009; Neta \& Whalen, 2010; Petro et al., 2018).
+Under this framework, which is known as the \emph{initial negativity} hypothesis, positive interpretations rely on the implementation of some emotion regulation strategy, perhaps similar to cognitive reappraisal.
+During cognitive reappraisal, individuals work to change intial perceptions of an emotional stimulus (Lazarus \& Alfert, 1964).
+Similarly, the initial negativity hypothesis posits that individuals' initial perception of surprised expressions is negative, and that those arriving at a positive interpretation must implement a regulatory mechanism to alter their interpretation.
 
-Given that a regulatory mechanism likely contributes to positive interpretations of surprised facial expressions, domain-specific interference may cause more negative interpretations of ambiguity compared to a more domain-general interference.
-Mattek and colleagues (2016) recently showed that different levels of cognitive load (i.e., holding either a single or seven digit number in working memory) does not affect subjective interpretations of surprised facial expressions, but that high cognitive loads do mitigate mouse trajectories.
-While the authors interpret this as a distinction between trait-like biases and dynamic cognitive-motor processes, there may be more domain-specific processes (e.g., emotional components) that span across these two measures of valence bias.
-Given the task irrelevance of the numeric distractors in Mattek and colleagues' (2016) work, it follows that the resources required for interpreting ambiguity as positive (Neta, Norris, \& Whalen, 2009) may not have been recruited for working memory maintenance, and thus no change in subjective ratings was observed.
+Behavioral evidence supports the initial negativity hypothesis.
+For instance, reaction time data show that individuals with more positive biases take longer to reach a valence judgment for surprised expressions than those with a more negative bias (Neta et al., 2009), suggesting a more time-intensive (regulatory) process for positive interpretations.
+Other work demonstrates the faster and default nature of negative interpretations through presenting either low- (LSF) or high-spatial frequency (HSF) images of surprised expressions.
+The images with only LSF information, which is processed earlier than its HSF counterpart, were rated more negatively than the HSF images (Neta \& Whalen, 2010).
+Additionally, surprised facial expressions are more quickly detected in an emotional oddball paradigm among happy (positive) than angry (negative) faces (Neta et al., 2011).
+The results from this paradigm suggest that surprised expressions are more readily perceived as similar to angry faces (i.e., perceived as negative) than happy faces.
 
-In the present study, we aim to test the effects of low and high working memory loads in both emotional and neutral domains.
-We expect that trials in which participants are maintaining an emotional working memory load will be more negative than neutral trials.
-Further, we predict that higher working memory laod trials, specifically in the emotional domain, will result in even more exaggerated negative interpretations.
+There is also support for the initial negativity hypothesis in neuroimaging studies.
+Ventromedial prefrontal cortex, a putative regulatory region, and amygdala actively are inversely correlated, and participants with more negative biases show higher activity in the amygdala while more positive participants show higher activity in vmPFC (Kim, Somerville, Johnstone, Alexander, \& Whalen, 2003).
+More recently, Petro and colleagues (2018) showed that participants with a more positive valence bias show more activity for surprised faces in emotion regulation-related brain regions (vmPFC).Taken together, both behavioral and brain data support the notion that negative interpretations of surprised faces are a faster, default process and positive interpretations rely on slower regulatory processes, which may be susceptible to demands from other cognitive processes.
 
-Recent work suggests that ambiguity resolution in this context requires more cognitive resources/processing compared to clearly valenced faces (Mattek et al., 2016; Neta \& Tong, 2016).
-The valence bias is trait-like (Neta et al., 2009) and generalizes to non-face stimuli (Neta et al., 2013); however, it is also malleable and may differ depenending on experimental manipulations, including stress inductions or instructions to slow responding (Brown, Raio, \& Neta, 2017; Neta \& Tong, 2016).
-Importantly, the valence bias relates to behavior outside of the laboratory; specifically, it is known to relate to depressive symptomology ({\textbf{???}}), at least in children.
-Chronic negativity biases are common in numerous psychopathologies, including depression and anxiety ({\textbf{???}}).
+\hypertarget{cognitive-loads-and-task-interference}{%
+\subsection{Cognitive loads and task interference}\label{cognitive-loads-and-task-interference}}
+
+In daily life, cognitive resources are often shared among several processes as stimuli compete for our attention.
+For example, imagine a student attending a lecture.
+If the student is frequently distracted by notifications and directing cognitive resources towards a text message conversation, computer applications, or even daydreams, then the student's ability to understand and remember the lecture will likely suffer.
+Indeed, cognitive resource competition, a phenomenon known as cognitive load, negatively impacts executive processes, such as attention (Lavie, Hirst, Fockert, \& Viding, 2004; Murphy, Groeger, \& Greene, 2016).
+High levels of cognitive load alter performance on a variety of tasks, including those in both cognitive and emotional domains (Kron, Schul, Cohen, \& Hassin, 2010; Nagamatsu et al., 2011; Pontari \& Schlenker, 2000, @jiaping\_empathy\_2017; Thomas, Donohue-Porter, \& Stein Fishbein, 2017).
+Working memory tasks, which require participants to maintain some stimulus representation in working memory, are often used for testing cognitive load effects (e.g., Burnham, 2010, @lavie\_role\_2005, or see @murphy\_twenty\_2016 for a review).
+
+The cognitive demands of active working memory maintenance often interact with concurrent affective processes (e.g., face categorization, subjective emotional experience), perhaps as a result of a shared resource pool for these processes.
+For instance, Ahmed (2018) showed that performance on a facial expression categorization task suffers when participants are under high cognitive load.
+Other work has linked cognitive load to changes in emotional responses (Blair et al., 2007; Van Dillen, Heslenfeld, \& Koole, 2009).
+For example, higher loads during a working memory task reduce subjective emotional experience, as well as amygdala activity (Van Dillen et al., 2009).
+Other neuroimaging work has shown that Stroop interference effects were exaggerated during trials temporally surrounded by emotional stimuli, while emotional responses in the brain (i.e., amygdala and inferior frontal gyrus activation) were lower during trials with Stroop task demands compared to trials with no concurrent task demands (Blair et al., 2007).
+Other work highlights the importance of cognitive load task characteristics on a syllogistic reasoning task, demonstrating that participants perform worse on tasks with emotional, rather than neutral, content when under high cognitive load (Trémolière, Gagnon, \& Blanchette, 2016).
+Together, these effects suggest an overlap between cognitive demands and emotional processes, with high cognitive demands interfering with typical emotion processing.
+
+Previous work has tested the effects of cognitive load on valence bias to assess both subjective ratings of surprise and the underlying cognitive-motor dynamics of the ratings via mousetracking.
+While there was no effect of load on subjective interpretations of surprised expressions, participants did show altered mouse trajectories, such that mouse movements were less drawn towards the response option (i.e., positive or negative) in line with one's bias (Mattek, Whalen, Berkowitz, \& Freeman, 2016).
+One potential explanation for the null effect of load on ratings is the domain-specificity of the cognitive load.
+While there are some domain-general effects of cognitive load on emotional processing (Blair et al., 2007; Van Dillen et al., 2009), which helps explain the effects of load on mouse trajectories, other lines of work have shown dissociable processing of emotional and non-emotional task stimuli (Egner, Etkin, Gale, \& Hirsch, 2008).
+Critically, Mattek and colleagues (2016) used non-emotional stimuli (i.e., number sequence) in their manipulation of cognitive load during interpretations of surprised facial expressions.
+The cognitive demand required for maintaining emotional information in working memory may tax resources used for emotion regulation more so than non-emotional information.
+Under the initial negativity framework, this would lead to more negative interpretations of surprise during cognitive load with emotional stimuli.
+
+\hypertarget{the-present-study}{%
+\subsection{The present study}\label{the-present-study}}
+
+In the present study we test the effects of both low and high cognitive load across emotional and non-emotional domains.
+We expect to find a main effect of load domain, emotional or non-emotional, on interpretations of surprise, such that interpretations made under emotional working memory loads are more negative than those made under non-emotional working memory loads.
+Further, we predict an interaction effect, such that emotional working memory loads with more content (high load) will result in more negative interpetations than emotional working memory loads with less content (low load).
 
@@
 
-The stimuli included faces from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets, as in previous work ({\textbf{???}}; Brown et al., 2017).
+The stimuli included faces from the NimStim (Tottenham et al., 2009) and Karolinska Directed Emotional Faces (Lundqvist, Flykt, \& Öhman, 1998) stimuli sets, as in previous work (Brown, Raio, \& Neta, 2017; Neta \& Whalen, 2010).
 The faces consisted of 34 unique identities including 11 angry, 12 happy, and 24 surprised expressions organized pseudorandomly.
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-ahmed_knowing_2018}{}%
+Ahmed, L.
+(2018).
+Knowing how you are feeling depends on what's on my mind: Cognitive load and expression categorization.
+\emph{Emotion}, \emph{18}(2), 190--201.
+doi:\href{https://doi.org/10.1037/emo0000312}{10.1037/emo0000312}
+
+\leavevmode\hypertarget{ref-baddeley_working_1986}{}%
+Baddeley, A. D. (1986). Working memory. \emph{Philosophical Transactions of the Royal Society of London}, \emph{302}(110), 311--324.
+
+\leavevmode\hypertarget{ref-barrett_emotional_2019}{}%
+Barrett, L.
+F., Adolphs, R., Marsella, S., Martinez, A.
+M., \& Pollak, S.
+D.
+(2019).
+Emotional expressions reconsidered: Challenges to inferring emotion from human facial movements.
+\emph{Psychological Science in the Public Interest: A Journal of the American Psychological Society}, \emph{20}(1), 1--68.
+doi:\href{https://doi.org/10.1177/1529100619832930}{10.1177/1529100619832930}
+
+\leavevmode\hypertarget{ref-blair_modulation_2007}{}%
+Blair, K.
+S., Smith, B.
+W., Mitchell, D.
+G.
+V., Morton, J., Vythilingam, M., Pessoa, L., \ldots{} Blair, R.
+J.
+R.
+(2007).
+Modulation of emotion by cognition and cognition by emotion.
+\emph{NeuroImage}, \emph{35}(1), 430--440.
+doi:\href{https://doi.org/10.1016/j.neuroimage.2006.11.048}{10.1016/j.neuroimage.2006.11.048}
+
 \leavevmode\hypertarget{ref-brown_cortisol_2017}{}%
@@
 
+\leavevmode\hypertarget{ref-burnham_cognitive_2010}{}%
+Burnham, B.
+R.
+(2010).
+Cognitive load modulates attentional capture by color singletons during effortful visual search.
+\emph{Acta Psychologica}, \emph{135}(1), 50--58.
+doi:\href{https://doi.org/10.1016/j.actpsy.2010.05.003}{10.1016/j.actpsy.2010.05.003}
+
+\leavevmode\hypertarget{ref-carroll_facial_1996}{}%
+Carroll, J.
+M., \& Russell, J.
+A.
+(1996).
+Do facial expressions signal specific emotions?
+Judging emotion from the face in context.
+\emph{Journal of Personality and Social Psychology}, \emph{70}(2), 205--218.
+doi:\href{https://doi.org/10.1037//0022-3514.70.2.205}{10.1037//0022-3514.70.2.205}
+
+\leavevmode\hypertarget{ref-darwin_expression_1872}{}%
+Darwin, C. (1872). \emph{The expression of the emotions in man and animals}. John Murray.
+
 \leavevmode\hypertarget{ref-egner_dissociable_2008}{}%
@@
 doi:\href{https://doi.org/10.1093/cercor/bhm179}{10.1093/cercor/bhm179}
+
+\leavevmode\hypertarget{ref-ekman_constants_1971}{}%
+Ekman, P., \& Friesen, W.
+V.
+(1971).
+Constants across cultures in the face and emotion.
+\emph{Journal of Personality and Social Psychology}, \emph{17}(2), 124--129.
+doi:\href{https://doi.org/10.1037/h0030377}{10.1037/h0030377}
 
@@
 
-\leavevmode\hypertarget{ref-gruber_effects_2001}{}%
-Gruber, O.
-(2001).
-Effects of domain-specific interference on brain activation associated with verbal working memory task performance.
-\emph{Cerebral Cortex (New York, N.Y.: 1991)}, \emph{11}(11), 1047--1055.
-doi:\href{https://doi.org/10.1093/cercor/11.11.1047}{10.1093/cercor/11.11.1047}
+\leavevmode\hypertarget{ref-frith_role_2009}{}%
+Frith, C.
+(2009).
+Role of facial expressions in social interactions.
+\emph{Philosophical Transactions of the Royal Society B: Biological Sciences}, \emph{364}(1535), 3453--3458.
+doi:\href{https://doi.org/10.1098/rstb.2009.0142}{10.1098/rstb.2009.0142}
+
+\leavevmode\hypertarget{ref-green_factors_2018}{}%
+Green, C., \& Guo, K.
+(2018).
+Factors contributing to individual differences in facial expression categorisation.
+\emph{Cognition \& Emotion}, \emph{32}(1), 37--48.
+doi:\href{https://doi.org/10.1080/02699931.2016.1273200}{10.1080/02699931.2016.1273200}
+
+\leavevmode\hypertarget{ref-izard_innate_1994}{}%
+Izard, C.
+E.
+(1994).
+Innate and universal facial expressions: Evidence from developmental and cross-cultural research.
+\emph{Psychological Bulletin}, \emph{115}(2), 288--299.
+doi:\href{https://doi.org/10.1037/0033-2909.115.2.288}{10.1037/0033-2909.115.2.288}
+
+\leavevmode\hypertarget{ref-jiaping_empathy_2017}{}%
+Jiaping, C., Yuejia, L.
+U.
+O., Fang, C.
+U.
+I., Jiaping, C., Yuejia, L.
+U.
+O., \& Fang, C.
+U.
+I.
+(2017).
+Empathy for pain influenced by cognitive load: Evidence from an ERP study.
+\emph{Acta Psychologica Sinica}, \emph{49}(5), 622--630.
+doi:\href{https://doi.org/10.3724/SP.J.1041.2017.00622}{10.3724/SP.J.1041.2017.00622}
+
+\leavevmode\hypertarget{ref-kim_inverse_2003}{}%
+Kim, H., Somerville, L.
+H., Johnstone, T., Alexander, A.
+L., \& Whalen, P.
+J.
+(2003).
+Inverse amygdala and medial prefrontal cortex responses to surprised faces.
+\emph{Neuroreport}, \emph{14}(18), 2317--2322.
+doi:\href{https://doi.org/10.1097/00001756-200312190-00006}{10.1097/00001756-200312190-00006}
+
+\leavevmode\hypertarget{ref-krieglmeyer_being_2010}{}%
+Krieglmeyer, R., Deutsch, R., De Houwer, J., \& De Raedt, R.
+(2010).
+Being moved: Valence activates approach-avoidance behavior independently of evaluation and approach-avoidance intentions.
+\emph{Psychological Science}, \emph{21}(4), 607--613.
+doi:\href{https://doi.org/10.1177/0956797610365131}{10.1177/0956797610365131}
+
+\leavevmode\hypertarget{ref-kron_feelings_2010}{}%
+Kron, A., Schul, Y., Cohen, A., \& Hassin, R.
+R.
+(2010).
+Feelings don't come easy: Studies on the effortful nature of feelings.
+\emph{Journal of Experimental Psychology: General}, \emph{139}(3), 520--534.
+doi:\href{https://doi.org/10.1037/a0020008}{10.1037/a0020008}
 
@@
 
+\leavevmode\hypertarget{ref-lavie_role_2005}{}%
+Lavie, N., \& De Fockert, J.
+(2005).
+The role of working memory in attentional capture.
+\emph{Psychonomic Bulletin \& Review}, \emph{12}(4), 669--674.
+doi:\href{https://doi.org/10.3758/BF03196756}{10.3758/BF03196756}
+
 \leavevmode\hypertarget{ref-lavie_load_2004}{}%
@@
 Load theory of selective attention and cognitive control.
-\emph{Journal of Experimental Psychology: General}, \emph{133}(3), 339--354.
+\emph{Journal of Experimental Psychology.
+General}, \emph{133}(3), 339--354.
 doi:\href{https://doi.org/10.1037/0096-3445.133.3.339}{10.1037/0096-3445.133.3.339}
+
+\leavevmode\hypertarget{ref-lazarus_short-circuiting_1964}{}%
+Lazarus, R.
+S., \& Alfert, E.
+(1964).
+Short-circuiting of threat by experimentally altering cognitive appraisal.
+\emph{The Journal of Abnormal and Social Psychology}, \emph{69}(2), 195--205.
+doi:\href{https://doi.org/10.1037/h0044635}{10.1037/h0044635}
 
@@
 
-\leavevmode\hypertarget{ref-mikels_affective_2019}{}%
-Mikels, J.
-A., \& Reuter-Lorenz, P.
-A.
-(2019).
-Affective working memory: An integrative psychological construct.
-\emph{Perspectives on Psychological Science: A Journal of the Association for Psychological Science}, \emph{14}(4), 543--559.
-doi:\href{https://doi.org/10.1177/1745691619837597}{10.1177/1745691619837597}
+\leavevmode\hypertarget{ref-murphy_twenty_2016}{}%
+Murphy, G., Groeger, J.
+A., \& Greene, C.
+M.
+(2016).
+Twenty years of load theory---where are we now, and where should we go next?
+\emph{Psychonomic Bulletin \& Review}, \emph{23}(5), 1316--1340.
+doi:\href{https://doi.org/10.3758/s13423-015-0982-5}{10.3758/s13423-015-0982-5}
+
+\leavevmode\hypertarget{ref-nagamatsu_increased_2011}{}%
+Nagamatsu, L.
+S., Voss, M., Neider, M.
+B., Gaspar, J.
+G., Handy, T.
+C., Kramer, A.
+F., \& Liu-Ambrose, T.
+Y.
+L.
+(2011).
+Increased cognitive load leads to impaired mobility decisions in seniors at risk for falls.
+\emph{Psychology and Aging}, \emph{26}(2), 253--259.
+doi:\href{https://doi.org/10.1037/a0022929}{10.1037/a0022929}
+
+\leavevmode\hypertarget{ref-neta_valence_2011}{}%
+Neta, M., Davis, F.
+C., \& Whalen, P.
+J.
+(2011).
+Valence resolution of ambiguous facial expressions using an emotional oddball task.
+\emph{Emotion}, \emph{11}(6), 1425--1433.
+doi:\href{https://doi.org/10.1037/a0022993}{10.1037/a0022993}
 
@@
 
-\leavevmode\hypertarget{ref-neta_dont_2016}{}%
-Neta, M., \& Tong, T.
-T.
-(2016).
-Don't like what you see?
-Give it time: Longer reaction times associated with increased positive affect.
-\emph{Emotion (Washington, D.C.)}, \emph{16}(5), 730--739.
-doi:\href{https://doi.org/10.1037/emo0000181}{10.1037/emo0000181}
+\leavevmode\hypertarget{ref-neta_primacy_2010}{}%
+Neta, M., \& Whalen, P.
+J.
+(2010).
+The primacy of negative interpretations when resolving the valence of ambiguous facial expressions.
+\emph{Psychological Science}, \emph{21}(7), 901--907.
+doi:\href{https://doi.org/10.1177/0956797610373934}{10.1177/0956797610373934}
 
-\leavevmode\hypertarget{ref-neta_its_2018}{}%
-Neta, M., Tong, T.
-T., \& Henley, D.
-J.
+\leavevmode\hypertarget{ref-petro_individual_2018}{}%
+Petro, N.
+M., Tong, T.
+T., Henley, D.
+J., \& Neta, M.
 (2018).
-It's a matter of time (perspectives): Shifting valence responses to emotional ambiguity.
-\emph{Motivation and Emotion}, \emph{42}, 258--266.
-doi:\href{https://doi.org/10.1007/s11031-018-9665-7}{10.1007/s11031-018-9665-7}
+Individual differences in valence bias: fMRI evidence of the initial negativity hypothesis.
+\emph{Social Cognitive and Affective Neuroscience}, \emph{13}(7), 687--698.
+doi:\href{https://doi.org/10.1093/scan/nsy049}{10.1093/scan/nsy049}
 
-\leavevmode\hypertarget{ref-stroop_studies_1935}{}%
-Stroop, J.
+\leavevmode\hypertarget{ref-pontari_influence_2000}{}%
+Pontari, B.
+A., \& Schlenker, B.
 R.
-(1935).
-Studies of interference in serial verbal reactions.
-\emph{Journal of Experimental Psychology}, \emph{18}(6), 643--662.
-doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}
+(2000).
+The influence of cognitive load on self-presentation: Can cognitive busyness help as well as harm social performance?
+\emph{Journal of Personality and Social Psychology}, \emph{78}(6), 1092--1108.
+doi:\href{https://doi.org/10.1037/0022-3514.78.6.1092}{10.1037/0022-3514.78.6.1092}
+
+\leavevmode\hypertarget{ref-said_statistical_2011}{}%
+Said, C.
+P., \& Todorov, A.
+(2011).
+A statistical model of facial attractiveness.
+\emph{Psychological Science}, \emph{22}(9), 1183--1190.
+doi:\href{https://doi.org/10.1177/0956797611419169}{10.1177/0956797611419169}
+
+\leavevmode\hypertarget{ref-thomas_impact_2017}{}%
+Thomas, L., Donohue-Porter, P., \& Stein Fishbein, J.
+(2017).
+Impact of interruptions, distractions, and cognitive load on procedure failures and medication administration errors: \emph{Journal of Nursing Care Quality}, \emph{32}(4), 309--317.
+doi:\href{https://doi.org/10.1097/NCQ.0000000000000256}{10.1097/NCQ.0000000000000256}
+
+\leavevmode\hypertarget{ref-todorov_evaluating_2008}{}%
+Todorov, A., Baron, S.
+G., \& Oosterhof, N.
+N.
+(2008).
+Evaluating face trustworthiness: A model based approach.
+\emph{Social Cognitive and Affective Neuroscience}, \emph{3}(2), 119--127.
+doi:\href{https://doi.org/10.1093/scan/nsn009}{10.1093/scan/nsn009}
 
@@
 
-\leavevmode\hypertarget{ref-whalen_emotional_2006}{}%
-Whalen, P.
-J., Bush, G., Shin, L.
-M., \& Rauch, S.
+\leavevmode\hypertarget{ref-tremoliere_cognitive_2016}{}%
+Trémolière, B., Gagnon, M.-È., \& Blanchette, I.
+(2016).
+Cognitive load mediates the effect of emotion on analytical thinking.
+\emph{Experimental Psychology}, \emph{63}(6), 343--350.
+doi:\href{https://doi.org/10.1027/1618-3169/a000333}{10.1027/1618-3169/a000333}
+
+\leavevmode\hypertarget{ref-van_dillen_tuning_2009}{}%
+Van Dillen, L.
+F., Heslenfeld, D.
+J., \& Koole, S.
 L.
-(2006).
-The emotional counting stroop: A task for assessing emotional interference during brain imaging.
-\emph{Nature Protocols}, \emph{1}(1), 293--296.
-doi:\href{https://doi.org/10.1038/nprot.2006.45}{10.1038/nprot.2006.45}
+(2009).
+Tuning down the emotional brain: An fMRI study of the effects of cognitive load on the processing of affective images.
+\emph{NeuroImage}, \emph{45}(4), 1212--1219.
+doi:\href{https://doi.org/10.1016/j.neuroimage.2009.01.016}{10.1016/j.neuroimage.2009.01.016}
 

### 2020-08-14 CheckingStimulusProperties.R

@@ -1,0 +1,55 @@
+### Run the data cleaning MERP script to get the MT.data object... ###
+
+### count new IAPS images in the memory probe condition ###
+## flag trials after face trials ###
+for(i in 1:(nrow(MT.data$data)-1)) {
+  MT.data$data$flag[i+1] <- ifelse(MT.data$data$cond.correct[i] %in% c("Surprise",
+                                                                       "Angry", "Happy"),
+                                   1, 0)
+}
+
+### remove flagged trials ###
+MT.data$data <- subset(MT.data$data, MT.data$data$flag == 1)
+View(MT.data$data)
+no <- subset(MT.data$data, MT.data$data$condition == "No" & MT.data$data$flag == 1)
+yes <- subset(MT.data$data, MT.data$data$condition == "Yes" & MT.data$data$flag == 1)
+count(yes$subjID)
+
+unique(no$stim) # 63 unique
+
+### read in the 144 images in the matrices to compare which were repeated in the probe ###
+library(openxlsx)
+stim.data <- read.xlsx("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/IAPS_Stim_List.xlsx")
+MT.data$data$stim.recode <- str_sub(MT.data$data$stim, 22, 25)
+MT.data$data$stim.recode
+MT.data$data$stimflag <- ifelse(c(MT.data$data$stim) %in% c(MT.data$data$stim.recode),
+                                1, 0)
+temp <- mt_subset(MT.data, MT.data$data$stimflag == 1) # empty dataframe, none of the "no" images were in the 144 IAPS. 
+
+### now want to equate pos vs. neg probe images... ###
+iaps.norm <- read_excel("~/Documents/Nick-Grad/Neta_Lab/Stimuli/IAPS_ratings.xls")
+
+### subset to only include "no" images from above ###
+no$stim.recode <- str_sub(no$stim, 22, 25)
+iaps.norm <- subset(iaps.norm, iaps.norm$IAPS %in% no$stim.recode)
+
+### find the valence cutoffs for pos and neg in the 144 stim... 
+min(stim.data$Val_Mn[which(stim.data$Condition == "POS")])
+max(stim.data$Val_Mn[which(stim.data$Condition == "POS")])
+min(stim.data$Val_Mn[which(stim.data$Condition == "NEG")])
[…]

### 2020-08-14 Data_Cleaning.R

@@ -31,9 +31,9 @@ if (!require("processx")) install.packages("processx")
 }
 
 {
-session1files <- list.files(path = "/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/Data/Session1", 
+session1files <- list.files(path = "/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Session1", 
                             pattern = "*.mt", full.names = TRUE, recursive = FALSE)
-session1.data <- read_bulk("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/Data/Session1/", fun = read_mt, 
+session1.data <- read_bulk("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Session1/", fun = read_mt, 
                            extension = ".mt")
 session1.data <- mt_import_wide(session1.data)
 foreach(file = session1files) %do% {

### 2020-08-14 Final_MS_Analyses.R

@@ -1,0 +1,679 @@
+#install.packages("TOSTER")
+{
+library(ggsignif)
+library(lme4)
+library(jtools)
+# install.packages("robustlmm")
+library(robustlmm)
+library(tidyverse)
+# install.packages("reghelper")
+library(reghelper)
+library(lmerTest)
+library(effects)
+library(emmeans)
+library(car)
+library(MASS)
+require(lattice)
+#install.packages("blme")
+library(blme)
+}
+### use ALL trials, no wm rejects ###
+#data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2020-02-05_10-02-59.csv")
+### set working directory to MouseTrap Demo folder ###
+
+### No RT / No WM exclusion ###
+#data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final_Data_NoExclusions.csv.csv")
+data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final_Data_NoExclusions.csv")
+### 2 SD RT exclusion ###
+#data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final_Data_2SDRTexclusion.csv")
+
+### 3 SD RT exclusion ###
+#data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final_Data_2SDRTexclusion.csv")
+
+data <- data[, -1]
+data <- MT.data.rating.table2
+### RATE ###
+long <- gather(data, key = "Condition", value = "PerNeg",
+               lo.emo.sur_rate, hi.emo.sur_rate,
+               lo.neu.sur_rate, hi.neu.sur_rate)
+
+level1 <- long[, c("subjID", "Condition", "PerNeg")]
+level1$Dom <- ifelse(level1$Condition == "lo.emo.sur_rate", 1,
+                     ifelse(level1$Condition == "hi.emo.sur_rate", 1, 0))
[…]

### 2020-08-14 FormatData_MLM.R

@@ -1,0 +1,494 @@
+library(lme4)
+library(jtools)
+# install.packages("robustlmm")
+library(robustlmm)
+library(tidyverse)
+# install.packages("reghelper")
+library(reghelper)
+library(lmerTest)
+library(effects)
+library(emmeans)
+library(car)
+library(MASS)
+require(lattice)
+#install.packages("blme")
+library(blme)
+
+#data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-09-06_12-18-56.csv")
+
+
+### use ALL trials, no wm rejects ###
+data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2020-02-05_10-02-59.csv")
+
+data <- data[, -1]
+long <- gather(data, key = "Condition", value = "PerNeg",
+               lo.emo.sur_rate, hi.emo.sur_rate,
+               lo.neu.sur_rate, hi.neu.sur_rate)
+
+#### RATE ####
+long <- gather(data, key = "Condition", value = "PerNeg",
+               lo.emo.sur_rate, hi.emo.sur_rate,
+               lo.neu.sur_rate, hi.neu.sur_rate)
+
+level1 <- long[, c("subjID", "Condition", "PerNeg")]
+level1$Dom <- ifelse(level1$Condition == "lo.emo.sur_rate", 1,
+                      ifelse(level1$Condition == "hi.emo.sur_rate", 1, 0))
+level1$Load <- ifelse(level1$Condition == "lo.emo.sur_rate", 0,
+                      ifelse(level1$Condition == "lo.neu.sur_rate", 0, 1))
+
+#write.csv(level1, "mlm_l1.csv", row.names = F)
+
+### try alternative distribution ###
+level1$PerNeg.t <- level1$PerNeg * 100
+# level1$PerNeg.t <- level1$PerNeg.t + .1
+
+### normal ###
+qqp(level1$PerNeg.t, "norm")
+
+### log normal ###
+qqp(level1$PerNeg.t, "lnorm")
+
+### Binomial ###
+nbinom <- fitdistr(level1$PerNeg.t, "Negative Binomial")
+qqp(level1$PerNeg.t, "nbinom", size = nbinom$estimate[[1]], mu = nbinom$estimate[[2]])
+
+### Poisson ###
[…]

### 2020-08-14 GEE_Analyses.R

@@ -1,0 +1,651 @@
+# install.packages("gee")
+library(gee)
+library(geepack)
+library(lme4)
+library(lmerTest)
+library(effects)
+library(emmeans)
+### run data_cleaning_MERP until line 287 ###
+
+# Reshape time-normalized trajectories data into wide format
+# only keeping xpos and ypos
+# and adding Condition variable
+trajectories_wide <- mt_reshape(MT.data,
+                                use="tn_trajectories", use_variables = c("xpos"),
+                                use2_variables = "condition.rating",
+                                trajectories_long = FALSE
+)
+
+### merge with .data ###
+full <- cbind(MT.data$data, trajectories_wide)
+
+### check RT min / max for outliers ###
+meanrt <- mean(full$RT[which(full$trialtype == "face")])
+sdrt <- sd(full$RT[which(full$trialtype == "face")])
+outlier <- meanrt + (3*sdrt)
+#print(outlier)
+
+### remove trials > outlierRT ###
+full <-full[!(full$RT >= outlier),]
+
+## flag trials before incorrect memory probes ###
+for(i in 2:nrow(full)) {
+  full$flag[i-1] <- ifelse(full$mem.cor[i] == 0, 0, 1)
+}
+
+### remove flagged trials ###
+full <- subset(full, full$flag == 1)
+
+#temp <- (ddply(full, "subjID", summarise,
+ #              xpos1_sur_n = mean(xpos_1[which(condition.rating == "Sur.Neg")]),
+  #             xpos2_sur_n = mean(xpos_2[which(condition.rating == "Sur.Neg")])))
+
+#for(i in full[, c(41:142)]) {
+#  
+#}
+
+varz <- 1:101
+varz <- paste("xpos_", varz, sep = "")
+
+### split to average x coordinates by rating ###
+sur.neg.low.neu <- full %>% subset(condition.rating == "Sur.Neg" & 
+                                     load == "LOW" & type == "NEU")
+sur.neg.low.neu <- sur.neg.low.neu %>% group_by(subjID) %>% 
[…]

### 2020-08-14 Sess1_Data_Cleaning.R

@@ -1,0 +1,608 @@
+### set working directory to MouseTrap Demo folder ###
+setwd("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads")
+
+if (!require("processx")) install.packages("processx")
+
+### load the packages... This needs to be done every time. ###
+{suppressPackageStartupMessages(library(mousetrap)) 
+  suppressPackageStartupMessages(library(foreach))
+  suppressPackageStartupMessages(library(tidyverse))
+  suppressPackageStartupMessages(library(readbulk))
+  suppressPackageStartupMessages(library(plyr))
+  suppressPackageStartupMessages(library(utils))
+  suppressPackageStartupMessages(library(stats))
+  suppressPackageStartupMessages(library(pracma))
+  suppressPackageStartupMessages(library(tidyr))
+  suppressPackageStartupMessages(library(magrittr))
+  suppressPackageStartupMessages(library(graphics))
+  suppressPackageStartupMessages(library(grDevices))
+  suppressPackageStartupMessages(library(ggplot2))
+  suppressPackageStartupMessages(library(scales))
+  suppressPackageStartupMessages(library(psych))
+  suppressPackageStartupMessages(library(Rcpp))
+  suppressPackageStartupMessages(library(diptest))
+  suppressPackageStartupMessages(library(RColorBrewer))
+  suppressPackageStartupMessages(library(cstab))
+  suppressPackageStartupMessages(library(fastcluster))
+  suppressPackageStartupMessages(library(parallel))
+  suppressPackageStartupMessages(library(fields))
+  suppressPackageStartupMessages(library(readxl))
+  suppressPackageStartupMessages(library(yarrr))
+}
+
+  session1files <- list.files(path = "/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Session1", 
+                              pattern = "*.mt", full.names = TRUE, recursive = FALSE)
+  session1.data <- read_bulk("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Session1/", fun = read_mt, 
+                             extension = ".mt")
+  session1.data <- mt_import_wide(session1.data)
+  foreach(file = session1files) %do% {
+    ### create "rate" variable (0 = Positive, 1 = Negative) ###
[…]

### 2020-08-14 T-Test_AccuracyEmo.R

@@ -1,0 +1,36 @@
+MT.data$data$stim.recode2 <- str_sub(MT.data$data$stim, 22, 25)
+
+iaps.norm <- read_excel("~/Documents/Nick-Grad/Neta_Lab/Stimuli/IAPS_ratings.xls")
+
+### find the valence cutoffs for pos and neg in the 144 stim... 
+min(stim.data$Val_Mn[which(stim.data$Condition == "POS")])
+max(stim.data$Val_Mn[which(stim.data$Condition == "POS")])
+min(stim.data$Val_Mn[which(stim.data$Condition == "NEG")])
+max(stim.data$Val_Mn[which(stim.data$Condition == "NEG")])
+stim.data <- read.xlsx("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/IAPS_Stim_List.xlsx")
+### ok, now label the "no" images based off the valence cutoffs above... 
+iaps.norm$CONDITION <- ifelse(iaps.norm$valmn >= 5.07, "POS",
+                              ifelse(iaps.norm$valmn <= 4.32, "NEG",
+                                     "NEU"))
+
+
+MT.data$data$probeVal <- ifelse(MT.data$data$stim.recode2 %in% iaps.norm$IAPS,
+                                iaps.norm$CONDITION, "")
+names(MT.data$data)[names(MT.data$data)=="stim.recode2"] <- "IAPS"
+MT.data$data <- merge(MT.data$data, iaps.norm[, c("IAPS", "CONDITION")], by = "IAPS")
+View(MT.data$data)
+MT.data$data$probeVal <- MT.data$data$CONDITION
+
+MT.data$data <- subset(MT.data$data, MT.data$data$trialtype == "memory")
+### fix 9635.2 discrepancy 
+MT.data$data$probeVal <- ifelse(MT.data$data$IAPS == 9635, "NEG",
+                                MT.data$data$probeVal)
+MT.data$data$mem.cor <- as.numeric(MT.data$data$mem.cor)
+MT.data.rating.table2 <- (ddply(MT.data$data, "subjID", summarise, 
+                                emo.acc.Pos = mean(mem.cor[which(type == "EMO" & CONDITION == "POS")], na.rm = T),
+                                emo.acc.Neg = mean(mem.cor[which(type == "EMO" & CONDITION == "NEG")], na.rm = T)))
+
[…]

### 2020-08-14 count_social_media_subj_Duration.R

@@ -1,0 +1,50 @@
+### set wd ###
+nhpath <- "~/Documents/Nick-Grad/Neta_Lab/covid19/Git/data/"
+# cbpath <- "~/Documents/Github/COVID/data/"
+setwd(nhpath)
+
+#install.packages("anytime")
+library(anytime)
+library(lubridate)
+
+### READ IN CONSENT 
+cbs_soc_v4_consent <- read.csv("data_exp_17280-v4_questionnaire-4qon.csv")
+cbs_soc_v5_consent <- read.csv("data_exp_17280-v5_questionnaire-4qon.csv")
+cbs_soc_v6_consent <- read.csv("data_exp_17280-v6_questionnaire-4qon.csv")
+
+### pull final questionnaire node to get duration ###
+cbs_soc_end_v4 <- read.csv("data_exp_17280-v4_questionnaire-1r6c.csv")
+cbs_soc_end_v5 <- read.csv("data_exp_17280-v5_questionnaire-1r6c.csv")
+cbs_soc_end_v6 <- read.csv("data_exp_17280-v6_questionnaire-1r6c.csv")
+
+cbs_soc_end_v4 <- cbs_soc_end_v4[!grepl("END OF FILE", cbs_soc_end_v4$Event.Index), ]
+cbs_soc_end_v5 <- cbs_soc_end_v5[!grepl("END OF FILE", cbs_soc_end_v5$Event.Index), ]
+cbs_soc_end_v6 <- cbs_soc_end_v6[!grepl("END OF FILE", cbs_soc_end_v6$Event.Index), ]
+
+### read in the final node for "end time" 
+cbs_times <- merge(cbs_soc_v4_consent, cbs_soc_end_v4, by = "Participant.Private.ID")
+
+cbs_times2 <- merge(cbs_soc_v5_consent, cbs_soc_end_v5, by = "Participant.Private.ID")
+
+cbs_times3 <- merge(cbs_soc_v6_consent, cbs_soc_end_v6, by = "Participant.Private.ID")
+
+cbs_times <- cbs_times[, c("UTC.Date.x", "UTC.Date.y", "Local.Timezone.x", "Local.Timezone.y",
+                           "Local.Date.x", "Local.Date.y", "Participant.Private.ID",
+                           "Participant.Public.ID.x", "Participant.Completion.Code.x")]
+cbs_times2 <- cbs_times2[, c("UTC.Date.x", "UTC.Date.y", "Local.Timezone.x", "Local.Timezone.y",
[…]

### 2020-08-14 data_cleaning_MERP.R

@@ -28,6 +28,7 @@ if (!require("processx")) install.packages("processx")
   suppressPackageStartupMessages(library(fields))
   suppressPackageStartupMessages(library(readxl))
   suppressPackageStartupMessages(library(yarrr))
+  suppressPackageStartupMessages(library(stringr))
 }
 
 ### import session two files ###
@@ -264,6 +265,30 @@ MT.data <- mt_import_wide(MT.data)
   ### factor ###
   MT.data$data$factor <- paste(MT.data$data$type, MT.data$data$load)
   
+  
+  ### add counts of pos and neg ratings for accurate and inaccurate trials ###
+  MT.data$data$ChiCounts <- ifelse(MT.data$data$rate == 0 & 
+                                        MT.data$data$mem.cor == 1 &
+                                        MT.data$data$type == "EMO", 1,
+                                      ifelse(MT.data$data$rate == 0 & 
+                                               MT.data$data$mem.cor == 0 &
+                                               MT.data$data$type == "EMO",2,
+                                             ifelse(MT.data$data$rate == 1 & 
+                                                      MT.data$data$mem.cor == 1 &
+                                                      MT.data$data$type == "EMO", 3,
+                                                    ifelse(MT.data$data$rate == 1 & 
+                                                             MT.data$data$mem.cor == 0 &
+                                                             MT.data$data$type == "EMO", 4, ""))))
+  
+  # MT.data$data$PosCount_Ina <- ifelse(MT.data$data$rate == 0 & 
+  #                                       MT.data$data$mem.cor == 0 &
+  #                                       MT.data$data$type == "EMO",1, "")
+  # MT.data$data$NegCount_Acc <- ifelse(MT.data$data$rate == 1 & 
+  #                                       MT.data$data$mem.cor == 1 &
+  #                                       MT.data$data$type == "EMO", 1, "")
+  # MT.data$data$NegCount_Ina <- ifelse(MT.data$data$rate == 1 & 
+  #                                       MT.data$data$mem.cor == 0 &
+  #                                       MT.data$data$type == "EMO", 1, "")
 }
   
   ###  MT Measures ###
[…]

### 2020-08-14 qualtrics.R

@@ -1,0 +1,21 @@
+### set working directory to MouseTrap Demo folder ###
+setwd("/Users/nicholasharp/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads")
+
+qualtrics <- read.csv("Data/qualtrics_2019.11.12.csv")
+
+### read data file ###
+data <- read.csv("~/Documents/Nick-Grad/Neta_Lab/depletion_study/study2/Analyses/WorkingMemoryLoads/Data/Cleaned_Data/Final.Data.csv_2019-09-06_12-18-56.csv")
+
+qualtrics <- qualtrics[-c(1:2), ]
+rownames(qualtrics) <- NULL
+
+### drop no shows ###
+qualtrics <- subset(qualtrics, !Q2 %in% c("71004", "71022", "71057"))
+
+qualtrics %>% count(Q4, sort = T, "sex")
+
+class(qualtrics$Q3)
+qualtrics$Q3 <- as.character(qualtrics$Q3)
+qualtrics$Q3 <- as.integer(qualtrics$Q3)
+mean(qualtrics$Q3)
+sd(qualtrics$Q3)
